November 2nd, 2017

8:33 am day 1

I'm especially optimistic about this new strategy of fixing my garbage
life. Already I'm at the bus stop and have nothing to do, so I naturally
go to make a journal. Perhaps this isn't as productive as reading a hard
book, but it is better than browsing crap. ``An interesting note'' --
stop conforming to fit into a stereotype mold of what you imagine your
ideal self-embodying. The human is complex, the ideal will just be, not
exist as some mental heuristic or predictable interaction patterns- just
there (referring to the previous sentence starting with perhaps) I
caught myself conforming to a previously observed bullshit speech
format. ``Perhaps I haven't done x, and maybe perhaps I haven't done y,
but I've done something that superficially relates to some wholesome
aspect of human living and behavior, thus all external observers must
acknowledge the `holy' nature of this deed and use that deed to justify
the entire act being described. `` I'm noticing my mind isn't clearer in
terms of mental fog, but more relaxed. Things feel empty, vanilla. The
multicolored hurried worries of whatever I'm doing to entertain myself
are gone.

Act in a way that acknowledges a superior role within an expected
hierarchy. The minds of people you talk with should naturally assume
this hierarchy and then acknowledge and respect your status.

\bigskip
\bigskip
November 3rd, 2017

Day 2,

Though it may be me trying to find confirmation in my first impression
of monk mode because it was a positive one, I do think I am more in tune
to my body and emotions. YouTube and videogames actually feel quite
distant now, I feel much more adult. I saw one of the nachman golf carts
with the old guy, I found it genuinely hilarious. It does seem my
sensitivity to happiness has increased.

\emph{typed during Friday night dinner party}

I genuinely need to stop being weird. My natural intuitive self, where
social interaction is concerned, is wholly ineffective at being cool or
socially regarded highly from years of malpractice (ie, a shit social
life). Because of this, social interactions can never be natural, at
least not until the proper social practice becomes intuitive. I need to
be conscious, always, of what I'm saying. Restrict all impulses and
conform in major marginal events that serve as a test of acceptance
within a perceived society (organized games regarding sex, physical
contact, or other ``tween'' topics that are forced for the sake of
mutually understood desires, sex). Intellectually identify yourself as
an individual, but don't emotionally respond.

A dinner party is not a gathering of your friends with whom you can act
naturally, it is a test to determine and reconfirm that social status of
those present. (edit next morning, I'm being a bit disingenuous here
because of the later mentioned bitterness and the perceived wrongdoing,
in my subconscious thought process, having the potential to justify this
disingenuousness when the inconsistency with reality will, in my current
perception, be inevitably confronted. This is not the reality itself, or
at least I haven't thought through that at all, this description is the
reality which would produce from me the desired responding behavior. I
want myself to act as if it is a test and not friends, though a dinner
party surely is meant to be a gathering of friends. This reminds me that
I must have a good time as well, seat placement is very Critical to be
close to people you can talk to freely.) When embracing an unconscious
assumption underlying your behavior of shared fundamental value (or
behaving as if they are true friends) you expose your weak points and
firmly situate yourself as shit. You have no friends, you have a
specific friend at a specific time. Two friends can never exist at once,
when interacting with one as a friend another can never be a friend, at
this point the social game begins and requires intensive thought (next
morning edit: again, this is disingenuous. This is the reality that
produces my desired response, not necessarily The reality though it
does, I believe, have relative truth in comparing 1on1 with group
conversations.). Even then, one on one interactions are still understood
from a context of a larger society. Unless you are close enough with an
individual where they can place you and themselves as the top of a
pyramid of truth and context, where the relevant society considered is
you and them and no one else (ex, Matt), they can and must never be a
true friend.

I'm speaking slightly bitterly now to express to an external observer
bitterness, and ultimately direct anger and blame at this observer at
this time emotionally substituted with myself, for the unfairness or
incorrectness of this system, being the dynamic to which the
aforementioned friends are supposedly directly responsible. Do not
reject the system, do not reject the dynamic. Acknowledge it is flawed
and that it wouldn't exist in the presence of extremely well minded and
open individuals (ie, proper adherents and scholars of the Torah),
however don't reject the flawed system. Embrace it, understand how to
excel in this system, for it pervades throughout every aspect of
advanced adult life within a nonreligious society. It will inevitably be
useful in business and everything there related.

(After eating cookies and shit) I should also remind myself that my
current state of hyper observant retrospection is because of monk mode,
including not gaining happiness from crap. Junk food is crap, find a way
out of the situation rather than endure it with shit. Psychopathy is
totally on the tables, justified by the previous observation showing
they are not your friends, but players in a game. Lie and tell them
you're not feeling well.

Don't be open minded about arbitrary conventions, be a doofis. Adamantly
demand conventions are followed by your knowledge of them, further,
specify what these are mentally beforehand so as to enable me their
strict adherence. Never acknowledge them.

\bigskip
\bigskip
November 4th, 2017

Day 3,

I felt angry just now at light rail. I additionally felt nervous about
paying the ticket. If I used a device to calm me down, I'm unaware but
I'm now quite calm. It seems to pass quickly with time, so something
like meditation is probably ideal for

\bigskip
\bigskip
November 5th, 2017

Day 4,

I began writing my college essay. It has the necessary elements of a
thesis, body, etc. but feels empty and badly usual. The topics I'm
writing about are lacking meat, I think that ultimately is a necessity
because of the word limit. Instead of trying to make profound statements
with little words, of trying to fit your entire being into a small
essay, it's likely better to talk about one more meat moment or to
briefly touch upon many things into an overarching conclusion that is
evident from the content itself.

\bigskip
\bigskip
November 7th, 2017

Day 6,

I have been having horrible insomnia lately. I only think about sex at
night, though I have surprisingly little inhibition at the thought of
making moves. Hopefully will get laid this week.

\bigskip
\bigskip
November 9th, 2017

Day 8,

I've made what appears to me to be a profound epiphany. I'm far too
focused on attaining women and that is exactly what will inhibit me from
doing so. A woman will judge a mate based on a perceived approximation
of their life. In a constant underlying pursuit of a mate, one is
impeding whatever other goals in life they are pursuing and will, thus,
not complete those goals as effective to the standard. One must simply
live their life in the most successful or satisfying way possible and
mates will come naturally, as creating a coherent and fulfilling
existence improves the mentioned approximation evaluation.

Its later in the night now. I'm fairly drunk but actually quite
depressed instead of happy, seemingly more so than I was before drinking
but hindsight about the same. I came on this trip with the idea in mind
that I'd be accompanying Lucy on the bus, etc. I wouldn't say I have
feelings for her in a romantic way, however I do very much enjoy her
company.

\bigskip
\bigskip
November 10th, 2017

Day 9,

I've come to realize the experienced depression I felt last night and
now is because of a lack of use and application of my ``genius'', being
the subconscious pattern recognition that is the source of brilliant
ideas or acknowledgements of the concealed reality. (By ``genius'' I'm
defining a mental process, not boasting about a personal genius, hence
the quotation marks). I believe now that the genius is vital to one's
sense of worth and personal identity. I need to pursue activities that
activate and use the genius in order to feel I have an individual value
again. These activities are also likely the things I'm naturally good
at.

This is later in the day now. I should mention that the depression was
allowed, however not initiated, by lack of application of the genius. My
emotional state prior was that of an underlying depression however that
depression could not be pushed to the side with immediate emotional
response and self-deception (ie ignoring the impending reality or
emotion by populating your existence with action and very superficial
emotion) because I was not properly accompanied by the friend who
convinced me to come in the first place.

Also, regarding attaining women through fulfillment of one's life, the
most immediately ascertainable aspect of a man is likely that he is
happy in the immediate level. Women, and likely the men as well,
perceived my marginal unhappiness and this associates with a lack of
confidence, somewhat in yourself as the unhappiness is internalized and
not blamed on a separate entity and, somewhat in your decision and life
direction, that you know at the very least what is best for you. The
practical application of this is conscientiousness -- think about what's
next and don't do what you don't want to do! Conscientiousness will
ultimately lead to higher perceived, and real, confidence.

``Judge people by who they are today, not by what you know of them from
the past.'' The guy from the kibbutz appeared to, over long periods of
thought and interaction, have discovered many important aspects of
maintaining and developing relationships. One of those things I could
gather was the above quote. It seems obvious that people are constantly
changing yet we often may not acknowledge this in our relationship
behavior. It is thus important to continuously run a check for who it is
you're talking to. Eli today is different from Eli yesterday.

\bigskip
\bigskip
November 11th, 2017

Day 10,

The fact that my lack of a feeling of satisfaction or fulfillment in my
day is due to my lack of use the genius is very clearly apparent to me
now, so much so that it seems necessary to make an organized effort to
fine fields that utilize the genius (of me). Without this genius my mind
feels vanilla, and empty, as if a blank piece of paper. Not clear or
transparent, but nothing in a space of nothing. The fulfillment and
satisfaction felt when using the genius makes me consider that it may be
part of the soul and intelligent human influence, despite it being
intuitive and seemingly subconscious in operation.

I had a glimpse of it last night during the meet and greet, I was
discussing and it just appeared. I'm thinking back to when I would stare
out the window and write the videogame ideas on my white board. That was
seemingly a controlled and forced application, perhaps something
similar, being a distinct goal of knowledge or understanding rather than
a simple improvement of knowledge, might trigger it again. Another point
is that it seems to emerge when my mind has had an abundance of
information to work with.

-unsurprisingly, it just occurred to me that I experience this
activation in talmud class.

\bigskip
\bigskip
November 12th, 2017

Day 11,

I came in my sleep last night but further I ate junk food, went on
twitter on the bus, and indulged in bullshit. It all must correlate.
Strength of the groin is strength of the palate is strength of the mind.
It is time to apply the more abstract principle behind monk mode.
Unproductivity, in any means, must be eliminated. Being with friends,
past the extent of maintaining and strengthening relationships, is
unproductive. A kibbutz trip is unproductive. Lolli gagging in the shook
is unproductive. Even this journal is in large part unproductive. The
main concept can no longer be ``not to do this'' but ``you must do this
and those things impede that goal''. Idea: begin to analyze and develop
a theory for social interaction among teens. Conceive (or really
observe) the incentives and goals behind social action and apply a sort
of game theory to that.

\bigskip
\bigskip
November 14th, 2017

Day 13,

Since I've been eating not crap but lots of dates and enjoyable foods,
I've noticed I'm tired like I was pre-monk mode, feeling the lack of
immediate stimulation. I need to actually start meditating and work on
programming as a genuine priority. Programming seems, at this time, to
be the one outlet for what do I do with my time.

\bigskip
\bigskip
November 17th, 2017

Day 16,

Profound day. I was about cum, had actually planned on doing so, but
then I fell asleep. In the morning I decided I would end nofap unless
something on the subreddit could convince me otherwise. What I found was
a general theory that is not quite fleshed out by the author but
something that seems to be correct for its practical implications. It
claims that our body has limited resources for operation. When we
masturbate or engage in immediate gratifications, our energy is put
towards those means and necessarily away from our minds. Over time, this
changes the brain to respond to incentives of limiting that resource and
we lose or weaken mental abilities. The way to change this, and the part
I most believe as useful, is that one must abstain from the supposed
energy sapping immediate gratification behaviors of masturbation, social
media fucking off, etc. and then meditate to direct the now extra and
unused energy towards the brain. If this is not done the energy will
simply try to release itself through the usual means. Monk mode
necessitates meditation. From now on I'll follow this regimen. This not
only gives me ample reason and understanding not to fap, but also
provides for me a potential solution to the missing piece of the shit
life puzzle, partially solved by monk mode. The implications of this are
also semen retention, meaning I must actively remain a virgin. At the
very least, these benefits will make it so social gatherings are ones I
truly enjoy, not ones I attend to further the possibility of sex. In the
back of my mind I'm thinking that I'll try not to get sex and then it
will come to me and I'll be happy, but that cannot be my thoughts. Being
offered sex and declining must be a feasible reality. I must decline
sex. This seems impossible to me now, but I will accept this fact and
hopefully my body will respond to this acceptance. This is the road for
me to greatness. The glory I was emotionally addicted to throughout my
childhood will only be realized by relieving myself of these very such
emotional addictions. Glory must be expressed in awe of the world rather
than awe of yourself. Become secondary to an existence that you work to
fit into. I feel as I'm writing this now a potent emotion, almost as if
I want to cry. I think I've encountered something divine. I'm being
careful with my words here not to abstract and emotionally misinterpret
reality. I feel a physical tension in the top back of my head, slightly
uncomfortable in pain.

\bigskip
\bigskip
November 18th, 2017

Day 0,

I fapped tonight. I need more mental data, nofap could still be an
unnecessary product of monk mode, with a large downside of constantly
thinking of sex all the time. Right now I feel very tired, though it is
quite notable I experienced horrible pain after ejaculation. I feel more
prepared now for Monk Mode take two. Next Shabbat I will make a decision
on whether or not to maintain nofap. This time, I must 100\% meditate
every day. I believe the activation of the genius is necessary to direct
the energy in the above theory to the mind. Monk mode is certainly the
future. Looking back, it was a vital first step.

\bigskip
\bigskip
November 19th, 2017

Day 0

Fapped again, not much to say. Meditated though, was very useful. I'm
going to wake up at 6:30 with cold showers and meditation starting
tomorrow.

\bigskip
\bigskip
November 20th, 2017

Day 1

I definitely noticed a mental fog when meditating. Nofap seems to be
100\% necessary, along with monk mode in both food and behavior.

\bigskip
\bigskip
November 21st, 2017

Day 2

Felt quite sick this morning, didn't meditate or cold shower, went back
to sleep for an additional 3 hours and went very late to first class.

\bigskip
\bigskip
November 23rd, 2017

Day 4

7 habits is getting juicy. Proactivity, referring to internal onus of
control, is an obvious habit but it's distinct acknowledgement is
probably beneficial. Also, I'm scared that these valuable habits may not
resonate, that in thinking about them I'll naturally be inclined towards
other bullshit self-improvement schema and thus the entire concept will
collapse as nonsense in my head. Perhaps I should tread carefully,
thinking in very basic logical abstractions. I've seemingly lost what
initial intuition I had of my thinking in the matter. I've thought of
something else just now though. Sort of in line with daily planning, I
can articulate what I can do that day to benefit myself. My success thus
far has been reactive to negative emotions. Instead of working to be rid
of negative emotions resulting from stagnation and poor life projections
I can work for positive benefits of good feelings upon being productive.
This would change self-betterment from a negative to positive benefit,
which would make it more consistent This makes the most sense, it's
interesting to me why I haven't realized this till now.

\bigskip
\bigskip
December 2nd, 2017

Day 1,

I've essentially broken monk mode, played videogames on phone in
Netanya. I've been feeling shit and unproductive lately. Physically I've
been quite well considering the inflamed lymph nodes and cough along
with cold showers. In my mind, however, I feel the same emotional dread
and self-pity/sadness that I believe prompted me to start monk mode.
This was triggered by my conversation with Matt's dad, which I reckon
caused me to consider and confront the inadequacy of what I've
accomplished while being in Israel. I have a lot of guilt over that, and
it feels like game development may be the only way out of having
accomplished nothing (by ``feels'' I do exactly mean feel. thinking
about game development relieves an anxiety, along with giving some
excitement perhaps because of the envisioned success or because of the
resulting lack of general anxiety about not being assured that I will
live up to an acceptable standard of success). If I develop a game, I
can say I did something. Right now I would ask God for help, but it's
probably there in the prayers, so I should really learn Hebrew instead.
It seems necessary to me to set two goals now that must be met every day
before considerations for grades or Hebrew. 1) study the prayers and
what they mean, translate and break down the Hebrew. 2) do the fucking
programming tutorial, one complete video per day. My mind needs to be
emotionally rooted in the reality of productivity. I've just observed
the lack of habit. I need to then be very strict with these goals so as
to develop the habit. I must accept that I will study the Hebrew, will
do the programming. Not just in symbolic language where the real action
isn't fathomed, but in complete understanding and knowledge of the
implications. This is my life now, like gym is my life now.

Something else has just occurred to me. I am most able to achieve my
goals and complete my intentions when I hit some sort of marginal or
local rock bottom. This is because it is the potential emotions of these
realizations that give me a sort of energy or force to drive toward my
goals. Additionally I think faster and feel like a superhuman described
in so much self-improvement literature. It isn't just a matter of
maintaining proper physical existence, or any specifically physical
existence for that matter. It is maintaining properly the goals set out
for oneself in their, to some extent, subjective value system. But
further, there is doubt and thus less proper maintenance in a value
system not derived from God. Thus, the extent of this contentness
phenomenon will be limited by the coefficient representing the
proportion of the used value system that is derived from God. I then
need to pray every day to reinforce the value system underlying the
marginal decisions I make within the outlines I've created in my life.
Further, praying provides the realization that ultimately triggers the
emotion, but every day. What I feel right now should be how I feel at
all times and it is prayer that achieves this. Prayer gives the
realization and emotionally power only otherwise derived from failure
and self-analysis.

Our capacity for learning and retaining knowledge is not limited.
Remember 20 words in one day doesn't mean you can't remember 20 more
that same day and retain them. Theoretically the storage of the brain is
incredible. Be aware of, know, pay attention to, and learn everything.
It is free knowledge. Lucy remembers all the terms she hears, to some
extent, because she knows from experience the mind is not limited in
this way. That is the hypothesis, I'll implement it and see if it's
accurate from now on. If I believe more confidently than I do now that
for some reason this hypothesis is wrong, I'll come back here and
correct it. (Edit March 6, unsure about this now, in truth haven't
considered it in a while)

\bigskip
\bigskip
December 12th, 2017

Win Hoff, or perhaps monk mode 2, has made me more in tune with my mind
again. I questioned what I'm waiting for, and it occurred to me yet
again I'm waiting for value in my life. I still haven't done anything
meaningful, and on a side note a girlfriend wouldn't change that. I need
to make money. Value as determined by dollars someone else is willing to
pay for what I produce. Sure, I wrote an essay, but grades aren't giving
me value. Sure im working out, but unless I want to work in construction
I still don't have value. I have the long term tools to work towards a
life of value, but at present am producing nothing to pay back the debt
of societal investment. I imagine when I first make money, not within an
employee job for I would likely encounter the same issue, but within
producing a product that others value, that I will experience great
euphoria. It can't be just some product, however, it must be something
that I am uniquely good at, something that utilizes my genius. This
reaction is based in that it helps me achieve something of the truest
value, intelligent children with ample opportunity.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Daily analysis journal.

\bigskip
\bigskip
December 17th, 2017

Rule 1, No distractions:

Failure 1) This morning I spent a little more than an hour reading about
net neutrality. My justification was that I was becoming informed, that
it was research, not a waste of time. In reality though this knowledge
has no worthwhile practical impact on my life nor does it get me
anywhere closer to my long-term goals.

Solution - before doing anything questionable, especially on the
internet or in a groggy, not 100\% state, question and prove to yourself
if that action will benefit you in light of your long-term goals. If
yes, you may proceed. Otherwise, no.

Failure 2) More innocent this, spent collectively an hour searching
online for injury's. I'm going to see a doctor if it doesn't improve,
ultimately this research was useless.

Solution- don't research injuries. ``research'' of WebMD bull shit is no
longer exempt from the tech distractions category.

Rule 2, Health:

Completed

Rule 3, productivity

I didn't finish Hebrew homework within the 3-hour timeframe and then
didn't have time to do an important thing. There was a lot of mundane
things to be done today -- cooking, gym, gym recovery -- that wasted a
lot of time. Programming was completed, but I wasted a lot of time
fiddling with the themes.

Solution -- If you sense yourself wasting time, stop. Find an immediate
solution to the largely unimportant issue and continue. Also, try
rushing through the gym procedure next time. Waiting for the perfect
moment for everything takes too long.

Conclusion

Rule 1 -- wasted time today, but is somewhat innocent.

Rule 2 -- Except for shoulder injury, no issues

Rule 3 -- need to be more time efficient, otherwise good job. I
struggled through Hebrew.

\bigskip
\bigskip
December 18th, 2017

Rule 1, No Distractions:

I was doing quite well earlier today, but as I progressed on completing
my Talmud paper I went on Facebook for an hour than talked to Ellie and
Evie for another hour and a half, getting to sleep very late.

Solution: do a concise greeting then unapologetically say ``I can't talk
right now, but I want to catch up after I finish this paper''. Further,
if mentally fatigued, take a walk or sleep. Do not go on Facebook,
Jewish argument is unproductive all the same.

Rule 2, Health:

I got to sleep quite late because I was talking to Ellie and then
Richard. Again, unapologetically say I need to go to sleep, let's talk
on the morning. Articulate this need but acknowledge that you want to
engage with them.

Rule 3, Productivity:

I did programming and Hebrew, though I grew tired and disenfranchised
towards the end, then I did Talmud paper. I ultimately got it done,
though I wasted time. Again, take a walk or sleep. If something is
wrong, acknowledge it and find a solution. Do not just sit there and
Facebook, or go get a snack or something -- that's another form of
Facebook.

Overall

Rule 1- did crap, need to address problems and stand my ground. Even if
tired, you must not conversate before work.

Rule 2 -- got to sleep late, same principle as above

Rule 3 -- I got my work done, but could do more.

\bigskip
\bigskip
December 19th, 2017

Rule 1) I again spent some hours in the morning on bullshit. New rule,
when I wake up in the morning I either a -- go back to sleep, b --
immediately make a hot drink, or c- do 10 pushups. I also find myself on
Facebook just when I feel dead and it seems like a decent thing to do. I
should stop this, even though I'm getting my work done, it is still
unhealthy. I can check Facebook for specific events and note if they are
achieved. Otherwise, I must go for a walk, just to laundry and back.
This means if I have a craving for Facebook I either work or walk. Also,
I find myself getting hot drinks and the such during work when something
doesn't feel right. These should be prepared in advance. Caffeinated tea
is permitted at all times now for this purpose.

Rule 2) Ate a few too many carbs, maybe 150g, otherwise it was fine. The
number itself is not exact so no pressure, but no more than that. It
should be centered on 125 still. Also, need to better plan my workouts
with my meals. 4 hours minimum between protein and workout.

Rule 3) Didn't finish Hebrew in time, largely because It seemed an
insurmountable-esque task. In the future, immediately when you get home
vet if the homework given is good. If not, make your own with disk and
texts in aleph book. Listen to the disk and read the text on bus rides
and such. Also, am adding translation to daily thing, 30 min. It thus
must be accomplished first thing when I get out, after programming.

\bigskip
\bigskip
December 28th, 2017

Just a thought, all ideas are only truly understood when they are at the
highest level of abstraction possible without losing any significant
details. If two ideas can be consolidated into a broader level of
abstraction while still specifying those specific things, then our prior
understanding was limited. If I know of apple only as apple and not as
fruit or food or organic matter etc. I don't understand as well as I
would knowing those concepts. Similarly, if I know a behavior, say
smiling, as only the act of smiling and not as a more abstract principle
of being happy, I don't understand smiling. This understanding of
understandings is necessary for how to win friends influence people.
Ultimately, Carnegie describes a surface behavior. Yes, he describes the
mental state of the performer, but not the natural motivation behind the
performance. This motivation is the principle. Applying concepts of 7
habits and this book, identify the principles using Carnegie and assume
those principles using 7 habits

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\bigskip
\bigskip
March 6th, 2018

Day 1,

5:00 am

I just consolidated my Journals now because I wanted to look over them
and reflect on what I wrote. What has struck me, and which is horribly
obvious to me right now in my lack of eloquence, is that I've regressed.
My mind is blank. I have stopped thinking really. The genius is gone,
but even the earlier foundation for the genius is also gone. I had maybe
a small glimpse in recognizing the separation of my mind several days
ago, but even that took lots of time looking at a whiteboard. I've since
been desperately latching on to that one moment of possible clarity,
progressing nowhere. I can only reason that I suffer the same ailments
of the mind that prompted the first monk mode. I feel I've descended
into normalcy. Sure, my social skills have improved I suppose but they
were never really broken -- I was just unwise. Along with this miniscule
wisdom during the break I've reacquired mental fog. My mind is empty,
blank. I have nothing to say, no connections to make. Utilizing the
genius is strained. ``Why make yourself desolate?'' -- because what I
presumed to be desolation is freedom, I know not true desolation. The
middle path is not to be confused with horrible myth of a balanced
lifestyle. I refuse to let my mind become a reactive, empty, dead sheep
(not primarily in following, but in being a dumb animal, though
following is included).

\qquad Today I start another Monk Mode. I pray God will help me in
knowing my failures and avoiding the same mistakes. I will adhere to the
necessity to write in this Journal as I adhere to my belief in Judaism.
Even now, one can easily see the similarities in my simple-minded
conviction with that of the stereotypical naïve protagonist, or perhaps
of a 14-year-old boy. This is all the more reason I must be strict with
this monk mode. I've tasted the nectar of genius and to lose it is
unthinkable, though only in memory as I can't comprehend its value in my
current state.

2:14 pm

I do think I feel different now, not much improvement of mental fog that
I can identify, but I feel more relaxed. The path forward puts me at
ease. I would also say my countenance is a stern one of conviction. I
also seem to be taking my actions with a slowness, as if I don't know
what's right so I won't make any rash decisions. I know much that is
right, my knowledge is just limited. I should subscribe confidently and
unapologetically to what I know, and seek to find what I don't when its
relevance demands its knowledge. This thought will be reconsidered in
end of day journal/analysis and a practical behavior change determined
if appropriate.

\begin{quote}
*I do agree with the existence and discussed explanation of a
``slowness'' and think it's rooted in a sort of apologetic mindset. This
should naturally subside as my confidence increases. If my confidence
doesn't increase, then I'll address that and, therefore, the
``slowness''.
\end{quote}

9:58 pm

I successfully adhered to my rules without much difficulty, if I'm
honest. As a result, my productivity wasn't anything remarkable, but was
at an acceptable pace. I spent a lot of time fatigued, napping while
awake, just staring into nothing. I imagine this means my mind is
healing. As I continue my energy and vigor should naturally return.
Immediate gratification seems like poison to me. The thought of it is
associated with headaches and mental ailment, as if classically
conditioned to dislike a food from bad experience. I feel as if I can
readily and easily make progress on my mind by sticking to this monk
mode. I'll gradually become more efficient and refined as I maintain
this pace.

\bigskip
\bigskip
March 7th, 2018

day 2:

12:41 pm

I'm a tad sick but will completely ignore it, except for
non-interruptive remedies. Apart from that I feel alright. I grew very
anxious doing my Hebrew homework I think because my surroundings weren't
thoroughly organized, too much potential energy. As my confidence grows
though this shouldn't become an issue.

\bigskip
\bigskip
March 8th, 2018

day 3:

3:40 am

Fuck me upside down, ignoring the sickness was a bad idea. I'm now very
sick after going to gym.

\bigskip
\bigskip
March 12th, 2018

day 1:

7:11 am

Perhaps it's a bit unfair to myself, but I reset the day counter since I
was watching movies while sick -- even though I maintained nofap 6 extra
days than the day counter.

7:54 pm

Just had an idea while avoiding laughing and trying to be productive by
reading software engineering book. - When reading with music it feels as
if the normally present negative space that allows for consideration,
manipulation, understanding, and critical reading is filled by the
music. You can immediately easily assign abstractions, understanding
what is being read. This is why some like listening to music while
studying. They're filling the negative space to make the reading in
question sort of cookie cutter, acquiring a face value understanding of
what is being said and nothing more. This may be faster but lacks true
understanding. It is this method that most easily and immediately
enables you to know and follow the route while ignoring everything in
the map, blocking your peripheral vision with music. This is consistent
with college kids listening to music while reading or studying. They
don't need, nor want, to look out the window and the surrounding
landscape. All that matters is the route I'm taking and recreating this
route, though no true knowledge of the map is gained. A line, a route,
has no area.

11:53 pm

I ate some cereal with milk today although I was specially allowing
myself some carbs. Tomorrow this stops, will gym Wednesday normal
schedule. I also didn't do any Hebrew homework or translation. Today was
a busier day on top of seeing a need and working most of the time on
restructuring the code once more, reorganizing the classes. This is
causing me anxiety since I feel unsure of how to reorganize classes
still. What responsibilities to what, what variables should I include in
each new class, etc. Because I'm unsure, continue reading and finding
sources. Ease your anxiety in the knowledge that this change is
inevitable and doing it now is better than later. I will not have a 2000
line player class. It also seems fit I should make a sick regimen for
when I'm sick and how to be most productive during that time. Still
unsure of game reorganization as well.

\bigskip
\bigskip
March 13th, 2018

11:30 pm

I'm kishing the days until I'm fully healed. I'm not being entirely
strict with the monk mode since I'm sick and eating garbage kind of
taints it. I also haven't been meeting my productivity goals, instead
seeking to alleviate the anxiety of my messy code by restructuring all
the classes and everything. I can definitely see though how, in the
current code I'm writing, I'll be able to write it sloppily first then
refine it later. There is some concern though with GameMap not
representing a game map but the game map and all the other problems.
Player won't be a player but the player. I'm thinking I shouldn't
include the changing of the game map in a GameMap class, or at least
remove the list of all GameMaps from it. But then should the changing of
GameMap to a different Map entirely be in the class itself or in another
class of something like MapDetermination. No, it's not different game
maps but different Map files so we're good. I'm drunk so journal isn't
so successful. Will stop now, night night.

\bigskip
\bigskip
March 14th, 2018

11:30pm

Im hoping I can start counting days after tomorrow. I didn't do Hebrew
homework tonight and I didn't do translation. I was a bit preoccupied
with programming though, but now I should be settled into a context
where I'm not existentially considering the whole thing, but can simply
work and apply in one aspect. I just need to do a once over my class
allocation and which classes are accessing/changing what, but I should
be ok. Once I start counting days again I'll be in normal routine.

3:58am next day

Seidel also fucked me tonight. I believe I decided to go because of
emotional appeal but also because of allowed flexibility. I think the
friend rule should be a limiter, not a minimum. Additionally, I should
plan for the late nights in these excursions as well. To maximize my
life performance these things need to be planned. No 2 hour relax time
after school to do whatever I want, that's bull. Day needs to be planned
with objectives in mind and opportunistic allowance determined from a
weekly context.

\bigskip
\bigskip
March 15th, 2018

7:07 pm

The sides of my throat are now irritated, not the throat but the sides
-- strange. Two tasks are in order, and I need to/ will do them tonight.
First, I need to denote a sick protocol I can follow. Something
requiring a treatment/remedy once for every waking hour. Second, I need
to compile a nofap motivation list in this journal. Nofap is broken
because one has lost awareness of their motivation and superego,
awareness of god. This state represents a split in the psyche, it must
then be immediately consolidated by reacquainting oneself with this
awareness. Thus, I'll put down all the motivations behind nofap, which
will restate my goals, reacquainting me with God in the meager capacity
in which we're acquainted, while demonstrating the direct connection to
nofap.

Sick protocol

-at the change of every hour must perform some remedy to your ailment

-can eat carbs but no candy, limited sugar intake as well

-if mental state is impaired, productivity goals are suspended.

-no Netflix or aids to existing.

-must sleep a lot. If tired not allowed to go out nor do anything but
sleep.

\bigskip
\bigskip
March 16th, 2018

4:48 pm

I adhered only hecke to sick protocol, and only did programming. I
definitely let myself go and I 100\% think it was food that did it.
Starting Sunday I'll be strict about what I'm eating again and on Sunday
I'll start day 1. I'll also allow myself Netflix and the such if I
absolutely need it, but if I get an erection at all I have to take a
cold shower in order to resume watching. That is the contract.

\bigskip
\bigskip
March 18th, 2018

day 1:

12:32 next day

I've gone to sleep quite late tonight, though I woke up later so it
works out. I felt a bit sick but was able to overcome it and workout. I
definitely wasted time today, meandering and waiting. Also I'm feeling
the super powers a bit but not a lot. I think I'm maybe starting to
flatline. Urges have been, for the most part, under control. Im somewhat
confident I can avoid wet dreams. I don't want to lose super powers, it
truly is a consequence of not living in reality. I must acknowledge my
reality is I will not experience sexual pleasure for a very long time,
perhaps not even a year. I don't need to find a girlfriend, but I do
need to be successful and perhaps I may meet a person whom I can spend
lot of time with. If not, I'll focus on programming and success, the
yooj. If the time comes that I'm older and still a virgin I'll ask Dad,
see what he thinks. I should be ok so long as I don't obsess over it. If
I can become content with no sex it shouldn't skew my sexual desires.
Really I have none right now, I fathom that sex would be pleasurable but
no type of girl is so especially appealing.

\bigskip
\bigskip
March 19th, 2018

day 2:

10:16 pm

So tonight I went to seidell and had chips and beer and carbs. Those
were most certainly pleasure foods. I will start gluten free tomorrow.
Carbs will come from brown rice or the pita allowed until next Sunday,
just what I've already purchased. But, something much more profound is
that I've come to realize I'm hanging out with Richard, forcing myself
to go to jeffs and events I don't want to do, because I want friends and
I also want to be cool. I was fixated on being alpha like a delinquent
when I should fixate on being alpha like me. Find those who share your
interests and become friends with people who matter. Don't conform,
don't become part of a community, don't be alpha, be you. Now, there is
the concern that me is old beta self, but there is a difference between
plain alpha and confidence. I shall be confident in being me, that
is\ldots{} I've just realized I don't really know what values regarding
other people define me. Should I be nice, helpful, tough, overly
confident, joke to have a good time. I've been avoiding assessing a
trait by mimicking successful ones, but ultimately mimicry is mimicry.
This is now where Maimonides comes in, The key is the middle path.
Should I be nice or tough -- I should be both when appropriate, tough
when someone displays malice, stupidity, or harmful ideas and nice when
they seem good-natured and well intentioned. I should joke when
appropriate, but be serious during serious matters. I should express
humility in knowledgeable matters but confidence in values.

I also have a suspicion that quizlet activated the same immediate
gratification response in my brain, perhaps this is why I'm sluggish
lately. And perhaps there is a value to nofap reddit, but this value
must then become a task, and relegated to a specific time frame with
goals for effectiveness in its benefits. Reddit will now be accessed
only on my computer and only during a specified time slot. For the next
week, however, I will not go on reddit at all. I need to first go to the
opposite extreme before approaching the middle path.

\bigskip
\bigskip
March 20th, 2018

day 3:

12:36 next day

I feel much better acting more myself, however I did go a bit nishech
when talking to Ethan. Again, the middle path is key. I shouldn't be
joking to much, but seriously talking of life and things of significance
with a jest here and there. The average over an extended time is
irrelevant, it must be an average over a very short duration, maybe 5
minutes. Also, confidence in values -- humility in knowledge. Also had a
bit of an argument with momzair. I think I need to be more genuine with
her with my criticism. I tend to hide what I'm really saying, quite
effectively, but it might still show and lead to frustration. It's not
like momzair doesn't do that either though, shes far worse than me with
that.

\bigskip
\bigskip
March 21st, 2018

4:25 pm

So I've just gone on Reddit when I wasn't supposed to and spent time on
crap. On a side note though, I've realized, though not for the first
time, that I'm assessing people's value and then greeting them with a
forced effort based on that value. I should be assessing who they are,
and greeting them based on that. If some is looking needy I should be
nice, if someone looks confident I should be happy. I also found myself
to, again, be quite chirpy. Well, not true. Richard doesn't like to talk
at all, so when I talk to him I ignore that aspect. When he genuinely
doesn't want to talk, then I become annoying. So, I should allow him to
talk to me, and engage him well, but from now I won't prompt
conversation.

\bigskip
\bigskip
March 22nd, 2018

day 5:

4:37 pm

So I didn't journal at night last night because was drunk and forgot,
but I had Mac and cheese and smoked a lot of hookah. My lungs were
rather nigger this morn and when I went to the gym it got worse, but I
was alright in the end. I fucked around on Reddit for an hour because
was tired then napped for 1.5 I think. In the future I should go to
sleep immediately when tired. Nofap reddit definitely has value,
specifically in the Valhalla motivation memes, but this value has
diminishing returns. What I'll do is one session at the end of the day,
not before bed, for 30 minutes.

10:49 pm

After programming I basically broke. Was tired again, lost energy. It
could be the fact I went to the gym and was tired, but I also did more
reddit today that before. Reddit must be the link. I don't need their
motivation. I already have my own. What they say will only consume my
time at this point. I am done. No more reddit.

\bigskip
\bigskip
March 24th, 2018

day 7:

7:14 pm

I forgot to journal yesterday because of Shabbat, which has been very
significant. I resigned, and mostly succeeded, to fully follow Shabbat.
I texted matt once to tell him I wasn't texting on Shabbat, and plugged
in my phone (unsure). Regardless, I spent most of that time reading and
with myself and have realized things through Faur's book based on my
previous realization of self-deceit and based on being alone with those
thoughts. Firstly, self deceit is not merely harmful to the soul, it is
idolatry. By subscribing to a false reality, a human made reality, we
are rejecting the reality of god, the one true reality. The myth of
reality only existing in our perception of reality directly contradicts
with Judaism and further encourages such idolatry. The poet, through
``charming'' (as Faur puts it) the people into subscribing to a false
reality, has them worship and follow an idol of his creation. This idea
isn't my own, but that of Philo and I likely heard it before, but this
is the first time I've truly comprehended it. Thus an analphabetic
society cannot grasp god because it cannot grasp reality, the only
domain in which we can find god, or rather what he is not.

Second, when one abandons the false idols of self deceit made to
``save'' people from bearing to experience the reality of God, there is
a darkness. This overwhelming darkness is likely the result of being
accustomed to idols of human fantasy as well as the lack of knowledge or
training in the Tora as a result. This view was confirmed when Faur,
too, referenced a darkness. When I removed all that I now acknowledged
as idolatry, as self deceit, as not a part of my future, I found that
much of my previous goals revolved around something other than god. When
I removed sex, movies, TV, pleasure of all forms other than god and
accept there is nothing but god in the ideal future, the darkness
appears. If you do not understand god and then remove everything that is
not god you are left with nothing except a faint light, so unbelievably
faint that you wouldn't even call it a light. It is a shade of slightly
redder darkness than the surrounding darkness.

It is then evident that this darkness is the true reality, completely
inevitable. But further, that it is so dark and so far from
illumination, that the prospect of going back to the idols of fantasy
and not working to illuminate it is terrifying. All of this was written
based on memory, so it isn't completely an accurate representation of my
thoughts at the time. As I read the chapters of Horizontal Society again
I will come back and edit this entry.

11:28

I don't know what happened, but after writing my journal I totally
collapsed. I ate a pizza and my stomach then hurt, I browsed reddit,
further hiding from reality, and even considered looking at the old
nudes of girls from omegle and the such, which would have assuredly led
to masturbation. I need to sleep and to be healthy. I need my mind
working.

1:47

Definitely did not want someone to talk to on omegle lol. Nearly
relapsed. Will go on Reddit now, then go to bed.

\bigskip
\bigskip
March 25th, 2018

day 8:

12:11 next day

So there's the fact that I peed out cum, nuff said about that. I also
did nothing really today. I tried doing things with the program, didn't
get anywhere, and didn't end up doing translation. Went to the gym
though. Won't go tomorrow. I also think there is a huge thing with my
diet. It's all fucked. Tomorrow and Tuesday I am going 100\% no carb.
I'll decide on Wednesday morning if I want to go carb, but I don't think
I will. Even if I'm tired and sleep all day -- no carbs. I want to be
free.

\bigskip
\bigskip
March 26th, 2018

day 9:

11:29 am

I skipped ulpan today and went on Reddit the whole morning. I didn't get
enough sleep and thought that affected me. As much as I love reddit, and
the support of nofap and the belonging of a community, I must realize
this is an internet addiction just like porn, just like YouTube, just
like fapping. No more reddit, forever. It is now part of monk mode. I am
seizing the light for myself. Today I will be no carb, today I will be
no internet.

2:27 pm

I need to make some strict and concrete rules.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  I'm not allowed to use any internet of any kind unless explicitly
  permitted in these rules
\item
  I may look up YouTube tutorials or Google a programming problem
\item
  I can check WhatsApp for new messages, however I cannot review old
  messages or images except for necessary information
\item
  I may chat on Snapchat. No viewing of stories
\item
  I may browse the mishne Tora for a very specific, productive purpose.
  Such as amassing information, or looking at his opinion on a specific
  practice to determine a rule regarding that process.
\item
  I can only read my journal directly before making another entry. This
  means not in the morning.
\item
  I can check new emails, but if they are irrelevant I must unsubscribe
  from the sender or stop reading after I realize this.
\item
  I cannot review or look at old photos except for a specific productive
  purpose or reason.
\item
  If there is something productive I want to do with an unknown time, if
  it takes 15 minutes or longer I give up on it unless it is necessary.
\item
  No Facebook except to RSVP a certain event.
\item
  No Jeff unless I can demonstrate it is productive. Netanyahu is
  productive in a few capacities. Barbecue is not in any.
\item
  Hanging out with friends isn't productive, however it is necessary. I
  am allowed 4 passes per week to do something that is not productive,
  but with friends. I may use them at my discretion. Ades counts as 1,
  Ben is number 2. These passes exclude Jeff events except for parties,
  for which I may use them.
\item
  On Shabbat I may spend as much time with people as I desire. The
  mandate is that I don't escape to reality, I can, however, be as
  lethargic as I desire, assuming I complete the Shabbat tasks of prayer
  and Friday preparation.
\item
  I cannot go farther than making out with a girl outside of a serious
  relationship. Hands may roam, but not under clothing.
\end{enumerate}

8:24 pm

I'm feeling better overall with my rules. More free and more pure, as
always when I start monk mode. Remember to commit to your promises to
yourself. If I say I'm gonna be nocarb for today and tomorrow, God
damnit I'll be no carb.

3:28 the next day

I stayed up late tonight talking to Matt, I really hope he sticks to
this plan or shows similarities to my efforts, so that he might have my
success soon. Regarding me, this was a rather successful night. When I
was hanging with naco and ``the boys'' I acted very well and had a good
time, naturally. Everyone laughed at my jokes and I was serious when I
should be, and funny when appropriate. Story telling may still be an
issue but we all had a good time last night. I'm also happy I made
progress on the prayer translation again. Slowly slowly I'll become
closer to god. I also stuck to my diet very well. I had salads with
hummus and the steak with veg. I'll shoof haircut tomorrow, see what I
want to do. Valhalla is on the way.

\bigskip
\bigskip
March 27th, 2018

day 10:

3:30 pm

The rules seem to be performing very well. Although I just ate and I'm
going to go the the gym very soon. We'll see the effect on my stomach.

9:37 pm

I didn't end up going to the gym, will go tomorrow morning after a rest
and meat plate gives me strength, hopefully. I also noticed, again, I am
fucking smooth as fuck. I can talk to people and I'm cool. Of course,
once I got into dodgy territory with the whole reality thing it got a
little out of hand, but now I need simply avoid such conversations until
I'm knowledgeable proper. Knowing what I need to do is very simple now.
I talk to people and have a good time and can tell that those who are
awkward are below me in this scale. Though, some self reflection now, I
shouldn't think in such a way. No one is below me, we're all made in
gods image, all with capabilities and so forth. Only those with improper
values should be shunned. In a concluding note, life is good. Life is
great, full of possibility. If only I was like this through highschool.

4:12 next day

Woke up at 3ish and have for some reason been stressing about rutgers. I
came up with a good essay idea though. To describe the process of
finding a solution as a cat chasing the mouse. The essay could be titled
``the little mouse in my brain''.

\bigskip
\bigskip
March 28th, 2018

day 11:

8:25 pm

On the bus back from tel Aviv. I haven't done much productively for past
3 days, though it is vacation time so it is permissible. I'll keep
reading at the very least. Matt also seems to be bullshitting. The
obsession men have with girls as if they contribute to happiness is
total nonsense. I think I'll stop engaging Matt as much and let him find
his own way to get his shit together. Like a parent with a child gone
astray, the only thing you can do is let them find their own path.
Hopefully his positive regard for me is enough so that my anger didn't
uproot the seeds of success from monk mode and everything. As for
myself, the one thing I must do every day is work on translating the
prayer. For now,my source of translation will just be sefaria, but I
should find some artscroll pictures or something.

11:21 pm

So I ended up heavily smoking hookah with frenchy. I feel impure when I
do this. I've stopped it in monk mode.

4:34 next day

Just had a wet dream. To impair the mind is to submerse in weakness, to
turn off the light. No drinking. No hookah. I will have an unimpaired
mind.

\bigskip
\bigskip
March 29th, 2018

day 12:

4:50 (approx, forgot to timestamp)

After shopping at the shook I feel very fatigued. I would reason its
because of the hookah. I am now adamant in never doing hookah again.
Hopefully I'll heal during the weekend and become productive again.

7:36

It just occurred to me I've lost my superpowers because of the wet
dream. I must now commit to no women. I'll be shomer negja outside of a
relationship. Girls need to be out of my life completely as entities
with a separate status from men. If I meet a girl and become friendly
with her enough that we mutually agreed to start a relationship, I may
think of her and only her as the female I consider now. Life is what's
important, nothing more.

12:20

Albi told me of book bigger leaner, stronger. Will get for Kindle.

\bigskip
\bigskip
March 30th, 2018

day 13:

3:59 pm

Was feeling sick today after tubi last night -- very sick. No more alc
when sick. Also, I'm allowed to get with gs when out, but no more than
that. Even still, it Shou be about for actually getting to know people.
I also spent most of today doing nothing truly productive. I hecke slept
until 11, then went on Reddit and looked at nofap videos on YouTube.
Then I ate cereal and carbs. I can eat carbs in the meal, but under no
circumstances can I eat cake. I don't eat desserts, sorry. I'll spend
the time with reading and discussion.

\bigskip
\bigskip
March 31st, 2018

day 14:

7:15 pm

I was sick and fatigued for most of the holiday, and they were speaking
Hebrew so I never chimed in. The correct thing to do would be to run the
conversation with English, but do I have such authority in a house where
I'm a guest? The whole guest dynamic seems a bit shit to me. Too much
politics and too much, ``what can I do for you m'lord''. Should guests
only be people you already know? Or should there be a way of getting to
know the guest properly after their invitation? Additionally, I think if
one is hosting, the topic of conversation should be something all
members can participate in. This requires contentful discussion
probably, and thus people who seek and discuss content. What is
conversation? There are the initial confirms to convention to situate
the relationship, but once that exists what do you discuss? It is
probably based off of good principles, like getting to know a person and
then providing the insights and perspective that you can.

1:17 next day

I thought to myself when I went out that shomer negia is ridiculous, but
didn't I think no sex outside of a relationship was ridiculous too. My
life will not improve by getting with gs. My identity and my value come
from my accomplishment, not my ability to get girls. Getting girls is
worthless. No more. No more girls dominating my life. No more wet
dreams. I'll touch girls for hand shaking, greeting hugs, but that's it.
No romantic anything with girls. No relationships until I find a girl I
would marry. Girlfriend means nothing.

\bigskip
\bigskip
April 1st, 2018

day 1;

1:30 pm (approx)

I've reset my counter again because reddit is self deceit. I lack
friends. Just like porn provides an ideal and completely unreal mate, so
does social media provide ideal and false friends. People with whom I
associate on reddit, with whom I make jokes and engage in behaviors
normally exclusive to friendship, are simply not real. This isn't to say
they aren't real people, but it is not a real friendship. I don't know
these people, they aren't my real friends. I assume them to conform to a
mold, an ``abstract class'', of a friend with the minor differences and
uniqueness they do present. My mind behaves as if I'm hanging out with
the best of friends, with whom I share values and have a good time, but
I am utterly alone. Real friendship and real acquaintanceship does not
work like this, just like real sexual practice does not work like
pornography.

This morning and last night I wasted far too much time on reddit. Hours.
I was escaping from reality to the world of imaginary friends, who I
don't even know, just like an imaginary online girlfriend. Both parties
are simply providing a service to the other, the deceit of friendship or
the deceit of romantic love. A medium for us to deceive ourselves. Man
should not be alone, but to be with false friends is only to secure your
loneliness. When necessary, from now on, I will be alone. Perhaps to be
together with another I must first learn to be truly alone. If I make
myself tolerable to myself, If I, as my only friend, can occupy myself,
then I can surely bring value to others. We should be strict with the
tora so that we may plan ahead in light of these restrictions with our
natural incentives. The natural incentive is to have friends. I will be
strict with no reddit, acknowledging I should not be alone, because
reddit will take me no farther from loneliness than porn will from lack
of sex. Listen to your body, assume its conclusions as truth, and it
will lead you to the correct path.

I don't know why, but I'm even getting dopamine from this. I don't
believe its because I think someone will be reading it. I think I'm
simply coming to love myself. My conclusions make me proud of myself. I
feel a deep, chest pressing happiness. Not because my life is ahead of
me, though I'm sure that happiness will come with time, but because no
longer am I imprisoned by this form of self deceit. With toil and time I
will rid my mind of these idols, and come to embrace the world of god.

2:24 next day

So I completed all the tasks, although I only meditated for 8 minutes,
did little Hebrew, and didn't translate much at all. What I did do,
though, is situate myself in a context to accomplish those things
better, tomorrow. I properly meditated by experiencing and observing, I
niggured out the sepharia, and got a decent understanding of the hebrew
I need to do. I felt much better today, both in sickness and in mind. I
definitely should not go to tell aviv in an Airbnb, but also I
experience fun and exciting shit in Israel, no? Tomorrow I'll have real
work ahead of me. It will be as much of a challenge as today was from
yesterdays existence of escape through reddit. I also am very proud of
myself. I was fixated on the Arab girls speaking English and I was about
to leave the gym. Then I said fuck it and went up and talked to them.
The pretty girl was 26 and didn't care to talk once I revealed I'm 18,
but the not super pretty one was very nice. Educated Arabs are fine.

\bigskip
\bigskip
April 2nd, 2018

day 2:

2:47pm

I meandered a little bit in the hot shower and in the morning, but did
alright following monk mode. I had planned on eating way to late and
became ravenous after programming so I ate a matza with 2 eggs and then
one with peanut butter and Nutella, not great. Regarding nofap I've been
totally urge free, which is good. I really think it's important I finish
and fix the code for the algorithm tomorrow at the latest, or else my
productivity if truly wavering. I'll give myself infinite time to finish
it, with set breaks only for eating.

3:58 pm

I went to the shook and got a fruit juice. I've also sampled some
pastries. Now my stomach hurts and I feel tired. No more sugar. Rule is
can only eat carbohydrates in a meal with protien.

9:49

I would have for sure gone on Reddit had I not stopped myself, and then
my night would have been a waste like many others. Though I wasn't so
productive in the end, I did not regress, and thank God I am still in
reality. I've been in the moat so long that holding myself out of it so
very difficult. After long though, I will become at home in reality.
Additionally I skipped Hebrew and faur tonight. I feel justified in
skipping faur because I'm genuinely fatigued and will sleep, the Hebrew
was just that it's uncomfortable. Again, discomfort is not bad but good,
it is to be embraced. Try again tomorrow. If I fail, then I will bring
up Hebrew again when I am situated in reality and able to withstand
discomfort on Sunday. I sincerely hope I need not wait a week to do my
Hebrew, but if necessary I must succeed in long term, even if it imparts
short term stress.

\bigskip
\bigskip
April 3rd, 2018

day 3

8:27 pm

So today I was rather productive, did everything on the list except
faur. At some point after coding for the third time today, I got very
tired and looked at a specific youtube video that was in my head. I
wanted badly to go on reddit but did not. Then I invited jae over for
charoset and we ate charoset. I then had more after he left and
chocolate spread. I then became very tired and was desperately craving
reddit or any form of dopamine. I didn't partake, though I lied on my
bed for a while and decided to write this journal. I feel better after
starting to write this now. I think I'l investigate livestreaming. Once
I get this code finished and cleaned, it's streaming time baby.

10:21

So I google streaming advice then watched a YouTube video then watched
Jordan Peterson. Intrinsically I don't think there is an issue with
those videos but I know in my heart I shouldn't have. It was because I
was tired and couldn't do work, and that's because I wasn't disciplined
and ate charoset. Eat only what your soul requires, till 3/4ths full.
This is when I'm most productive. This is how I progress. Accept that
after 3/4ths hunger you won't be eating anymore, for at least 2 hours.
That's new rule, in addition to limited carbs with every meal and sweet
only at beginning or first meal. I also feel as if I may have a wet
dream tonight and I won't. I keep saying it, but I'm unsure of whether
or not I'm fathoming it. I will not have a wet dream. If presented with
an opportunity for sex I will decline, for my life is too valuable to be
hindered by short term pleasures. I have no need for such idols when the
grace of God is before me, and I before him. It is so important I make
progress with the prayers. Without them I am lost.

\bigskip
\bigskip
April 4th, 2018

Day 4,

So today I relapsed. No, I didn't fap lol I'm not that weak, but I did
go on Reddit for probably an hour. This shows me, I can't even abstain
for a week. This is just like nofap. I need to break it. If I am alone I
am alone. If I am tired I must sleep. If I sit and do nothing I shall
sit and do nothing.

\bigskip
\bigskip
April 5th, 2018

Day 1,

10:00 (approx)

Wet dream. I know exactly how it happened to. I was in the party, and
the girl was grinding and twerking. I went up to the hottest of the
uglies and grinded on her for 5 seconds, then came. Then, as if to save
me, the girl I knew through chabruta suddenly asked and became my
girlfriend, a completely religious girl. We did a sort of cuddle thing
in the dream and nothing more. No more clubbing, or rather, aspirations
of clubbing. Is a good story all that worth it? Do we really bond drunk
out of our minds? Perhaps it increases status to get girls, so I might
pursue it, but success I assure you will increase status more than
anything. No more clubbing. My values are such that I don't wish to have
any sexual interaction with girls, so I must act out this behavior. For
all the times I wanted to go clubbing, I will not go not once, unless
you count that disaster with Lucy. When I get to college, perhaps I'll
go to sophomore dorms. I need real girls if I want them, not whores and
sluts. If I see girls dancing, I will leave. No Jeff parties no nothing.
Boys nights out, sure, if a girl becomes involved I no longer will be,
end of story. I'm done with this shit.

1:14

Today at the gym I felt really good, was talking to people, met Nazer,
looked good. Even though I relapsed, I still have super powers. It's
important I make friends though. Being alone -- just can't do it.
There's not enough to find within yourself, or maybe there is.

\bigskip
\bigskip
April 7th, 2018

day 3:

So apart from a single omegle conversation I stayed strict to the thing.
I watched a lot of YouTube lectures and went to meals to keep myself
busy. I'm gonna do no carb for a week starting tomorrow, I think I may
have the yeast thing forgot the name. After this I need to get and stay
healthy. Brown rice, sweet potatos, etc.

\bigskip
\bigskip
April 8th, 2018

day 0:

2:00 (approx)

So I went on Reddit again for some 5 hours last night. I really should
have kept to my principles with ades. It's grest to go out with him, but
I can still eat healthy. Regardless, u behaved as if I will be carb free
for a week so now I must stick to the plan I've laid out. Cook all your
own food. It's not worth it. Everything is more connected than I
explicitly realized. The health, the mind, the body, success,
relationships, the soul, everything is connected. What is bad for one is
bad for all, what is good for one is good for all. It is then so
imperative to pursue the correct path in all facets of life. So, for
school, we really need to start working on the projects. Procrastination
brings stress and poison to the body.

12:38 next day

So I spent the majority of the day cooking and hackying with libgdx,
also did some reddit. Didn't do other stuff, was too tired I guess.
Tomorrow I'll have a lot of work to do, may end up napping.

\bigskip
\bigskip
April 9th, 2018

day 1:

Bollocks to lot of work to do lol. I wasted too much time watching the
nice Australian doctors YouTube videos and recognized I need to stop.
Also, someone showed me how to clear the screen in libgdx from stack
overflow, which worked out well. I also feel like I'm back. When I was
doing the prayers today, the only thing I really had time to do, I felt
that same productive feeling as before. Tomorrow I should really try to
make a rough script and eclipse doc for the tutorial. So not in the mood
for neuro ec, too much stuff to do. I also think the sort of weening iff
reddit where I can respond to responses but can't make new comments us
good. But I really need to stick to no lurking and no new comments.

\bigskip
\bigskip
April 10th, 2018

day 2:

11:53

I drank carrot juice, had mayo at Burger market today. I felt like crap
after, had bad gas at the gym. It could also be the chocolate though.
Tomorrow Im cutting out chocolate, mayo, and carrot juice. Productivity
wise I was ok. Was befriending Kayla in hopes of connection to my girls,
which isn't bad I guess.

\bigskip
\bigskip
April 11th, 2018

day 3:

7:48

I'm feeling white hungry and tired in resent, hopefully as a result of
the diet and the candida going away. I've also been less productive. My
genius feels depleted I think. I feel an anxiety as if I can't be
productive at all, it's been quite saddening. Perhaps it's because I've
been focusing on YouTube and not making the actual game. I do think the
skills I'll gain becoming a YouTuber will benefit me in life though.
Presenting yourself before a camera can help you present yourself to a
public, hopefully. I then need to try to compile some values, use my
analytic skills to determine ideal concepts. Idk. I fear I won't be able
to do this analysis. I probably only need one YouTube video. The
rendering part is the bit we need to understand.

\bigskip
\bigskip
April 12th, 2018

day 0:

Full on watched YouTube videos today, just so tired all the time idk. I
think it's very related to success in your field. You need passion to
give you energy. On a positive note, I went out clubbing without
drinking and was rather confident and alpha. Freya got with that total
beta, but then I wasnt really trying to get with her. I just enjoyed the
pheromones of hot blooded woman, with the two others are not -- nish.

\bigskip
\bigskip
April 13th, 2018

day 1:

Though I'm still incredibly nervous about rutgers, and this is a point
of stress in my life, the future looks bright. I felt incredible today.
The combined benefits of going out with people and not drinking are
fantastic. I must do more of this. Tell Aviv every thur, work every
Friday. Also, the benefits of a proper diet with weight loss further
contribute to this enhanced mood. When in tune with reality, you must
craft for yourself a good reality. Then you will have reality based
emotions which are the most potent and real. If the reality is good,
your good emotions will be incredible. If it is bad, the bad emotions
will push you towards the good. Even if I don't get into Rutgers, I
still have options. Don't think permanently about an unknown. arrogance
is harmful for others, but most importantly it is harmful to the self. I
can still be successful, not on a long shot but in Reality, regardless
of whether I get into Rutgers. If I don't, I'll need to work hard to
create a new plan, but I am ready and prepared to do this necessary
work. God has equipped me with the tools, I need simply use them. I am
100\% capable. The Tora will never be outside your grasp.

\bigskip
\bigskip
April 16th, 2018

day 1:

So this entire past weekend I've been paralyzed by the stress of
rutgers. I felt I needed all the youtube and crap to cope. It's because
I can't think my way out of this one, any work I'd do towards a solution
will be meaningless. I simply need to wait until the decision comes out,
then I'll have a stable life to work towards improving.

\bigskip
\bigskip
April 17th, 2018

day 1:

It seems I won't be seeing my application decision until later. The only
solution then is to recover from the horrible binge, and proceed as if
accepted. I must continue to code, I must reclaim my life regardless of
college. All the progress I've made with staying in reality may be lost.
This is terrible. I can never let something like this happen again.

\bigskip
\bigskip
April 18th, 2018

day 2:

I've seemingly calmed down from Rutgers. No need to think on it further.
As for my productivity, it wasn't great yesterday because of the tekes,
but I must be fully productive today. I don't see myself going to the
gym today, but if I can get some Hebrew and programming progress done
I'll be happy. If not, I really need to start addressing where my time
is going. I chill with Richard every morning, perhaps I should just
close my door and start working idk. Maybe I should work before the
shower. Definitely need to enforce rule, when I am awake and look at my
phone for the time, I go in for a shower. It doesn't have to be cold,
but I should end cold.

\bigskip
\bigskip
April 19th, 2018

day 0:

I had a wet dream, or something, last night. I was awake as I came, I
first thought I was peeing. I'm not sure if im craving the pleasure or
the release or both, but I'm craving something now. My dreams also were
dark and terrible. I was at some event with friends and a group of
midgets was there. I would taunt the midgets and run for my life as they
chased me I should've been able to outrun them, but could not.
Additionally, a few little kids kept on teasing me, before this (unsure
if in same dream) about why I couldn't do some Jewish thing. I don't
understand it, but I felt this horrible feeling at the end of all the
dreams, feeling more and more shit as the night progressed. I seem eager
to claim these as a manifestation of my minds failure in my dreams and
then to use this as some sort of turning point, but I shouldn't be
strict now more than ever because I felt like shit last night and came.
I should be strict now because I always should have been, because I'm
failing to fully embrace god. When I think ``no, I can't remove from
myself the internet and all this stimulation'', I am denying god. I am
doubting the faculties with which he has presented me.

This is the same scenario as every other failure. I doubted god. I don't
want this to seem as if ``theres the revelation, there's t ticket, I was
doubting God now I have the knowledge and caution not to doubt him. `` I
will emphasize again this is exactly the same as every other failure and
if I fail again it will be the same as this failure. It can't all be the
same though, if it is then you would simply fail again in the future.
What will be different for next time? My resolve maybe? Have I seen some
light in my dreams last night that will better enable me to withstand
the struggle? No, it is a choice. There is absolute free will within
humans and this time I will choose differently. This does not leave room
for a comprehension of why I chose to fail in the past, but this is an
absolute proof of free will -- not that one was needed. I am the same
person I was yesterday, and the day before, and likely for some 3 weeks
now. Yet, this time I am choosing to do differently. For my happiness,
for my soul, since one can only be happy if they are developing their
soul.

Further I must be cautious of tongue, for I don't know anything. No, I
shouldn't be eager to display this fact -- boasting about how humble I
am. I should acknowledge I don't know much in every facet of my being.
But what then if I get cucked, so to speak, by an arrogant buffoon who
claims to know everything. Don't, reject their posed reality, but only
for yourself as we are justified to do.

My new attempt now poses an issue. How am I to handle the emptiness. The
past response has always been to fill this with content, but what if I
know within myself this content is poor. What will I do when I find
myself at Ben's house with nothing to do on Saturday evening. I must
think this through now. Is preparation really the key? But we can't
prepare for everything -- there must be another solution. Maybe this
solution is applicable only for the small frequency of scenarios where
we were not capable of preparation. If I were to become imprisoned, in a
room with nothing and no one but a phone before me with YouTube videos
constantly playing in loop if I want to watch them -- what could I do to
not watch these videos? I can always expand my knowledge of what I know
by utilizing the logic potential energy in my experiences. I can
meticulously go through every experience I've had, and try to learn
something from it I did not recognize before. It even has a limiting
factor, because if this energy is used up faster than you can accumulate
it through experience, then you will be left with nothing again. What
else? I should not fantasize either, as this would be to worship and
idol. If God's reality is such that I am placed within a room within a
compound within his world of creation than so it is- and is not me in a
different place somewhere else. Journal writing, even, is capitalizing
on our logical potential energy. Im starting to be convinced this is our
only option, save prophecy. Perhaps prophecy is even the next step. Once
our logical potential energy is exhausted, once the some core patterns
of the world are discovered and no more information to be learned in the
traditional manner from considering our experiences, perhaps our mind is
then ready for prophecy, and we begin to hone in on the central
understanding of everything available to humans. Though perrenialism
garbage kind of hijacked the triangle, we can keep reforming and
reforming our thought until we reach the most singular understanding
which would apply to everything in the universe.

\bigskip
\bigskip
April 22nd, 2018

day 2:

7:00 pm

I started my new diet where I eat healthy carbs. I think I ate too much
though, next time should do less rice.

12:32 next day

Didn't get a ton done, but got some done. Tomorrow I'll hopefully do
even more. IAt the least I'm not disgusted with my progress. Healthy
carbs is definitely the way to go though. I'm also stressed about
Hebrew, but it is what it is. I can still get a good grade, and can
still learn a sizeable amount of Hebrew in the coming two months. This
week I really need to prioritize getting something going for the summer
though. I want to give momzair flight info by the end of this week
100\%.

\bigskip
\bigskip
April 23rd, 2018

day 3:

I'm feeling better, I feel good when I eat, am very tired after eating
the big meal though. Could be just because I need sleep. I hope I can
get some coding done during kabbalah. After watching the movie with
Woody Allen and the such, I'm feeling a tad existential. As if I'm at
some point in my life where it's near the end, like we're getting ready
to move out. Since, when major things happen you consider everything in
a major scale and thus the remainder of life is not even fathomed as you
think of life as one step or a series of steps in a larger picture, with
undue focus on the other parts.

9:47

I felt emotionally insecure after getting my 86 grade back. As if it
hurt my intelligence. My mind is totally not in sync with reality when
it comes to grades. I must be careful with grades and be prepared for
the possibility of failure. I could have failed my philosophy paper too,
and if I have I am no different than before. I choose to do real work
over trying hard to get a grade, so the grade is only important insofar
as it is an accurate assessment of real knowledge, which it is clearly
not.

\bigskip
\bigskip
April 24th, 2018

day 0:

8:38 pm

I will call this a somewhat unintentional relapse, so though it doesn't
have the implication of consciously rejecting god as I have so foolishly
in the past, it will have otherwise negative impacts on my health and
mind. I played fortnite today, even though it was with friends, I have a
headache and feel tired. No more fortnite. Also no more Instagram, I
don't even know why I allowed myself that. I must remember I'm not yet
healed, I've only just begun to heal.

\bigskip
\bigskip
April 25th, 2018

day 1:

11:26

Got into Rutgers! My life won't have that struggle and hardship, this
must be a platform to ascend to greatness. Speaking of ascension to
greatness, I felt rather unproductive today. Going over what I did, I
translated prayers, worked out my biceps and triceps, cooked and ate
food, and worked on editing, finishing tutorial and just need to work on
introduction. If we break down by expected time, translation is prob an
hour, biceps triceps another hour, cooking and eating should be around
2.5 for today, and editing would be an hour. That's 5.5 hours yet I woke
up at 11 and it's twelve hours later. I need to rush through the
unimportant things. It's nice to take life easy and be relaxed, but we
can still be tranquil when rushing. Maximize your time, it is valuable.

\bigskip
\bigskip
April 26th, 2018

day 0:

I'm in the most severe relapse yet, eating icecream and watching anime
as I type this, but I realized something. When you try to abstain from
things for so long without due diligence of necessarily filling it with
content, you get sick. You stop believing in your current method. I have
a responsibility to be productive and successful.

\bigskip
\bigskip
April 27th, 2018

day 0:

1:00 the next day

This is the real relapse. I fapped. The counter is reset. I must
absolutely fill my life with content, with productivity. If it is hard I
will struggle. If I feel like crap I will still do, even at the
production of a bad product. I will keep producing no matter what. In
sickness or in health, in hunger or in satisfaction, in exhaustion or
with energy. Fuck. Fuck. Fuck. What I've lost needs to be mourned. I can
build it back, I will build it back. I will be productive. I will pray.
I will no longer be a slave its done. It's done. It's done. Monk mode 4
starts this Sunday. God help me. We are in survival mode. This is our
life. To not do this crap is to live. After Shabbat ends we are done.

\bigskip
\bigskip
April 30th, 2018

day 3:

10:58 pm

I woke up at 6 today and it is 11pm now. That is 17 hours. I had class
from 8:30 to 12, then again from 3:30 to 8. That is 8 hours. What did I
do with the 9? I showered, prayed, translated, went to gym, cooked and
ate food, talked briefly with udren, cooked and ate food, then fucked
off texting. I need to be more energetic, especially with the cooking. I
need to save time.

\bigskip
\bigskip
May 1st, 2018

day 4:

I began to relapse today, watched a few YouTube videos, but was able to
bounce back. Just consider that the YouTube and garbage won't benefit
your situation or ease the fatigue and physical ailment. It is still
very much a long term issue.

\bigskip
\bigskip
May 4th, 2018

day 1:

6:33 pm

So I have been steeped in relapse over the past few days. This has led
me to incorporate punishment into this next attempt. Incorrect behavior
is punished with a water fast, for every incorrect thought I must take a
cold shower for 1 minute. Today I thought 5 times about biting my nails,
once about sex, once about an omegle girlfriend, once about videogames,
starting singing music to myself once, and thought about movies once.
This totals 10 minutes of cold showering at the end of the day. Even
just ensuring my thoughts are always on what is at hand, I find myself
more relaxed and more like what I envision a sage to behave like in
superficial matters. I've also done other things like relegate all
internet use besides directions and communication of irl people to my
computer. Before I could check youtube or look up a tutorial on my
phone, now I cannot. If I'm doing this correctly, it shouldn't be hard.
Once you actually realize the truth your physiology conforms to that
truth and the urge is gone. If It is hard it means I have fucked up, and
I'm undoing something of the past. This is where the defenses come in.

\bigskip
\bigskip
May 5th, 2018

day 2:

Today I walked through the old city for some 3 hours 45 minutes. During
this time, I found it incredibly difficult not to have songs playing in
my head. I also found that I had troubling really absorbing the
surroundings as I wanted to. Later I was doubtful of the singing
prohibition and sang for 2 minutes roughly. I immediately got a
headache, this tells me music, even self created, is immediate
gratification and, for my specific case, must be eliminated for the time
being. I also feel a bit dead and tired, perhaps I am healing. We shall
see, 2 days isn't enough for positive change. In a week I should
probably start to feel better.

\bigskip
\bigskip
May 6th, 2018

day 3:

11:42 pm

I feel the water fast really helped me set my goals straight and be
conscious of what I'm eating. I also had what I believe to be a
productive conversation with Noam, hopefully my insights can help him
improve his life. I don't feel like writing right now, Richard believes
in kabbalah suddenly and I would rather like to dissuade him of this
nonsense.

\bigskip
\bigskip
May 7th, 2018

day 4:

12:34 pm

I felt very good this morning, but got incredibly tired during ulpan. I
mean, I usually do, but I suppose I survived reasonably . I'm also very
hungry right now, am going to gym to work off the hunger. I should be
able to finish my list today.

12:30 am

Finished the list except for faur after poker, which was dumb to think I
could do anyway. In poker though I became a child after winning and lost
in the end. I was playing well in the beginning though, I think. I
notice my mind healing, it feels good. I still lack the super powers I
once had though. It will take time and more healing to build them back.
Hopefully soon.

\bigskip
\bigskip
May 9th, 2018

day 0:

12:30 pm

I relapse last night with YouTube only, but right now I'm feeling pretty
good. I think the lasting effects of an immediate gratification binge
are definitely less than a food or fap binge for sure. I think it's in
the fact that I'm engaging with a community, even in a false skewed
sense. An idea that makes a lot of sense now immediately comes to mind,
friends give you the emotional energy necessary for productivity. New
rule, do something with friends every single day. People you can enjoy.
I really think I've found the common cause of relapse, loneliness. But
it just can't be hanging with friends, it has to be people your
comfortable with. And then we can only develop this through nofap.
That's the in, it's the key. Starting with shit life, the first step is
noFap with as much productivity as you can muster. Step two is increase
your friend pool by a lot. Make friends with everyone, get to know
people and consider that we're all very similar. This should lead me to
a genuine neutral position.

I will now describe this ideological position to set it in stone, so I
don't forget it and know to embody it. My natural inclination is
pragmatic libertarian, but I consciously decided not to judge people
based on political views and then also not to take my political views so
seriously, and certainly not as facts to use in concluding other things.
I decided this because I figure that most other people would decide the
same thing as me in my situation. That's not to say everyone is right in
their own way, or this sort perrenial thing, but I think certain
situations are more conducive to a true conclusion than others.

\bigskip
\bigskip
May 11th, 2018

day 0:

10:34 am

This is perhaps the most shit I've felt in a very long time. I feel
extremely fogged, so much so that I fear I can clearly see the path to
clarity, putting me in a negative feedback look. I also am feeling a
love, for mankind for everyone for everything. I feel a power in my
loins, I believe this is the source. Though I feel incredibly sad at the
same time I am joyous and happy. What's happening is I have a physical
response of some type of excitement. I don't know if this is happy or
sad excitement, fear or love. Because I feel very fatigued and foggy,
I'm going to state the goals I consciously recognize or remember
recognizing and move from there, starting with ones I have the most
confidence in. In a way I'm situating the absolute truths for myself to
conclude the rest of my life, like descarte.

\qquad I want to be Jewish and follow Judaism, follow god. This is true
100\%, perhaps the most true. Reducing that to less abstract goals, I
want to be successful in secular life, and with god in mental life.
Further, I want to be productive and I want to know reality to the
greatest extent. Now an emotional pursuit, I want friends. I love
mankind and want to be with them. Even further with Jews, for we are a
tribe. Right now we have productivity, accurate comprehension of
reality, and human relationships. I also want to love god, but I don't
know if I do. If I don't this is because I don't understand properly
what god's presentation to us is. One reason I love people or things is
because they provide something of value to me, and God is certainly the
greatest source of bounty. He gives everything that is given, creates
everything that is created. I state this as fact, ready for logical
manipulation to conclusions, but I really don't comprehend it. Must I
see examples maybe? Is it impossible to comprehend? I will throughout
today and tomorrow look at everything not as I normally see it but as
gods creations, which they are. I first thought that someone loving me
also makes me love them, but I'm reconsidering. I think now that love of
one as a source of bounty must come from a full desire to provide you
with bounty, proven by its manifestation in behavior. I've lost my train
of thought and have become tired again. I will go to shook, eat bread,
and reassess my goals. Maybe I will have a food only diet, allowing
bread and things, for a week. I feel hunger will impede me.

5:12

I fapped at 5 pm. It is high time we stop dicking around. This ``Oh I'll
just start over the next day, a fresh start'' is pussy liberal bullshit.
Man the fuck up right now. We don't have time. While we have wasted 19
years of life, those who man the fuck up and experience the discomfort,
regardless of what comes their way, have succeeded. I don't have the
capacity for sympathy of others. Simply, I am not worthy. I am lowly
piece of shit. I shouldn't have confidence, should not have friends, not
until Sammy comes. Then I may be confident in the values I espouse.
Thinking ahead I see, trying to escape the current reality through time.
Fuck that, I am here and now. I suck. I have always sucked. I do
nothing. I accomplish nothing. I am a beta male faggot piece of shit. A
real man does not need a family to push him to greatness, only god.
Extremes, this is what will bring me grace, and what I need. DO NOT EVEN
THINK about that smut. Extremes of health, extremes of productivity,
extremes of god. I am not ready for friendship by fault of my own. If I
want to be a pussy and not take control of my life because no friends is
sad, I can go fuck myself. I disgrace god and everyone I supposedly
befriend.

I have no right to even be mad at myself, I conceded to my primal self.
I now understand. I allowed it to rule me. I was the primal self's
master. Now the primal self can go fuck itself. This declaration is
abstract and meaningless and unproductive, but I have chosen to express
it as an abstract concept behind my new actions. If they are not in line
with this text I am a piece of shit. If I behave in line with this text,
I will achieve morality. Let us begin.

\bigskip
\bigskip
May 12th, 2018

Day 1,

9:18 pm

Shabbat was mostly a success. Was tired during the reading at the end,
and didn't finish all of it, but occupied most of my time with
productive things, pushing through fatigue. It is also good I read what
I wrote yesterday. Those words are clarity. Man the fuck up is correct.
Now that I've done it my entire countenance had changed. I'm focused, my
head is in the game. The shit I'm studying now is so fucking difficult,
life is easy. This is a good thing. The one violation was that I ate
watermelon to my content. It doesn't matter how much you eat, it should
never be to the point where an additional piece won't taste good.

\bigskip
\bigskip
May 13th, 2018

Day 2,

8:23 an

Strange dream. I went to a hotel on Shabbat for some event. Was with my
famy, can't remember event. I order pan fried vegetables from the hotel
restaurant a bit before Shabbat ended. Was rushing to leave. Once we get
in the car get into semi argument with Rebecca. She tells me I'm fat, I
tell her she thinks her ass is big only because it's fat and it's
actually chubbed out and miss-shapen. I compare Rosa and Jaime's butts
and stay confident in my decision, not in a sexual way. There is also a
third entity among Rosa and Jaime's who I compare the ass of. I believed
this girl to be another sister. Was taller, dark Arab skin, long black
straight hair, and generally larger in stature and more fat, but not in
an unattractive way, more like classic whore with big ass way.i never
saw her face. I woke up some time after. Genuinely the fuck is going on
with my dreams.

9:19 pm

I've finally firmly grounded myself in reality, but I still now need to
find my way. I have the capability now not to binge, but I still must
strive for and achieve perfection. I do believe a mostly all meat diet
will help me do this. Today was a relapse btw, I started it with the
falacy of bread though. Not tomorrow, but right now, I am starting
without this fallacy. Low carb all the way, yet still practical. The
strawberries in limited amount at the beginning of a meal. Otherwise no
sweetness. I'll eat mostly eggs and chicken. Also perhaps the kale
cabbage salad.

10:28

God in his Mercy has provided us with a two step plan for success. To
know what to do, and then do it.

\bigskip
\bigskip
May 14th, 2018

Day 1:

So I went out with Ben tonight and the lack of superpowers was
disgustingly obvious. Nofap is more important than anything. I
definitely have urges like Friday, no matter what I can't give in --
even if I were to become permanently debilitated. The diet was
successful though, I'm very pleased with how I feel on carnivore.
Hopefully I'll have more to say later on, I feel fatigued and headache
now, probably because no exercise and dehydrated.

\bigskip
\bigskip
May 15th, 2018

Day 2:

Dream, 8:24 an

On a different bus to philosophy, landscape is different. Looks almost
like outside of a courthouse and inside uni is a shopping mall layout
with ice cream shop inside. y my dad is here and wants to review classes
I'm taking. I get there and end up up being hungry. Me and Richard and
others go to a restaurant that is expressively homosexual, and someone
in the group made a gay joke. We're eating appetizers as they come to
kick us out. I start scarfing down food because I'm hungry. I try and
act nice throughout, then at the end I'm pushing it to finish my food,
kind of refusing to leave the restaurant. They say something like ``we
were so happy, you were the nice one but now it comes out'. I come back
to philosophy 7 minutes late and say ``ah, 7 minutes not an issue'' and
go into class. My dad comes in with me and we try and sit but can't find
seats or can't fit, so everyone turns their desks 90 degrees and teacher
teaches from the side. My dad starts screaming quietly that I should
apprentice with someone teaching a trade, and leaves. He was interested
with the ice cream shop, wanted me to leave class to go make cones that
are really tall soft serve. Teacher chastises one student about a single
absence in their career, which makes me nervous as I missed a lot. I
think I have classic liberal retard discussion with liberals about my
dad, with sort of implication ``those damn boomers don't understand us,
stuck in their old ways''. That's all I remember.

12:33 next day

I feel like, even though it's only day 2, I'm starting to get very mild
super powers. I'm become relaxed and I'm hackying easily with friends.

\bigskip
\bigskip
May 17th, 2018

day 1:

11:39 am

So I did another of those stay up till 6 am on phone because can't sleep
things, and I think it's 100\% because the hookah. No more of that.
Otherwise still Gucci with everything else.

\bigskip
\bigskip
May 22nd, 2018

day 0:

1:56 pm

Haven't journaled in ages, will update everything in tomorrows entry. I
had a good idea though for exercise that emulates predator prey. One
person Chase's, the other runs away, full on Sprint. The predator
tackles prey when prey is caught. Slower is always prey, fastest is
always predator.

Things to ask reddit: chicken liver

\bigskip
\bigskip
May 23rd, 2018

day 1:

10:00pm

Getting to sleep a little too late tonight, but it's alright. Mostly on
schedule. Did well today, though still needing to figure out diet. What
is committed is I'll still do keto, with mostly meat and follow
Maimonides guidelines but more strict. Within keto and Maimonides I have
free range. I've definitely got most of my super powers back as well.
Also should update, on Shavuot I figured I would just relax and do
nothing and it totally fucked me. Was tired all the time, actually got
readdicted to videogames again which was ridiculous. I said that
yesterday would be my day 1, ended up a day 0.

\bigskip
\bigskip
May 24th, 2018

day 2:

7:13 am

Dream time boys. Me and some friends had found an old game that was
broken, we fixed it up with someone putting more effort than everyone
else into fixing it, and we played it. It was 2d, almost looked like
MegaMan. You would jump around and shoot each other with a volley of
machine gun bullets. You had to jump far though and the map would start
falling. Interesting.

10:00 pm

Waiting at bus stop to go out with ades. Today I felt ok, did work but
also did a lot of sleeping and read Robinson Crusoe for a long time.
Perhaps I should limit this as well on weekdays. I felt a little
insecure as if I was avoiding work, but I should know in truth what I am
doing, and need only look within myself for the answer. I definitely
felt I needed a fresh perspective, at least regarding my presentation.
We'll see, don't stress about the quality I think. A passing grade is an
A+. It is also notable that I was very tired, then had butter with
Cacao, then felt energized. I'm gonna make literal Cacao butter a staple
food. Overall, I feel content but the anxiety of these final projects is
definitely there. I should do them perhaps months in advance for the
future, so as not to disturb my tranquility in the slightest.

\bigskip
\bigskip
June 1st, 2018

day 1:

4:45 pm

Bread makes you tired, makes you relapse -- so we've learned. Monk mode
5 has begun, because I've been horribly sick since binging on food and
computer, though that surely can't be all. Diarrhea is a still runnin'.
I think I'm coming to realize some wise truths now. For social
interaction and the such, beliefs should be determined by behavior. If
one ought to do something, like be friendly to others, his beliefs
should incline him to do that thing, so he would believe everyone has
value so as to be friendly to everyone. In other news, very tired today.
Well, wasn't so tired but I'm certainly tired now so whats up with that.
I'm supposed to read an article before shabbat, I'll just read both on
shabbat though, still read what I can before too.

I get a certain emotional melancholy whenever I see something
picturesque, in this case trees blowing in the wind. It's removed,
leaving open the world to possibility, it's color and figure are quite
pleasing, and it seems as if it would be part of an ideal living. That
such simplistic beauty would surely be in my ideal life, when I say no
more to bad destructive behavior and ascend towards the heavens. It's at
these times that I feel love. Its not for a human though, which says
something about love. Maybe it's towards a human I desire, not a
specific individual just having someone in general. I feel I'm still
dreaming towards an ideal life, but I feel as if all of it will be the
same as what I'm doing exactly right now, and that the joy is there for
us to find. On a likely unrelated not, all art is describing life. Back
to the trees, good times with friends? Is this the source of happiness
that prompts my emotions? Holidays with Christmas socks and hot cocoa?
I'm not even Christian, this is just in my mind from culture, so this is
not quite an accurate source. Perhaps , and it feels accurate now,
perhaps I'm longing for the childhood I never had, probably a bit over
shot for the proximity to such an easy cliché, but something in my
childhood maybe. Riding bikes with connor and brian, childhood
adventure, is this what I'm so reminiscent of? Why? Perhaps it was a
necessity to be exercised out in order to see it's meaningless and it is
meaningless because it is not of god which we have situated must be
source of absolute meaning so we can ignore it with that simple logical
proof or simulate it's happening in our head to see it through to
meaninglessness, but then what? Find meaningless in the next thing.
These are just like the empty pleasures of so many other things, but
``childhood friends stuff is natural, not computer. How can it be
meaningless?'' nature is not meaningful necessarily. Fine then so how
are we to find the deep, emotion inciting meaning. All these emotional
invocations relate back to past experience, again, the artificial
potency of emotions through childhood I suppose, but maybe they aren't
artificial. Maybe they are more pure because the proportion effect,
where they encompass a higher proportion of our experience, or rather
our experience hasn't been muddled by excess or bad behavior. Is there
real emotional excitement left in the world for one in adulthood? Surely
this is found within the realm of Judaism, or god, but in the mundane or
only the pardes? Are we supposed to perfect our fulfilment of the
mistvoth until we are prepared for the pardes and then reap the rewards
of cosmic understanding from there? Side note, we must labor to fulfill
the mistvoth because if we were to take without experience this cosmic
understanding we could very easily jump too far or too little, Our minds
must be firmly rooted before stretching so far, lest we become lost from
reality. I suppose this is madness, and that this journal entry has been
quite a ramble. Ending it now, will read over a bit.

\bigskip
\bigskip
June 16th, 2018

day 0:

1:06 next day

Well boys, these past two weeks have been rough to say the least. The
derech has been lost in near totality. There are things I regret
frustrations upon me, but the realm of purity I may have once glimpsed
need not be out of reach. I must and can try to get it back. Let us go
through what must be done.

Food. Well, I'm skeptical of a fat based metabolism, so let us combine
them w

With a plan. We know that working when hungry is good, so I say
intermittent fasting is the way. 8 hour windows, with 3 meals of
approximately 750 calories each. This way it will be controlled hunger.
The restrictions will be general health as we know. Must have meat every
day, must have fat every day, sugar from fruits, no processed
carbohydrates besides natural breads, when out to eat we can order what
we want, but it must be the closest dish to those items possible.

Purity. Omegle must go, we know in our hearts it is wrong. But how,
then, are we to fulfill our desires for people, our loneliness. Patience
is a virtue, and we might befriend the past authors of time through
reading their books.

Productivity. We know it is scary and daunting. It doesn't matter. What
is scary now will be exciting later. Embrace it with every fiber of your
being.

Workout. Weight lifting daily. If tired we do a contrast shower or
sleep.

\bigskip
\bigskip
June 17th, 2018

Day 1:

11:31 am

There is too much uncertainty in the logistics of my life right now. I
need to plan and organize everything, make a proper system so I can
focus on what's important. The demo must be finished by this week,
period. Today I need to settle in entirely. I must have sleeping
arrangements, a planned diet, and all of my stuff must be unpacked and
in a place.

\bigskip
\bigskip
June 18th, 2018

Day 1:

12:52 pm

So yesterday I ate carbs and was exhausted. Legit ridiculously tired.
Carnivore is really what I need. I might be generally tired and
fantasize food, but I'll be productive and free from ailment.

\bigskip
\bigskip
June 20th, 2018

Day 1:

12:17 pm

So I fapped and feel no difference, aside from the slight stomach ache.
This tells me the super powers we're very likely not even present,
suppressed by my other ailments. Computer, food a big one, and really a
lack of utilizing the mind. I just feel uncomfortable all the time, the
heat, my head, everything. I need to learn to become at peace with my
environment again. Meditation is key, and reading. So rules will be must
pray, meditate, and read every day. Then programming will come
naturally. Also must journal daily, the analysis really gives me
insight. No, don't say it's important to have your own room. But, at the
same time, I can't have people reading my journal lest they take it out
of context. Should I write it at empty times, and close it when people
walk in, being adamant about not one reading it? Idk, but I can't give
in to anything. Yea, I don't think there's a way around it, a private or
semi private room is necessary. Don't raise kids unless you have a room
for each.

\bigskip
\bigskip
June 21st, 2018

day 2:

11:59 pm

So, I'm 19. I don't see this as a time to reflect though, it's only
another arbitrary day. As for relevant things the most important is my
programming. My progress is still slow as I pursue perfection I tried
working today but ultimately worked very little. I've begun to settle
into my proper self though. I just felt a huge urge though, and though
I'm tempted it is still this moment that I do not give in. Tomorrow I
will wake up stronger or weaker. An urge is a test, a choice between
mediocrity and greatness and I must take this chance to rise to
greatness.

\bigskip
\bigskip
June 23rd, 2018

day 0:

4:01 next day

Monk mode 5, the failure, has officially ended and Monk Mode 6 has
begun. This chapter is Monk Mode: The Summer to Start a Lifetime. I will
not fap, I will not waste time again, for the rest of my life. I
proclaim this now because this is my goal and because it is wholly
attainable I will simply attain it. As for the science not being
settled, I will have an opportunity to change whatever I want one month
from now, on July the 23rd. Everything is in place for me, god is with
me, and my life begins this moment. In moments of uncertainty I must
clarify after thoughtful consideration and stick to my clarification
until July 23rd. One clarification, for example, my diet will be strict
keto and approximate carnivore. Honey is allowed to make food palatable
within the restrictions of keto, but food itself is for fuel. Cold
showers every morning too. My mornings will be pray -- shower --
exercise. I will filll my evenings with productivity. Tomorrow, I must
settle into the basement. I must fill the shelves with items essential
to my success. I must eliminate my negative impact from this house.

Fatigue must be met with fire. Resistance and physical ailment met with
masochism. Desire met with punishment and laser focus. Do not fantasize.
Ever. Ever. Ever. Do not consider the pleasures of fapping, of food, of
immediate gratification. These things no longer exist for you. Resonate
this truth within, all these things are non-objects within your life.
When one mentions it, it is like a tattoo, like a hatred of math, like a
following of sports. These things are not you, you are semantics,
philosophy, Judaism, self improvement, natural ways of living, humility
and awe of the world, and witty good hearted humor that seeks not to
alienate but to accept people. Thank God for the beautiful life I've
been given and thank God for the faculties we all have to enjoy it.

\bigskip
\bigskip
June 24th, 2018

day 1:

10:16 pm

Today was a moderate success. I abstained from crap, but was almost
wholly unproductive. I maybe spent 15 minutes writing code, absolutely
nothing remotely substantial. I need a whiteboard and I need to plan.
Coding is a struggle because I know I'm always lost and struggling, but
it is precisely this struggle that makes me a better coder. Toil, work
hard, and you will be amazed at your progress. New rule, must code for 1
hour every day.

\bigskip
\bigskip
June 25th, 2018

day 2:

11:46 pm

We made great progress in the game. The halls of Valhalla await us!
Next, we must read.

\bigskip
\bigskip
June 26th, 2018

day 3:

8:42 pm

I still don't quite have super powers, but I'm getting there. Everything
is really good. I'm becoming who I am. Can't think so great atm,
genuinelg exhausted. Diet is good, still have energy.

\bigskip
\bigskip
June 28th, 2018

day 5:

Was not as productive as I'd hopes, resisted urges though. Tomorrow I'll
do gym and stop Reddit until Saturday night. Well try cream with low
carb veg, no honey though. We'll see how it goes.

\bigskip
\bigskip
June 29th, 2018

day 6:

8:53 am

So last night I had a dream that Lucy was here. In this dream I loved
her, I felt the emotion, and we interacted as if in the pre stages of a
relationship (flirty, playful, etc.). The dream ended this way and then
I woke up, reminded of Rose and the similar event I remember those years
ago. Then I, feeling love for her, looked at past pictures of her and
saw her promiscuousness, her whoring really, and almost entirely fell
out of love. It's imprint is still there, but my love for God has
resumed itself at the highest point of my belief. This makes me
immensely glad. The idea of fapping is completely repulsive to me, I
feel in the presence of God.

\bigskip
\bigskip
July 4th, 2018

day 0:

5:00pm

So today I decided to fast because my previous failures, really sins,
have been troubling to my psyche. Well, it is more really because I have
been unable to change my habits and I hope this will give me some
emotional easiness to change. But, it isnt the affliction but the
behavior that changes you, but the affliction must play some role
psychologically that makes the behavior easier, right? Perhaps the
behavior has a set difficulty level of psychological strain, no matter
what you do it'll be just as hard. This goes well with the nothing is
changing idea, that every failure I have is truly the same.

I think I must now approach this with a scientific method of sorts. That
is, to approach this like a research. Document how I'm feeling, when I
feel an inclination to deviate from my ideal path, and what I need to
address. Perhaps in the notes we will start some journal, or perhaps
we'll make a physical copy. Right now for example, I want to stop
writing. Why? I feel tired perhaps, there is a tension in my head, I am
uncomfortable, it's too hot, my pinky is discomforted from an awkward
position

\bigskip
\bigskip
July 5th, 2018

day 1:

2:52 next day

I wasn't gonna journal today, but couldn't really sleep so decided to.
As far as the log goes I was semi productive today with coding and c++
all that jazz though I was eating crap and didn't exercise, or meditate,
or practice typing, or read. So I'm for sure missing some big shit here
and it's all part of it. You have private time when Sam is at work, use
it nigger. Get your books in order, get your whiteboard in order.

\bigskip
\bigskip
July 11th, 2018

day 1:

10:16 am

Anything is possible. We can succeed if only we put forth the effort and
refuse immediate desire and relief from the pains of long term success.

\bigskip
\bigskip
July 13th, 2018

day 1:

8:57 am

I was typing a comment on Reddit and it suddenly occurred to me that I'm
tired. I must be tired because of social media addiction. Everything in
the body is connected. Listen to it. Understand it's signals. Before
Reddit was the outlet of our great ideas, now it should be here. A
format may be ``what am I feeling, what is then happening in my mind,
what can we do to fix it.'' What is happening in my mind right now,
then, is that I'm tired. I looked at porn images from 4chan last night,
I watched a movie, and I'm still suffering internet addiction. It has to
end now. I'm scared to death I won't be able to break it. I know in deep
truth that it's fucking my head. I pray that this knowledge will propel
to a greater state of mind.

6:00 pm

I'm in the bathroom reading my past journals and there is a nagging
sense that I have a certain brilliant quality, and in tunedness with my
emotions, only in Israel. Of course, I want to believe this is false and
find some way to prove to myself that it is so, but the real proper
course should be to leave it open ended, and pursue greatness
regardless. This has given me a feeling if freedom and pride just now.
Whether or not it is possible is not a concern. If it is, fine, if not,
fine. I need only pursue it, which makes me think it is possible. I do
need to read more, I'm suddenly though excited for my life and feel good
that I didn't look at Reddit or other assorted crap. Remember this
feeling of satisfaction, of warm tranquil pleasure, and know with your
very being that this is the result of abstaining from what seems so
noroushing at the time. We are deceived until the brief moments in which
god may reveal to us the light penetrating through. He does this every
so often, yet we are so forgetful of it. How is that? Will discuss more
later, I'm beginning to feel the potent emotions once more, this time a
love perhaps for myself, nay for God for gracing me with this
understanding, for it was not me that got here.

\bigskip
\bigskip
July 14th, 2018

day 0:

10:46 pm

Though today wasn't anything major, I simply watched some anime and
YouTube for 2.5 hours perhaps, I do need to call it day 0 to acknowledge
the ideal life exists without this. Face the void, man. The void is
bliss, the void is life.

\bigskip
\bigskip
July 15th, 2018

day 0:

3:12

I just fapped. I don't even know what happened. I just lost all vigor,
all my fight. I had nothing to live for. I'm in a job I don't like,
working on a project with no direction, and no ability to move forward.
This is an opportunity though. I'll now pursue complete extreme, the
perfection I've so desperately been seeking. Anything is possible now,
but don't feel pleasure from this. Pleasure in any form will be your
downfall. Cold showers every morning, then pray, then workout, then
work. After 1 hour of work we may eat. That will be the schedule from
now on, no excuse. On Shabbat we will wake up, cold shower, pray, then
read faur. During this time and utterly no form of online anything. A
YouTube video must be directly related to work. No Joey Diaz, no
fortnite, no Reddit. This companionship is ``needes'' only as an excuse
to hide from the void, face your susceptibility to sexual arousement but
don't think on it. We fail every time because we are loose, there is no
discipline. We wake up and sloth, get home and sloth. Time matters --
use it.

\bigskip
\bigskip
July 25th, 2018

day 1:

8:32 am

Oh how we have fallen. Perhaps matured, perhaps not -- either way I am
not what I want to be.

\bigskip
\bigskip
July 26th, 2018

day 0:

2 next day

After reviewing some of my journal from my true streak of march, Monk
mode 3, I have rediscovered the motivation that excelled me to
greatness. What is Valhalla? It is the realm of God. It is connection
with myself, deep interaction with my subconscious and an understanding
of comprehension of what is value in life. The teachings of the stoics,
everything. Girls are meaningless -- no sex until marriage. No
girlfriend, nothing. These are empty desires. I will remain celibate and
I'll be fucking happy as a virgin. Why? Because I will devote my life to
God, to success in the faculties I have been given. Then when the time
is right and my money is plentiful I'll surely procure for myself a wife
to bear my children. I've fallen into the trap of a goy. Life is not
about having a family and being a successful citizen in the eyes of
others and yada yada yada. I must never forget this. Never. I'll create
for myself a new constitution here, and transfer this to notes. The rule
will be I must read it every morning first thing after waking up. I may
make changes to it in the first week in line with my goals, but only
towards the more strict with 2 exceptions to account for errors. Here we
go. I pray to God that he will give me guidance, and help me remove from
myself the physical ailments that inhibit my mind. I pray to God that he
will help me in recognizing the truth. I must pray with tefillin, I must
create the translation of the amida again -- there is no choice. Prepare
everything Tonight, to start a day tomorrow that serves justice to God
and his glory, his grace and his mercy. How many times I have failed
him, desecrated the gifts he has given me, and how many times I have
been granted wisdom to get back up and reacquire brilliance long
lost.אלוהינו מלך העולם ברוח אתה אדוני

Core beliefs and values:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Our main pursuit in life for the current moment must be success. I
  will not have a girlfriend, I am forbidden. I will not have sex, or
  any form of sexual pleasure. It is mercury injected into the blood. It
  weakens the bones and decays the soul. Success and god, though this
  distinction is really non existent.
\item
  Life would be glorious even without children. What is the purpose of
  life? What is the key to true happiness? It is god. Not women, not
  family, not friends, but god. Though one who approaches the true
  brilliance of which we are capable naturally acquired a wife,
  naturally acquires friends, and naturally attracts family.
\end{enumerate}

Rules

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  No immediate gratification whatsoever. Ever. No YouTube, no Facebook,
  no Instagram, no Joey Diaz, no Vin wiki, no fiction books, nothing.
  Food must be eaten before a workout.
\item
  No pleasure of people that doesn't serve a productive purpose. No
  beach tomorrow, no lunch dates, nothing.
\item
  Must go to the gym or do a cardio workout every day except Shabbat no
  matter what.
\item
  Must meditate every day.
\item
  Foods must be eaten in basic form, never changed to be more enjoyable.
  No splash of milk to our cream, no chocolate unless we need fat, no
  strawberries with whip cream, nothing. Food is for the soul, not the
  palate.
\item
  We must wake up at 5:30 every morning. Naps are allowed after 8 am.
\item
  The journal must be written in daily, no exceptions.
\item
  The day must be planned, even if only roughly, and it's schedule must
  be adhered to with allowance for productive leniency.
\item
  There must be a dedicated reading time (the first time will be used to
  find books to read)
\item
  We must not have pride. We must not be arrogant. We are shit, this
  must be accepted and internalized. During our job we may act with
  confidence, but in other realms acknowledge our ignorance.
\end{enumerate}

\bigskip
\bigskip
July 27th, 2018

day 0:

4:54 pm

It's just failure after failure after failure. No more.

\bigskip
\bigskip
July 29th, 2018

day 2:

6:37 pm

I think I've got something going now. Have certainly not been perfect.
Watched YouTube videos, ate garbage, the works, but I'm water fasting
now and very excited. The fatigue makes resistance easy if I'm honest. I
also still feel terrified of not being productive. Maybe a therapist
would be good for me? Idk. At least for the moment I won't have access
to one and going to a therapist at Rutgers would be an orwellian
nightmare. I think I need simply look to the Torah. I'm excited I'm
doing the translation at least. Or I have the artscroll with which to do
it.

\bigskip
\bigskip
August 5th, 2018

day 0

3:41 next day

Woah buddy this is a late one. I'nve noticed I always feel tired before
I go to write the journal but that once I do I feel a lot better and
happy I'm writing it. Tomorrow morning we have to plan a system. Steak
and eggs diet also, 100\% because we are getting very very fat. If we
lethargically starve it's ok, we can always rest or meditate or read a
book, perhaps even go walking. We also need to create a system. This is
why a room is so vital for productivity, or at the least a whiteboard
that I don't mind sharing. If I were to write my shit on the whiteboard
in the basement I'd advertise my inner most thoughts to the whole
fucking house. Ultimately, maybe I should be comfortable with this, idk.
At the very least my kids will have their own room. A schedule is
something I can write down though, it's just the constitution I really
have to hide. A primary goal must be to recreate the translation and to
harass dad to make the recording. It's a fucking disgrace, I have no
capacity for prayer. Or perhaps I do but I'm a pussy, halas. Also, even
if I'm tired on keto, my productivity will never be optimal until I've
been clean for at least a month. I need to accept that and take the 40\%
instead of the unrealistic 80\%, which really results in maybe 3\%
efficiency. For example, what did I do today? I spent maybe an hour and
a half installing whiteoard. 3 hours were spent working, the rest were
on garbage. I woke up at something like 10 this morning. That is 16
hours, 5.5 of which were actually spent doing something (when building
bookcase is included). My net productivity was about a third, and worse
of that third none was spent programming. Fuck dude. I hate work. Don't
hate it though, don't make it another source of blame. Be glad you have
the opportunity to work rather.

\bigskip
\bigskip
August 6th, 2018

day 1:

9:07 pm

So today was definitely more successful than yesterday or my usual days.
The improvement wasn't massive but was good. I feel at peace. As I
continue to heal I hope I'll become more productive. The job is
bothering also because I'm afraid I won't get paid for the lack of
catalyst data. Just destress. Even if we don't get paid our situation is
still good and optimistic. God has given you many gifts, there is no
need to be upset if he takes from us in addition to giving.

\bigskip
\bigskip
August 7th, 2018

day 0:

10:55 pm

I watched avatar with Sammy just a bit ago. My mind immediately felt
worse. No more of that. Leave the room or some shit next time. Also,
finally settled on a Thinkpad which is nice. Otherwise I was very
unproductive today but not indulging in crap. If we break down my day, I
woke up late, went to gym, then went to work, then gazzed for far too
long, investigated some videos maybe? I'm not sure, I don't actually
remember at this point. Then it became 6 ish and I went to pick up Rosa
and do butcher. After that I went to Dean's, ate cream, and did a good
amount of nothing. I chatted with Jared and then shoofed laptops, before
ultimately and lethargically showering and retiring to bed, where we
watched avatar. Be more productive tomorrow.

\bigskip
\bigskip
August 9th, 2018

day 1:

9:39 am

I didn't journal last night because I was tired, but today is true day
1. Yesterday I was watching the fortnite videos on the bus with the kids
and I finished avatar. It's also been disturbing my tranquility that I
haven't put in the data for work. I must do that first thing today. Its
harmful to my soul to maintain this stress. Otherwise I pray to God this
will be a good streak now, where I finally and truly break free of
nonsense once and for all. Break free. Also, I met and old Christian who
started preaching to me about god, and I suppose it made me a bit
nervous. Was it because I doubt Judaism or I am simply afraid of
doubting Judaism? Should I investigate it further and purposefully
doubt? No. I don't think this is necessary. The doubt will disappear
with study -- it is only natural that sn educated person would have
fewer grounds for proof than someone like daddy. That guy was searching
for meaning though, not finding it. He created meaning from nothing,
like all idolaters in the end. They're too weak to perhaps face the
desolate truth before facing the abundant truth.

\bigskip
\bigskip
August 10th, 2018

9:06 am

Dream. We we're in Matt's new Audi and I crashed it, fucked up the
bumper. Was depressed and mom picks me up from apartment somewhere and I
get marshmallow fluff. In the apartment I came for some reason, I think
just jerking off because of sadness, and wet dream. There was an a'bed
in the apartment and I came in my hand in the bathroom for some reason.
Then, an a'bed told Mom about this and then she got me the marshmallow
fluff and I told her about Matt's car.

\bigskip
\bigskip
August 11th, 2018

day 2:

11:37pm

So even though I ate crap on Shabbat and watched some more Lenovo
reviews, I still think I performed well over Shabbat, though I should
work on belonging with my family I guess more than what I'm otherwise
doing. I'm not necessarily their friend or counselor, but their family
(at least regarding mizrahi children). I also came dangerously close to
relapse but also saw the new benefits of my streak. I was fucking on
today at Paullete's and it was great. Also with dogie I was ok. I was
cringey with Jaime on the bike though, speeding to get validation if
some kind. Overall I'm happy with how Shabbat went and look forward to
next week. I do need to plan my day though I still have a level of
anxiety over unfinished projects etc. Also need to email people asap for
my dining at RU.

\bigskip
\bigskip
August 13th, 2018

day 1:

7:32 am

In gym parking lot, relapse yesterday on youtube, not importabt. In the
carride to the gym just now I was able to rediscover, not a belief in
Judaism, but how the path forward is through Judaism. The idea is
fleeting, but the god we worship is arbitrary, he outlines a set of
behaviors we should do to improve ourselves and these behaviors are the
law. At the very based level, we may at some point feel we have no
control over our lives, over our inadequacy. At that point I told myself
``at least I can control my behavior, keep going to the gym and keep not
immediately gratifying''. And then it ``hit me'' that we are lost truly
in what we should do, and this is the necessity of a god, to define what
behavior we should have. The behaviors God has laid out for us are how
we improve, it's bot about the concept, it's not fairyland abstraction,
it is about the behavior in all it's low level glory.

\bigskip
\bigskip
August 18th, 2018

day 0:

4 next day

Well, we've fapped again. There is no longer anything left to think. It
has all been thought. When the urge arises tomorrow, and it will,
remember your motivations. The world is beautiful without it, Valhalla
awaits, and the terror and regret that will result if we break it. Just
because I don't feel terror now, does not mean I am not terrified. I
will be, just wait tomorrow we will see what terrifies me. I will look
fat. I will behavior mediocre, despite my best efforts to embody the
confident true self I once knew. Carry this motivation with you, like a
torch growing brighter and burning stronger. When you next fap, go
outside and walk. When you next look negatively at the potential work
ahead of you -- gym, translation, prayer -- know that it is in these
things that we will find grace, security, and happiness. It is in sleep,
right now, that I will find grace. Tomorrow it is in prayer and gym and
translation of prayer and coding and reading that I will find grace. The
true battle is not the beginning, the true battle is at around 3 weeks.
Once your mind has accustomed to it's true self, you will be faced with
inadequacy, with unachievable happiness because of malpractice. The time
is now, right now, to fix your life. No longer tomorrow. No longer
waiting for the next day, the next chunk of time. Renounced forever, to
the life of happiness. No symbolic meaning, but ineffable existence in
true intention. Not every day is a battle, not every hour, not every
second but every instant. Each infinitesimal moment is a battle, and one
we must win unquestionably. Good day and good night.

\bigskip
\bigskip
August 19th, 2018

day 1:

12:20 pm

It seems fitting to call this Monk mode 7: Maturity (7 is just the next
one in line). I even reformed my goals to an extent. No longer do I
desire success, I desire to be my best and to work at my most efficient
level, to be as close to god as I can or rather to serve him as
effectively as I'm able over my lifetime.

7:20 pm

Well I shoofed Reddit while waiting and it wasn't a good idea. My head
hurts now, I feel fatigued not invigorated. Tonight I'll find something
to do when I have free time.

\bigskip
\bigskip
August 21st, 2018

day 1:

10:58 am

For fucks sale. We've done it again. No more. Understand that you will
not be happy at Rutgers unless you have healed, and we already have not
given ourselves adequate time to do that.

\bigskip
\bigskip
August 23rd, 2018

day 1:

9:34 pm

Today was mostly a success. I was very productive in the morning and
then not so much so in the evening. The schedule was integral to
success, for sure. We will do again tomorrow. Also, new laptop is fun 😊

\bigskip
\bigskip
August 29th, 2018

day 1:

12:53 next day

You are not special chapter of not giving fuck. Though I didn't think
I'd learn much going into it, I now see that my specific chronic problem
of addiction to immediate gratification and escape from reality must be
commonplace. I'm not the only one with this problem. I'm not the only
one who's an unproductive fuck. I'm definitely on the lower end I must
think, perhaps my basket was shit in this way, but there are people much
lower than I am and there are people at precisely the same level too.
The problem must have been solved, but I'm getting ahead of myself
because I still haven't resonated that the experience I'm having is
being had my many many others if not most others. It's something big and
prominent -- and no don't become special by beating the problem everyone
else has. Become valuable and integrated by achieving the best success
possible along with everyone else. Maybe it's grow the fuc up (probably
if I'm honest), maybe it's just to be comfortable being uncomfortable.
Perhaps I can't feel happy as an adult because I don't enjoy the other
pleasures of adulthood -- notably personal relationships. It may be
unfortunate that I can't integrate like I imagine I ideally would, but
maybe it's not unfortunate but average. Maybe growing up is always this
hard, regardless I need to grow up with or without friends if I ever
hope to enjoy adulthood with friends. Don't do extremes, but you know
what you need to do. You need to lose weight and eat less -- you need to
tell Jared you want to assess your schedule before moving forward with
the game, you need to apologise for not being as productive as you'd
hoped you'd be -- careful not to entice pity. You then need to finish
the amida translation because we need to pray meaningfully. We also need
to say the shema with tefillin because it is beneficial.

\bigskip
\bigskip
August 30th, 2018

day 2:

9:38 pm

SAoNGaF prompted me tt question why I'm sad that I wasn't so popular
today, especially at the end. And it really all comes back to a
girlfriend. We are done with this. I'm hesitant to restrict myself from
having a girlfriend because it seems it would be beneficial, but I would
never marry this woman anyway. It does not matter. No girlfriend --
done. But maybe I don't even desire a girlfriend, maybe I even desire
just being playful with a female. No being playful with females then?
Yes. That's a move. Just as I'm not playful with men, I shan't be
playful with women -- at least for a month. I must stop desiring
anything, and start being content with what I have.

\bigskip
\bigskip
September 1st, 2018

day 0:

7:37 pm

I call this day a relapse for a number of reasons, all of which are non
traditional. Firstly, I pursued seriously someone who I won't be in a
relationship with. I've started caring for the social life -- and this
has made me once more a socially inept fuck. Secondly, I broke my streak
as apparent to me through the conscious wet dream I had. In short, I was
in the dream and the weird girl was there. She was willing to be sexual,
representing my ill viewing of her. I then made a decision at some point
that I was gonna cum and then I forced the situation to become sexual,
almost forcing myself on the girl but she was complicit, and then I
came. I woke up immediately from the dream realizing my choice and since
then my super powers have subsided. I was an absolute social train wreck
today. I actually want to crawl into a ball and die. I felt a grand
depression today and that ties into my final sin, breaking Shabbat. Work
will set you free, and if I'm not working I need to be following the
tenets of Shabbat. Observe how god will care for you if you allow him
to. I broke Shabbat thinking, ``it will be good for me to socialize
through text'' and it has brought me no good. It brought me despair. I
would have been much better off if I had followed with the strictness of
one who loves god, one who doesn't question the rightness of God. In my
hubris I thought being popular through fucking girls would bring me
happiness. Not only have I not even attained the false source of
happiness -- which is honestly for the better -- but I have even
sabotaged my social life by behaving and then situating myself as a
damned weird fool. My roommate probably thinks of me as grotesque. The
reality is not one of despair, however. Sure, my situation is worse
today, but incredible minus 10 is still incredible. I must follow god,
for it is he and no one else -- especially not myself -- that will bring
me grace and proper living.

1:54 next day

I'm drunk -- tho I didn't hook up with the girl. Is it right that I
should do so? Should I be so focused and honed on hooking up? Fuck. I'll
find grace in my class. I also would prefer a girl more feminine, more
gentle. IDK man. If she is in fact so innocent maybe I shouldn't pursue
her -- or maybe I should to get some medals on my belt or whatever the
fuck the saying goes. This is my drunk , poo perhaps unadulterated and
real thought process. God is with me I hope.

\bigskip
\bigskip
September 3rd, 2018

day 2:

12:24 next day

So I've yet continued to pursue Skylar, and consciously I do acknowledge
it as a problem but I don't actually believe it. There is an
uncertainty. Every time I visualize myself and her hooking up, I look at
it as if it will benefit me, but will it really? Perhaps I'll fool
myself of a relationship once more and then fuck myself over. I must
stop fantasizing -- must stop pursuing. She isn't real. She is a slut.
She will not be your girlfriend -- nor is this what you even desire. You
desire the high, the pretend of marriage and intimacy that could never
exist. Firstly, stop desiring anything period. Don't desire, simply
pursue. Secondly, cease to pursue things that don't matter. Sex doesn't
matter -- I could graduate a virgin and be wildly successful. Why?
Because fucking and false intimacy will bring you no happiness -- only
escape from reality. The reality is we may have passed the test for a
fuck buddy, we may be accepted as an empty form of dick and balls, but
we have yet to be accepted by the opposite sex in our whole person. We
are still a failure, we still need improvement. Our work is far from
finished, it has merely just begun. Don't pursue girls. This sounds
horrible, but hear me out. Success in your field will make you more
happy than a girl ever could, because you'll be far closer to true
marriage ntham everyone else. .

\bigskip
\bigskip
September 4th, 2018

day 0:

9:33 pm

So I missed my bhuddism class and fell into a depression. I then watched
a Jordan Peterson and Sam Harris debate. I feel sad and then lost in the
world, and this leads me to question everything. Should I ``hold on''
and wait for my emotions to return to a normal state. If my fundamental
rules for the good life fall into question, then the good life must have
something to do with my predisposition. Perhaps it is a result of
health, perhaps it is a necessity of love. I don't actually think that's
it. It's true, I feel like crying, so perhaps live seems like an outlet
for that anima. I want to hold tight to something I enjoy, knowing at
least I have that. But is this right? At this time, we know it is
actually feasible that not hookups but relationships are good.

\bigskip
\bigskip
September 5th, 2018

day 1:

3:56 next day

That's right. We were about to text her again, but we didn't. Now we see
-- it is identical to addiction. It is no good to text her, to desire
her. Remove her from your life since she has not responded to you. Such
is grounds for excommunication -- never again.

\bigskip
\bigskip
September 12th, 2018

day 1

4:21 pm

I've just started a new, proper Monk mode where every behavior in doubt
is cast away. The indecision, the unknowing, bothers me. It is an
identifiable form of suffering so it should be removed, but then is that
in itself conceding to a demand of the mind rather than changing it? A
question for later, but the motivation, which is passive which I'd like
to label as hopeful for it's consistency, stems from the realization and
acceptance that our behavior is absolutely arbitrary. Buddhism class
served me well, because it had me face the arbitrariness of our
existence and consequently our behavior. If behavior is arbitrary than
anything to cause doubt of pursuit of God, our ideal, is to be cast
away. The Buddha cast away everything in this way, and lived perhaps not
the ideal but the lack of common horror.

Just like the Buddha, I should cast away everything as far as I
personally go -- I should have no dependency on anything, and then be
open to accepting whatever I am lead to believe is the proper path to
God. In this way I pray every morning, not because it fits within my
emotions to do so but because it is the correct path. Instead of holding
on to my feeling of comfort or holding on to an alleviation of an
emotion (anxiety being the product of not immediately doing a pressing
matter), I am empty and open, a blank amorphous ball of clay to be
molded however God has deemed fit to be, as per the determinations of
the axioms of logic created by him. Are we really individuals then if
the ideal is a deterministic behavior? Perhaps this determinism is for
an abstraction of behavior, a single category yes but not a single
behavior allowing choice of equivalent idealism.

I feel that was a bit too eloquent for the simplicity of the thought at
the end, this is likely to be I'm deriving pleasure, somehow, from the
perception of intelligence here or effectiveness. It makes sense though
that I would be happy that I'm smarter, happy that I'm more effective.
But then it more supremely doesn't make sense because existence is
arbitrary. What is this metric of effectiveness, of intelligence? There
is only the metric of how closely ones behavior follows the path of God.
That is conflicting with some belief I still hold -- an attachment I
encountered that must be severed. ``No'' I think `` it is good to be
intelligent, it is good to be more effective at what you do''. This is
false, there is only adherence to the behaviors layed out by god.

The problem arises because I've simply stated, with no coupled path to
reason, that I must achieve a 4.0 . This is based on prior reason, yes,
but that has aged and must be rediscovered if it is still our goal. I
immediately do believe though that money is important for a good life.
The power it provides gives a security, and also better enables one to
follow the path of God. It better enables one to study unbothered, to
study one more verse instead of preparing food or cleaning a house. The
same with friendships, because they lead to money and success but only
certain ones at certain times. Relationship activities that matter, that
are important to the individual in question.

But here we are sort of assuming an omniscient perspective, but perhaps
we still require wisdom from others. Yes, we do as it relates to
effectiveness in society. We must be wise to navigate the sea of
civilization better so as to better enable us to serve God. So
relationship activities as they develop the relationship and grant us
wisdom are within this metric of God. Well the natural conclusion to
this has now become I'm robotic. Behavior is arbitrary, so I need only
act (and I already see it now -- the solution) what is desirable by the
metric if God, the misvot. But, as far as our ignorance is concerned,
perhaps the standard metric of how other people view us is not bad. As a
default act with the values that produce the popular behaviors. In other
words, rely on the innate wisdom of collective human as your guide in
the face of ignorance. Will clean this and paragraph it later. I am
glad, it is a good break through to determining what to do (not in
addressing a single problem, but simply what to do period.)

8:05pm

So now I've become quite situated with the ideas and concepts above, the
arbitrariness of our behavior, but I have now encountered a new issue.
After talking, or more closely lecturing, someone on these topics and in
writing down the journal entry itself, I felt a pride, a happiness. The
fact this is a happiness gives us the connection to a metric and is
itself the solution. I am proud, why? ``Because I did something good, I
was eloquent and superior in the heirarchy, I was effective''. But we
need only go back 3 paragraphs to see the error. Let go of intelligence,
let go of superiority. Let go. ``Well, perhaps I have let go but simple
wish to enjoy the pleasure without a dependency''. But to label it a
pleasure is to say now is better than before, that before is worse and
therefore bad. No, this intelligence of sorts I've gained through truth
realization is meaningless. It is not better nor worse. It just is. Do
not be happy at an event of no change. Now pause, consider and absorb
these words.

\bigskip
\bigskip
September 16th, 2018

day 0:

2:15 pm

Was on the true verge of relapse last night. I don't know what to do,
but I cannot do immediate gratification on YouTube anymore. I require
intimacy, perhaps, but reserve that intimacy for God. This is the
solution. Well don't say marry yourself to God cuz that's gay but nohomo
love god. Confide in him, our father. He will protect us, but cease
disappointing him. It is only when we live under him that he is there
for us.

\bigskip
\bigskip
September 23rd, 2018

day 0:

9:44 am

I still call this day 0, why? Well I've set to release myself from
technological immediate gratification. I am still trapped. Break free,
brother! Let go, there is happiness beyond immediate gratification -- a
happiness ferociously burning, an inferno of life. No more Reddit for a
week. No YouTube ABSOLUTELY. No movies, no computer, nothing. Turn it
off and don't turn it back on. Texting because I need friendships --
desperately. I need to enjoy them -- desperately. I need to enjoy work
-- desperately.

\bigskip
\bigskip
September 28th, 2018

day 0:

3:26pm

I'll use the journal now as an outlet. I've decided again I've lost
super powers, even though nofap is day 37. I've lost super powers
because pleasure again. Just gotta get off it. Whenever I need something
to do, when I desire pleasure -- which I will -- I'll go to this journal
and describe what I'm feeling.

\bigskip
\bigskip
October 5th, 2018

12:22 pm

The day counter will be the counter of my own righteous, of my
accordance with the path as is best befitting my circumstance. I am
unsure of what I will do as regarding women if Molly seems not to work
out. The purpose should not be sex, not such desires, but intimacy.
Intimacy because it will have a lasting impression, a benefit to my soul
and mindhood to better enable me to pursue the knowing of God. I'm every
renouncement of women, I have caved in severe lack of intimacy. Make no
mistake, the intimacy of a women is something irreplaceable. Or, at
least, it seems to me to be a tangible need. Perhaps we could,
however,like the Buddhist renounce too this pleasure -- for only the
duration of college. No. The interaction is key to being a realized man,
one respected. This pleasure is one expected of men..

\bigskip
\bigskip
October 9th, 2018

day 1:

9:35 am

I say this is day 1 because I downloaded tinder last night and it
properly corrupted my mind and day. No more tinder. I'm adding it to the
list of Monk mode - not until after a month. Also, if it goes somewhere
with Molly limit your interaction with her. Have her come over shabbats
for sure. Also was very tired today and didn't wake up at 5:30. This is
bad, tomorrow definitely.

\bigskip
\bigskip
October 10th, 2018

10:34 am

So yesterday I relapsed in watching YouTube and the such. Not fun, my
social skills went in the toilet. I was ok on my diet, I need to eat
more though. Have some sort of snack or two scoops of carb at lunch.

3:15 pm

I'm walking to my tinder date, decided to write her to relieve some
nerves. Why be nervous. If she hates you then your golden, you'll have
an exam to study for and do well on. You're a genius buddy, get with it.
If there's something you don't know, derrive it like back in highschool.
. You're a genius, again, focus on the unconscious, not concsious
communication.

\bigskip
\bigskip
October 11th, 2018

day 1:

10:16 a m

I was actually about to go look at Reddit and the such, then I thought
it would be more productive to check my journal. I then felt a strong
aversion to checking it and figured it is then very important that I do
check it. I now feel the aversion is gone and feel more open I suppose.
This was progress, I am glad. I was sabotaged today by breakfast. Too
Carby. I don't think it's a relapse, but should avoid in future by
eating enough during the day prior.

\bigskip
\bigskip
October 12th, 2018

day 1:

9:19 am

Oh boy wasn't a relapse in the end. Nofap, but felt an urge and watched
anime all night. I killed myself. I skipped Buddhism class. I need to be
strict this Shabbat. Don't go to the gym, or should I? I'm afraid I'll
go and be pooped and then succumb to hunger and garbage. Maybe it is the
gym that will enable me to not succumb. This is a good time to check
past journals.

10:26 am

Well. After reading the past journals, starting from the very beginning
almost a year ago in december, I'm not quite sure how to begin, or even
what it is I'm beginning. I noticed back then I was much more
analytical. The genius I purported to utilize was this analytical, hyper
observant quality. Even now though, I am still conforming to stereotypes
and tropes, This sort of monologueish disenchanted writer who has come
to accept some fate, even going as far to consider the sound of the
keyboard in the silence as harboring some symbollic value of this fact(
in that it contributed to my assignment of this specific trope). Before,
I was very open. It came to me while reading that this was perhaps
because I had annihilated the identity I once was and had great freedom
in fleshing myself out, only for this freedom to taper with a
diminishing return of growth. I am then prompted to reject this idea,
that I am capable of that same growth now if I only choose to do that
growth. Now I'm quite tired, I have a headache. This is surely
attributed to the horrible binge of pleasure I had last night.

\qquad I felt I should have some sort of retrospection since I now have
finally passed my prior streak of nofap, but I don't think we need to
much of a retrospection, we simply need to learn from the past in
addressing our past failure, and string of failures. Let us begin the
diagnosis.

\qquad First, I was pursuing women, pursuing especially normalcy. My
emotional state juggled between girls and social normalcy (Sexual Market
Value essentially) to academic success and the right path of a ``based''
individual. I then in large part abandoned God in favor of SMV. This,
being a suitable god for goyim, is not for a Jew. What seemed to bring
me happiness in the past was simply a truer, stricter following of monk
mode. It was an alleviation to anxiety. And yet again, I feel the
anxiety of not having a girlfriend, of not being in life as a baseline
what a man ``ought to be''. Before this would lead to the conclusion, ``
I need to get a girlfriend, I need to be succesful in academics, I need
to be a based individual.'' Is this what will really give us happiness
though? For now, we will assume I need to be content in order to be
happy, and this contentment will come form long term, permanent success.
Why not simply befriend mathematics, simply befriend programmiong,
academic success. This seems to me to be the most stress free solution I
can fathom. Have all things be secondary to this success. To yourself,
in other words. Build for yourself a large cushion of comfort. That
isn't to say a bed of pleasures, but a strong and stable raft, one with
padding that is high and will protect you from the turbulent waters of
failure. There will then be a desire, or more accurately the capacity
for an inclination, to liquidate this boat for pleasure. To sell your
sail for videogames, to sell your hull for the prospect of sex, to sell
your oars for sexual market value -- validation by others. Don't do
this. Not doing this also requires a reevaluation. Before, there value
was in their liquidity as pleasure, but this is not where there true
value is. There value is in their use. Use the boat to keep you afloat.
Use it to keep you comfortable, high on your cruiseship which is steady
enough to build a ladder to god. While the lost goyim squabble on rafts,
doing the bare minimum to keep themselves afloat to liquidate the next
asset they acquire, the wise man will continually build his ark. Higher
and higiher, stronger and more stable. Once it is suitable enough to for
god, he will not liquidate it, not ever, but instead stay atop this
vessel in the pursuit of god and the training of his children in this
pursuit.

\qquad I must be the same way. I will build my vessel, not liquidating
it for friends, for food, for pleasures of intimacy and longings of the
heart. Even now, I yet feel a need for intimacy. This is a good
oppurtunity to analyze this feeling. It creates an excitement, an exit
of frame to one higher. This demands more urgency. The end of this
demand seems to be a child, and then life. Life together, as a family,
this is the ultimate demand. Look upon this emotional longing. Look upon
its futility. See it for what it is, a façade. I long for the skies yet
my vessel is bloody sinking! How foolish it would be to build a ladder
at this time. Further, the fathomable points to pursue before me are not
even the real ones I seek. I would be dissapointed only to find these
islands built on foundations of mud, sinking to nothing and leaving me
stranded without a boat, for I will have abandoned it in coming ashore.

\qquad To put it shortly and concisely as I can, one's freedom from
``objective'' pain and distress is their boat. This includes your school
work, your livelihood, you providing. This can be compared to the
``basic needs'' of Mazlows heirarchy. The ladder which we seek to build
is self-actualization. This is the highest level of Mazlow's heirarchy
or pyramid, or the self fulfillment needs. One thing I may be forgetting
though, and this is a demon come to haunt me, is the needs of friendship
and love and belongingness. This intimacy Mazlow identifiies as a
psychological need. How am I to express this? Am I not to express this?
I fear I will choose not to and then refer to some buddha dala lama
compassion crap and be nice to everyone, this is the wrong path surely.
In what, then, to I express this? Or is it even possible to not express
this at all? Should I become a cold individual? Psychopathic? This would
necessitate removing everyone from an expression of intimacy, a very
dark path. Using this darkness as a default, I am now tempted to try
something new. Befriend and feel intimacy for those valuable. For those
who are not, be as cold and as psychopathic as the worlds most
abominable killers. Express for them no compassion, no mercy. No, this
is not accurate, but close. If they are to come to me, palms up and in
submission, mercy and compassion must be provided. But their ego, their
confidence, is something to be psychopathic towards. As long as they are
not in submission, they are a nothing. That is, unless they demonstrate
themselves to be of wisdom or value. This circle should be incredibly
small. Including a small number of valued friend and nothing more. Even
then, those with ego who are your ``friends'', who are yet useless
still, they will be dropped. This is the middle path. HaHA! I feel such
an elation. I have discovered something. God has given me such
faculties, and yet remains owner of this faculties I must be cognizant
of. God, our king, owns everything. We are but action figures of his
sandbox, possessions of his. We must not do what is not his will.

\qquad While the above was meant to be a summary, I had a realization
while writing it. This paragraph, then, will be the true summary.
Firsly, the protections from anxiety and what we may call ``direct''
suffering are your life boat. This boat should be a beautiful
masterpiece, furnished lavishly. Build it up, and do not liquidate it
for pleasure. Every unjustified pleasure is a degradation of this boat.
Build it high, a beautiful cruise of fundamental needs (I use
fundamental instead of basic to avoid the negative connotation). Then,
when this cruise is ready you will use this platform as the base of a
ladder to god. This ladder is your self actualization. Don't think on it
now, as you've no fathoming of what it is. In the meantime, however,
there still appears a need for intimacy and love. This must be achieved
through the middle path, and psychopathy used as a baseline. Those who
submit to you, who prostrate themselves before you and god, you will
show them mercy. You will elevate them as an ally. Of those who show
ego, however, you will be cold. There will be no mercy and no
compassion. Your intimacy and friendship of these people must be earned
through demonstration of wisdom or value. What, then, am I to do if I
encounter such a person who does not demonstrate. How am I to be cold to
them. Perhaps be open and acknowledge there will not be any extra
friendly relations between you. Don't respond accusingly. Though also we
should not bear compassion for them. We should not wish them the best,
this is to be self righteous. Firstly, do not engage them. You have no
need for them, so engage them only if they do you. Then, and this is a
very good idea, mimic their level of engagement, or something as a
function of their level. If they do not ask how you are, in an attempt
of prostration, do not prostrate yourself in asking how they are. If
they ask how you are, you may ask how they are but no more than that.
You do not need to reciprocate in the rate at which you reciprocate. If
they initiate a reciprocation you do not initiate a new one, escelating
the reciprocation. This is foolish, naïve, and nonsensical. Those who
are in our circle, however, we shall engage with compassion and
kindness. We shall seeek the best for them and elevate them. Let us now
list who is in this circle, who is inbetween, and who is explicity out.

\qquad After recapping I shouldn't match their level of compassion. I
should match only if they thoroughly prostrate themselves before me, if
they accept a role as mututal subservience, or if they have earned my
respect and it is acceptable for me to prostrate myself before them. Be
kind to those who respect you or those who have earned your respect.

\bigskip
\bigskip
October 15th, 2018

day 0:

6:55 pm

Music is key, tomorrow.

\bigskip
\bigskip
October 16th, 2018

day 1:

9:35 am

Yesterday I said tomorrow, now I say today. I'll commit to these
precepts for 1 month. No, fuck that, the rest of the semester. Valhalla
awaits, happiness awaits. In the path of God we will yet find her, god
having created both her and his path.

\bigskip
\bigskip
October 17th, 2018

day 0;

4:40 pm

It is clear to me now my convictions are fleeting, temporary. When the
tests of failure come, what prior seemed such a certainty of misery
seems then to be a benign antidote to the poison of desire. I then need
to rediscover my convictions, a thorough investigation of confident
conclusion. This past self then must be remembered, and the emotional
state enabling my willpower reinstated. Is it not just enough, though,
to remember in the past I was miserable, or even now the remnants of
misery that are more speedily yet returning? The extremes have brought
me grace in the past, yet I don't follow them and the slope is
grotesquely slippery. My mind becomes blank, a genius of repression.
Instead of isolated focus, I maybe should practice focusing on
everything all at once. Or perhaps just elucidating for myself once and
for all, then referencing that confident conclusion. Make a document and
go through every single belief I hold with such absolute certainty that
I am never to question the document. The success of this document would
then depend on how many conclusions I could make of necessary
confidence. Too few and the list has no implication and is disregarded
for something for encompassing. Too little confidence and the whole
document is invalidated. Fuck, there needs to be a way. There must be.
Perhaps prayer. Make monk mode again, and pray every time a resistance
presents itself. Pray to conquer it. This is what we will do, for I must
commit before I decide to decide later and let myself slip beyond repair
for the valuable night. We'll start right now. Please, God, enable me to
conquer all urges and embrace the coinciding change of this conquest. By
conquering such resistance I will build for myself, for you, God, a
valuable servant. You have given me the tools and I pray now that you
will help me utilize them and cease neglecting the great gifts you've
given me for empty pleasures. I am using your tools wholly incorrectly.
This is wrong, I should not do this ever again. My convictions are not
strong enough to say I'll never knowingly use them incorrectly, but I
ought certainly to take this oath. At least for a time to rid myself of
this poison of extreme. That is what I'll set out to do. Resistance is
healing. Resistance is healing. Pain is healing. Pain is greatness --
yet only pain that is temporary. Permanent pain is futile, the grace of
the useless and goyim.

8:48 pm

I wasn't able to prevent myself from consuming crap yet again for the
remainder of the night, but even just typing the journal I feel my
genius hasn't abandoned me. My intelligence, my gifts of God, are still
well present when if I only endeavor to use them. The last excuse has
come to past. From this moment forward, it is completely and utterly
fitting to follow monk mode with a strictness. An extreme to treat an
extreme. I also completely forgot about rjx tonight, no need I'll let
them no I'm no longer interested. I've no need to stoop to the level of
deserters, Jews who have abandoned God. I disgrace god in my own ways,
in my own negligence and delusion, but even if I have thus far failed to
conform my subconscious mind to this belief, with the directness of my
soul I will always know such delusion to be wrong. Those Jews, who I
must never hate but pity, those Jews act disgracefully. I pity them, I
would show them mercy if they came to me. It is difficult not to despise
them, but I am absolutely wrong to. Enough melancholy speech, you are
not Dumas. The morning of morrow is the morning of redemption.

\bigskip
\bigskip
October 18th, 2018

Day 1:

8:36 pm

Success! I stayed with monk mode today. There were somethings I showed
to friends and some wastes of time, but for the most part I stayed true
and was productive. More of this please. Thank god. I'm rather tired and
perhaps too tired to write something proper, but I'll have something
better to say tomorrow I imagine. This fatigue is actually quite good. I
cannot concede on shabbat though, of all days concession on the most
holy would be horrid.

9:54 pm

As I tried to go to sleep ironically my fatigue left me and I suddenly
was overcome with sadness. Am I so horribly inadequate that I have no
friends, or rather no real friends. I don't hang out with people, I'm
not invited to chill. There's just misery and sadness and misery and
sadness. I talk to people and they talk to me, but our conversations
lack meaning, are without substance. But what is this substance I am
seeking? It all comes back to intimacy, I feel unloved. Yes, this is
quite the terms for it. It is humiliating, a horror of horror. I seek to
love others yet this love is never reciprocated. I now see. Love no one,
no one but god and family I suppose. Fuck. I need monk mode. There will
be no saving grace if I am a sad fuck my whole life. No saving grace at
all. I'll just be worse than everyone, with no reason to be worse. Just
a trap of mediocrity, destined never to marry, destined to amount to
nothing. That is what I'll become I must rightfully fear. For now,
perhaps, it's essential to learn not to love. Perhaps psychopathy is
necessary, to break from one extreme to the ultimate middle path.
Starting now, we repress all warm feelings toward anyone. Manipulate and
achieve, manipulate and achieve. No laughter, no interaction. This
journal will be my friend. In other words, I alone will be the
protagonist of my life, save family. You can be sad and yet
psychopathic, we don't need to be this sort of dick dadtardly. Simply
sad, but caring not for others.

\bigskip
\bigskip
October 20th, 2018

day 0:

12:53 next day

The day 0 upsets me, but it was on Shabbat only though so b'seder. What
is more prominent is that Matt had planned on fucking this Kelly girl
and she agreed to a threesome. Matt didn't tell her it was me who was
the third member, he just said it was a friend. This prospect is
exciting, but it mustn't change anything. Don't expect anything, don't
fantasize. We are unattached to sex, and it makes us happy to have no
attachment. I enjoy having no attachment, much more than I would sex.

\bigskip
\bigskip
October 22nd, 2018

day 1:

6:43 am

So, to update on the last entry, the girl was supposedly busy. Anyway,
yesterday I ate hella garbage -- it was bad. Today is day 1 then. I have
my midterm in 2ish hours. With gods help we will yet get an A.

\bigskip
\bigskip
October 23rd, 2018

day 0:

12:24 next day

It has struck me that I am 1) acting as if I am different somehow than
the average redpilled AFC but further that in my pursuit of perfection I
am limiting myself. A powerful true is that the pitfalls of indecision
are far greater than those of a wrong decision. Stop waiting for the
perfect mindset to come, and start pursuing it. It's ok, you can always
change your mind. Right now, simply begin to internalize the lessons.
Ah, but what's re the lessons. This is a a difficult question, the
behavior is not so stone. There are a few lessons I'm confident in
accepting as the teaching, however. Firstly, my goals and relevant
considerations before all others. Talking to Afam was not only
counterproductive to this purpose, it was my own childish pursuit of
comfort. It feels good to be smart, to speak in a domain of which you
are knowledgeable, but this is not where you will learn. Save it for
dinner parties, not for the dorm room. During that time you should've
been studying. Incorporate that right now. Additionally, I don't send
good reason to befriend girls. You want to have sex, so only talk to
girl who you think will provide what you seek. Maytar and Luigi have
already situated you as beta, as have all the chabad girls. To hell with
them, they no longer matter. At this point, I shouldn't even pursue
girls -- no this is perhaps a cop out. I shouldn't really pursue friends
that aren't valuable. Have a good time with girls? Sure, but not even at
the slightest expense of my own goals. Don't care about them, not even a
little.

I fear this journal entry, seemingly like many others, will be yet
another wall of text that will fade away, lost in time. This is to
address a constant throughout my life -- I don't pay attention. I never
take anything as true, thus I never remember anything. My frame falls
apart because everything is fallible, always. I must now adopt the new
view, what you observe is truth. Why? Because God would not create false
truth. There we have it. Take it as iron rule that people behave as they
do. Start to finally Garner experience from which we can truly learn and
apply. Go with it until it's wrong.

\bigskip
\bigskip
October 24th, 2018

day 1:

2:34 pm

I'm not sure if this is day one truly but I supposed I'll refer to it as
such since I'm not wasting my life on videogames and garbage. The
interview, however, was a total and utter disaster, worst professional
experience of my life hands down. Thank god it was horrible though, it
gives me yet insight into how the world works. It is yet another piece
of the puzzle. Let us assess. Firstly, I rambled. Terrible. Secondly, I
had absolutely no direction whatsoever -- it was a travesty. I tried
hurrily to talk about random garbage and she wanted me to ask questions,
which I had not prepared in any capacity. I then tried to bullshit
question which communicated ``I am open to you''. It did not communicate
strength, but the greatest and most profound weakness. I feel shit
because something is being challenged. What is being challenged, my
belief I have attained alpha. Lose attachment. Don't be attached to an
internship, don't be attached to even the dharma, even alphahood. Be
attached to none of it, for as we have just experienced, the wound still
raw in our minds, attachment brings suffering. For internships moving
forward, you will be honest, probing, and real. The ideal company like
the ideal woman does not exist. It is fantasy you assumed. Fuck them.
AWAY. I will return their call, so then this is attachment, no? For
fucks sake, my life must not come to attachment. I just again dipped
back to resentment and glory. This is not the path, brother. Do not
resent, for they have done no wrong. It is you who has done wrong. Be
kind, and grateful, that such oppurtunities exist in the world. Instead,
we must acknowledge our own shortcomings and say to ourselves, ``It is
unfortunate the relationship is no more. This is from entirely my own
doing. However, the relationship is not so necessary.'' I have even, in
my flusterness, lost the idea I had grasped. Become unattached, for the
love of god, become unattached. No, the nirvana I seek is still
attachment. I feel in being unattached I will attain what I desire, but
what I desire doesn't exist. In being unattached I will only see the
truth. Don't go home, to the wedding. This is not a time to engage with
parents and their limiting expectations.

10:24pm

I've just realized, while reading the rational male, that it is
important to dispel the fantasy. Life is not as complicated as I make it
out to be, or its complications do not exist in my juvenile
understanding of mysticism. It isn't a realm of infinite possibility and
mysterious connections between things in this world. It precicsely
transcends thins in this world. Life, as I shall live, is not
complicated and thank God it isn't. This seems to be one of the keys to
why I wasn't able to accept anything as true before, When all this
complexcity is introduced into possibliity, there is nothing likely
enough to be legitimately accepted.

\bigskip
\bigskip
October 29th, 2018

day 2:

12:51 pm

It is clear to me now why a succesful man shouldn't express his emotions
carelessy. Like masturbation is the liquidation of sexual energy for
delusional purposes, careless emotional expression is the liquidation of
emotional energy for delusional purposes. Once it is expended it is no
more. In my fit of joy from getting a 97 on my midterm, I lost all
emotional energy of the joy. This joy should've carried me through my
day, as I savored it silently and contently. The energy is not from
expending, but from the option to expend it. It is as if in every moment
you are expending it when you have the option to. Just as it is as you
are eating every junkfood imaginable with immense pleasure when you are
fasting. All expenditures, then, of any sort of emotion or pleasure
should be savored and used only when appropriate, only when their value
is needed.

Also, I call this day 2 because I ate icecream and a dunkin donuts bagel
item on Saturday night, though Saturday was a rather succesful day.
ather succesful day. Also, in the sake of keeping this journal as a
logically congruent documentation of my process of improvement, I'll
strictly enforce that 8pm is journal time.

\bigskip
\bigskip
November 2nd, 2018

day 1:

11:00 am

When I say day this time I mean to keep it. This needn't dominate your
life, but write in this journal every day and be cautious in
incorporating new habits. One habit at a time. Anyway, I was prompted to
write in my jounral over a confusion of what disposition I should have.
On one hand we have the extroverted friendly character to play, on the
other we have the solemn, serious and manly disposition. Perhaps the
middle path of these two extremes is to have in your heart the
extroverted individual, and have in your behavior the male. No, this
wouldn't work, it is one extreme. It occurred to me earilier, perhaps
the best way is to pursue actively and with value the things that you
value -- the use of the genius. It is ok that you aren't perfect, but
you must learn. Never must you stray from the pursuit of perfection, but
it is always exceptable not to be perfect. It is even unacceptable to
consider oneself perfect. Yes, that is the fallacy of what's caused my
poor confused disposition. I considered my job done. No, never. There is
work to do, not just within a known framework but in expanding this
framework and discovering frameworks anew. In this way the right now is
everything. There is no far shore, I am already on the shore. Nirvana is
not some distant place, nirvana is ordinary. Nirvana is right in front
of our eyes.

\qquad Now, as far as practical implication goes, I think the solutions
will overlap of my inability to have a consistent monkmode and my
delusion of perfection. Quite simply, modify monk mode to include the
baseline of behaviors, the default. Things like studying, sleeping on
time, and working out. Then we will incorporate, one at a time,
behaviors till they are formed into habit. This allows us to focus on
that thing, to investigate its nuances and modify our approach towards
it to ensure success. Once that is learned, thoroughly investigated, and
incorporated into our person and identity, we will start a new project.
I think two weeks is a good start. So, we will begin with this very
journal, since journaling on a consistent and not sporadic basis is
still something quite foreign. Good day to you, reader, and see you
tomorrow. Looking briefly at my past journal I see how much of an AFC I
am, even so recently as 2 months ago. Grasping at impractical extremes
in an attachment to the past. If I am mediocre, so be it. I wil try to
imporve, but in the event I am unsuccesful, in the event I am a fat
virgin for life, then it has thus happened. I need not cling to the
past, to some prior idea of elitehood. Elitehood is not good enough for
me nor is mediocrity, nothing is good enough for me. Good enough here
means that at some point you are done. I am never done, I take the card
I'm dealt and I play it. That is all. The outcome of the game matters
not, so long as I play it effectively. If my past self did not play it
effectively, that is my past self and that is not me. As I write this I
cease to exist, the time it takes for each letter to display being
plenty enough for the person who conjectured the letter to cease. You
shouldn't think of yourself wholly as a different individual, your past
self is not remy, for example, but you shouldn't necessarily identify
with and feel guilt for those actions. They are indicative of what YOU
might do, so then you should repent to rid your physicality of the
defilements of your past self, but do not feel this personal
responsiblilty.

\bigskip
\bigskip
November 3rd, 2018

day 0:

12:43 the next day

One thing I noticed in my past journals is I always take it as an
oppurtunity to declare ``here and now'' that I'll finally shape up, and
finally become a person I'm not ashamed to be. My natural response is
that I'm not accepting my state and I think it's right. Instead of
always feeling bad about what happened and proclaiming ``I'll finally
change, this time I'll see the light'', it would be better to accept
what I've done, accept that I am the aggregate of my actions, and try to
have the best future. Who I am is not a matter of conscious choice, it
is a dependant result on the conscious choice of action. Who I am right
now is someone who watches meme videos and anime all day, who doesn't
interact with people very much and drinks gatorade because he is
addicted and attached to pleasure. That is who I am, and that is fine.
Tomorrow I will be a new person, yet one with a physical inclination to
such behaviors. Whether the brave soul will handle it in stride and
study for the Buddhism exam or sloth further and watch meme videos or
read the laws of power or the next rational male book all day, that
choice is up to him. Again, I feel like I'm trying to change through
proclamation in this journal. Alright, well then lets change the format.
Instead of a rambling essay of thoughts, we'll have two main essays or
likely paragraphs. First, it will be an analysis of yesterday's journal
and theory. We will have a theory document in which we write down the
theory as we come up with it. Today, for instance, we'll talk about
identity being an aggregate of behavior. The second paragraph will be a
practical analysis of our behavior, or identity for that day. What we
did wrong, what we could've done better. It hurts just to even think
about it, so I will indulge and save that for tomorrow when we don't
have to address such a massive failure complicated by shabbat.

\bigskip
\bigskip
November 4th, 2018

day 1:

10:08 pm

I felt again the same inclination for change through proclamation that I
felt last time, but reading yesterdays journal has helped me reassume
correct frame. I don't have an enormous amount to say about yesterdays
journal except that I agree. I think it is fitting then to summarize the
concepts for retention of the theory. Firstly, the self is a product of
the empty (buddhist empty) physcial body and the soul, which we will not
say is empty nor non-empty, as it is something we fundamentally don't
understand. Who we are, then, is too (also) empty. I am not who I am a
moment ago, there is a connection no doubt, but the individuals are
different. What comprises who I am is my behavior (the influence of my
soul) and its interaction with my body (which is morphed and changed by
prior selves). This is how a congruent individual forms. One may say
that the body is empty and this is true, but it is the basket in which
our experience is aggregated and then prior reality used to communicate
the current reality.

\qquad As for today, the good stuff, I was holy unable to do buddhism
work today. I think it must be a result of my failures and indulgences
in immediate gratification of yesterday. I had a bad headache and felt
fatigued, as well as very hot, every time I tried to study. Before we
take the practical steps as to how to fix this, let us investigate some
theory behind the observation. What comes to mind is the idea that my
mind began its acclimation to false reality yesterday, and that this
headache is a result of its now unacclimated state to proper reality.
Lets expand on this. The mind acclimates to whatever reality the soul
chooses to adopt. Yesterday I think I took steps to incorporate what was
a false reality into my own reality, not just rejecting my own reality
but through delusion deigning to accept it and the false reality, which
necessarily contradict eachother. Through this belief that I was
actually accepting a true reality, I was able to convinve myself,
well\ldots{} convincingly, to readily believe the false reality I had
produced through morphing myth and truth. My, in both not being suited
to that reality and beginning the acclimation process, rewired itself
into the mess we find today, where I'm disconnected with my genius and
incapable of studying.

\qquad Since this is a physical sensation I am experiencing, I am also
lead to believe that there are physical causes behind my ailment. My
diet was heavy in sugar, heavy in menthol, and was very sedentary. I
didn't get as much sun as a should. Well, I feel right now very hot,
very uncomfortable, and sort of ``icky''. I feel like a plague, unclean.
As part of my healing I'll then do everything in my power to feel clean
and cool. Firstly, the nails must be preserved. No nail biting.
Secondly, our food must be healthy. Shredded wheat and milk, no greasy
carbs. No cheese, probably no chabad lunches. We'll do it formally in
the monk mode. We'll update on the success tomorrow, I feel I'm so out
of it, I feel what I'm writing is completely incoherent so I'll stop
here.

\bigskip
\bigskip
November 7th, 2018

day 1:

12:57 pm

I abandoned my monk mode when studying for Buddhism, now the exam is
behind us. I was going to jounral now, but my mental state wouldn't be
able to describe what I experienced yesterday adequately.

\bigskip
\bigskip
November 8th, 2018

day 1:

2:39 pm

Aaand failure. What I experienced yesterday was a pure sort of focused
state, but I readily shifted back to the attached self. It was sort of
like the edge of death, like the present doesn't matter because a great
journey is ahead. I wouldn't pursue what was yesterday, I'll just
continue as I am. Also, fast is going exceedingly well, but in building
this potential for food I must be careful not to spend it. Frivolously
and be bankrupt once more. You should be rich with all the things you
could eat, yet never spend your riches in order to maintain security.
Tomorrow is Mono diet time. We will live off Shredded wheat with milk
and tea.

8:57 pm

Well, today has been a success. I held frame for the most part, whenever
I used the internet I asked myself ``What is it I'm using the internet
for''. Day 2 is a long time coming, lets not fuck it up. Tomorrow will
be monodiet except meat on Shabbat. After Sammy communicated through
Rebecca that he has issue with my interaction with the chabad girls,
I've resigned to not interact with them. Sammy was mad and his anger was
making me mad and disturbing me. I told him I won't interact with him
until he relieves the tension, which I am always open to do. This was a
good diagnosis. Now, back to monk mode and the such, I didn't study much
today, nor did I go to class in the morning, nor did I work out, but all
is well. This day 1 is a precursor because we fasted. Tomorrow we'll
also start our precursor week with the monodiet. We'll be allowed lean
meat (grilled chicken, burgers, steak)

\bigskip
\bigskip
November 10th, 2018

day 1:

5:39 pm

Only because was drinking last night and lost frame. Don't drink anymore
as a rule, you don't need it for game. Otherwise I held frame well
enough through Shabbat. Lost it on discord and temple OS, but recovered
especially with music.

\bigskip
\bigskip
November 11th, 2018

day 2:

1:31 pm

How quickly we are susceptible to insanity. I've lost frame, and I can't
seem to retain it. The only way I was able to save myself was from 1- my
admission to kurt that he can have the icecream, so that if I eat it
there is shame, and 2 -- classical music. Even now, I'm on a steady
mental IV drip of classical reading music just to prevent myself from
relapse. This journal is also serving that very purpose. I believe it
was the food. I didn't need to eat, I chose to eat. Never choose to eat,
be forced to eat. There are always options, don't fret for timing, with
anything, ever. Pursue food when hungry, and be late. The body can
compensate, a missed meal here, and extra there. It should work and lets
try this strategy. Only puruse food when you feel a need.

\bigskip
\bigskip
November 13th, 2018

day 0;

10:58 pm

Really didn't want to do this journal right now and that's precisely why
I've done it. I've lost my 83 day streak and fapped, once twice and
three times. Today is day 0 and if we keep it our streak will be
consistent for both monkmode and nofap, which is convenient. So don't
fuck this one up. Very high energy from the caffeine, just took 111
midterm2. Anyway, so what went wrong was a loss of frame, of
realization, of the positive benefits of monk mode. The prize escaped
me. It's not good enough for me to consciously recognize it, this
position isn't strong enough. I must emotionally feel it's value. An
easy way to do this is to befriend many women, of course, and perhaps
this is the route I'll take. I should hang out with women more, be more
aggressive and get numbers, hang out, everything. Female friends can be
your salvation, but of course not alone. If you use them to escape doing
work you will fail. Work must still be the number 1 priority. Study up
that linear algebra tonight, since you won't be asleep for any time
soon. Lets get fucking cracking nigga. Monk Mode whatever begins.

\bigskip
\bigskip
November 16th, 2018

1:25 next day

Failure here, failure there, failure really everywhere. Up, down, all
around. I hate it. I hate that k watch movies. I hate that I'm addicted
to YouTube. I hate that I am dependent on these immediate
gratifications, that I can be conversation with someone and my energy is
dead, that it suddenly is a burden for me to talk to them. I hate the
headaches, I hate the impact it has on my psyche, j hate how it requires
my brain to crave and respond to and seek out this shit, how my brain
has interpreted reality from the standpoint of it's necessity. Why can I
just not want to waste time, why can I just never get tired of working.
Well, hang on a tick, physically I think it should be possible. Now, our
Lin alg midterm may be a failure, this is unavoidable. Further, being
20\% of our grade a failure can be really bad. So, it's very possible
because of our incompetence we'll only get a b+. If that happens, so be
it. We weren't ready. The failure is then perfect. If it is a result of
my behavior it is the reality that is a perfect remedy to my crippled
soul.

\bigskip
\bigskip
November 17th, 2018

day 0:

4:37 pm

So, we fapped again and found the source of the headaches. Very clearly,
it was fapping. So, now we will try an extremist idea. There is the
concern, of course, that it will be too extreme. EVEN IF IT IS NOT
OPTIMAL. I repeat, even if it is not optimal or even very far from
optimal to act this way, it is certainly better than what we fear is
inevitable relapse. Go to monk mode and update it.

5:33pm

Cut the bullshit. Our systems aren't linearly independent because deep
down we know we've been full of shit.

\bigskip
\bigskip
November 21st, 2018

Day 1:

10:42 an

I'm considering starting a new journal. Right now, at least, there is no
question or anything to consider. There is only improve and get better,
with the acceptance that our current state is sick.

\bigskip
\bigskip
December 5th, 2018

day 4:

12:12 am

From the wisdom of Pook I have made a revelation. When meditating, one
is enabled to see their true nature, their buddha nature. But wait, one
may ask, if one's true masculine nature is to be that uncompromising
idea we know is succesful with women, how can this be when typical
buddha nature is not like this? How can one have compassion in this way?
You fool! You great fool! You do not see compassion for it's true
nature. It is not compassionate to be nice to women, it is not
compassionate to cater to them, to laugh at their jokes when they are
not funny, to give them unearned kindnesses. Nor is this compassionate
to do for a man. Should it be that people are rewarded for no merit? We
know this reward, we are regretably familiar with it. The reward of no
merit, pornography, has brought us nothing but sadness, nothing but deep
debilitating depression. Do not reward a woman for doing something
beyond your interests, for it is not in your nature to do so and,
therefore, not within her nature to be rewarded. Reward without merit
must be extended to those only in need. Just as honey is healthy to the
sick, it is harmful to those of good constitution. Hold for all people
the utmost compassion by rewarding them for nothing, by \textbf{never
compromising your own goals for theirs}, by enjoying life in your true
nature, without concern for theirs, for God in his perfection
constructed us that your true nature will never compromise another
individual. To be true to yourself is to be compassionate to all others.
To be compassionate to your self is instrinsically coupled with being
compassionate to others. We all win together, or we all lose, you more
than others. To win for yourself, then, is to claim victory for all of
humanity. \textbf{Claim this victory. Embody your nature as a man. The
desires of a man}.

\bigskip
\bigskip
December 27th, 2018

day 0:

2:13 next day

Deep, debilitating relapse. A fatigue only known to those at rock
bottom. Everything has been prepared. Tomorrow I must begin anew, but I
don't face tomorrow empty handed. I am armed with knowledge and wisdom.

1- You must study things, and they must be hard. We will do very
difficult CP problems tomorrow, no need for baby shit.

2- The conditions for happiness are not of this world. They are
respective to a moment, and within the realm of your soul. To be truly
happy for a moment, one must seek to see the truth. Then they will be
happy.

What can I say that would be unique? I've had this very journal entry
many many times. What do I do? I psych myself up? I proclaim,
desperately holding on to a mindset I am scared shitless I will lose,
that this time I'll be different, that this time I'll change. It never
happens though. Why doesn't matter to me. I simply attribute it to my
own desires as reflective of my own attachments that I refuse to cede.
Cede all attachment. That's it. I'll do that. I'll pray here that God
helps me, though I don't even need him to help me especially more than
he currently does. I have all the faculties necessary to lose
attachment. I need simply do it. That's all.

Also, as successful as I was in my classes and all that, I shouldn't
look on my streak as success that I need to reach. I was still watching
YouTube and garbage every other day. That wasn't success at all, it was
corruption that avoided fapping purely for symbolic value and not a
continued wisdom. If I ever feel myself faltering in wisdom, I should
eat something (ensure I'm not tired) and then re align myself with the
truths above.

\bigskip
\bigskip
February 1st, 2019

8:18am

I haven't put a day counter up because I'm afraid putting a 0 might
deceive and entice me to relapse, while a 1js disingenuous. I haven't
journaled in over a month, nofap is on a 36 day streak, though I was
very close last night and urges still present this morning. I went on
Kik and Omegle again, thank God I didn't get any nudes. Also had a good
streak going of waking up at 5:30. When I start that again, I need to
focus especially on meaningful work. I also need to investigate clubs
literally asap. There is a longing in my heart. I feel alone. And yet we
have control over this, we should be able to just be happy, but we lose
sight of things. Even now, my negative conception is bullshit. I need my
own fucking room too, or someone who wakes up as early as me at least.
Not this 9am bullshit. Honestly don't know if there's anything useful to
right rn. I'd like to focus on essays about theory in here moving
forward. Instead of responding to people on Reddit, respond to yourself.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\bigskip
\bigskip
February 14th, 2019

Day 1:

11:00pm

In this new Journal, there won't be ramblings of my emotional diarrhea,
but valuable ideas. If you wouldn't send shit to a friend, you shouldn't
send shit to yourself.

As a result of the dopamine fast (which is also a regular fast) I slept
a lot more and feel much better. I'm much more free than I was, though I
don't yet feel fully in control. We should be absolutely free to pursue
what we want.

My mind seems open to suggestion and emotion.

New Journal

\bigskip
\bigskip
February 19th, 2019

11:57 pm

Wow, so quick and so insightful. He is right, I am focusing on marginal
things that will magicaly make me better, but nothing will happen this
way. I lose sight of motivation because there is no improvement.
Suffering for the sake of it is not a goal in and of itself, it is not
an achievement. Here is an achievement. Bench press 1.5x your body
weight by next January. I currently weigh 170 pounds, if I lose weight
that 150. Bench press 225 by January.

Goals:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  To weigh 150 pounds by the end of the semester (3 months).
\item
  To be a week ahead of all my classes, while on track for a 4.0.
\item
  To have a morning routine of waking up at 5:30, praying, running 5
  days a week, and then lifting for 3 days a week for 30 days, until
  March 20th
\end{enumerate}

I've rediscovered a fire of perfection under me again. No more. No more.
No more. Fuck that video, I don't need it, it will only serve to sap me
of my convictions as so much immediate gratification has. For God, but
also for me. I want to complete these goals so I am a better man, one
able to utilize the faculties upon whom God bestowed me.

\bigskip
\bigskip
February 20th, 2019

8:07 am

I woke up at 5:30 this morning and felt the same lack of conviction that
has characterized my life since I relapsed from my morning routine, but
likely was even present throughout everything. I asked myself again, why
am I doing this. I then read the Tora for an hour or two, stopping after
chapter 28 of bereshit. I answered this in my notes:

Why am I doing this?

Why do i want to lose weight?

Why do i want to get good grades and master my subjects?

Why do i want to wake up at 5:30 every morning and pray, then have a
fitness routine?

I will be honest here so that the path i take is accurate of the desires
of my soul, so that ill stick to this path. There is a long tradition of
men in my house, though my connection of them may have felt weak, it has
always been strong. I am the son of their sons, an heir to the house of
Jaacob. They are my tribe, and this tribe is one of honor, but God's
honor. One of capability and righteousness. We've enacted a covenant
with God to fulfill his misvot. In this fulfillment we achieve our
ultimate actualization, prophecy. We will achieve an ultimate pleasure
directly, intimately linked and as a result of that reality. Slowly, as
we begin and continue to pursue prophecy and a closeness with God, we
will see a healing of our soul, rhe restoration of our humanity we feel
being lost. We may connect eith people, accepting them as the imperfect
beings they are and not expecting of them beyond their means. There is a
certain feeling now as if on the cusp of the end of a reality amd the
beginning of a new one, bringing excitement for the future, coming with
the light like a spring bearing the future. In truth, isn't every moment
the end of a past and the beginning of a future?

With that being articulated I hope to maintain a motivation to keep to
the misvot, encompassing all the positive and beneficial
qualities/achievements I seek and more.

\bigskip
\bigskip
February 22nd, 2019

3:08 am

It's been a few days since I've started my new goal focused program. The
largest difference now is my diet, where I eat little and savor every
bite. I've also started to really push myself in being productive. I try
to do work every day, and though I'm not meeting all of my quotas, I'm
meeting some of them. For example, though it was difficult I finished
reading expos today, which took about 2 hours because of the
inefficiency and inability of my focus. That is something to work on
every day.

I'll also mention that I feel my mind healing. I wrote on Reddit about
how I felt dead, emotionally disconnected and without emotion to
motivate my behavior. Now, my emotions are being restored. This is a
result, I think, from disengaging with sources of immediate
gratification, most notably food, and also through the consideration and
visualization of tangible goals, emotion then being incited by past
experience suggesting what it might feel like to achieve them.

\bigskip
\bigskip
February 23rd, 2019

7:13 pm

I fapped last night and binged on milk and irish cream. In starting a
new plan to recover I've identified 3 categories of behavior.

There is Do:

mentally or physically strenuous work that engages all one's faculties.
This includes dedicated study and intelligent production.

There is Wait:

behaviors that don't engage one's faculties yet take up time. This
includes resting, meditation, errands, and pipe smoking.

And there is Consume:

A passive engagement of one's faculties, your faculties being engaged
for you. This includes immediate gratification,
over-eating/pleasure-eating, and consumption of material for the sake of
it.

On consumption:

It typically utilizes the senses, overexciting our emotions through
delusions as falsehoods or compartmentalizing interdependent reality, or
physical senses through hyper stimulation (food, sex).

What we suffer from is an addiction to consumption, and an aversion to
doing. Doing brings you, apart from financial security, grounding and
confidence, assurance and healing. It is the foundation for growth that
underscores fulfillment. Consumption overuse stems from a lack of doing,
and our lack of doing stems from our aversion to it. It is a cycle, the
more we consume, the less we are able to do and the less we do, the more
we are inclined to consume. The new program, then, will be to restrict
almost entirely consumption and focus on doing. Why almost and not
entirely eliminate consumption is some behaviors innately harbor some
consumption, but it is in combination with other things. Watching a
play, for example, has some consumption but then has doing in the form
of the plays interpretation. Similarly, pipe smoking has some
consumption in tasting the smoke, but a small amount of doing in keeping
it lit and then is mostly waiting. Most of these things will count as
waiting, but will still be restricted in use. Which brings us into the
important topic of waiting. When we attempt to Do, we will encounter
resistance because of our aversion. Like a muscle, our capacity to Do is
weak when we haven't Done. We must Do more and more every day, starting
with what we can (Doing until failure) and Doing more the next day,
after we've resting and our capacity is greater. When not doing, it is
important not to usurp this capacity by consuming, and thus we will wait
most of the time, doing when capable. Succinctly, then, the new program
is this:

Maximize Do, Wait when needed, never Consume.

\bigskip
\bigskip
February 27th, 2019

2:39 am

My sleep schedule has been pretty insane lately and I've been using it
as an excuse to be mediocre in aspects. This is ok, tomorrow I start the
whole working plan. Writing my expos essay has unexpectedly enough
(since I thought they would be of zero value) provided me with a bit of
a realization, a tiny one. The Above is true, with Wait, Do, and
Consume, but separate from Do and perhaps filling a need for interaction
or entertainment is Produce. The idea really bloomed after thinking on
the consumerism of today, how we just buy and buy with no using. What I
keep doing with information is essentially buying and buying, without
using and appreciating what I have. I then, in addition to no consume,
want to truly solidify that with not a quota but an allowance for
Produce, in journal but also on Reddit. I feel giddy and excited, even
though we should be nervous for exams, so that's good. God does his
work.

\bigskip
\bigskip
April 15th, 2019

10:30 pm

It's time, once again, to attempt to get my life on track. Seeing the
fruits of success, not just of being top lobster, but of developing
powerful emotions with other people, creating a thus powerful bond. When
looking at my last lecture, of my losing weight and how far I've come, I
was then motivated to pursue the greatness I once had. Looking at me in
that attractive body is especially so appealing. It represents value. It
represents social acceptance, a security necessary for greatness.
Looking at Mazlows hierarchy, hitting social acceptance unlocks new
things. Upgrading 10\% up the line moves you 50\% up in productivity. I
think we were most successful when we did cold showers at 5:30 every
morning. Tomorrow when we wake up and nominally can't fathom reality,
remember greatness. Remember how good it felt when we were offered by
Marshall, how good it felt to feel a powerful powerful emotion, in both
sharing your vulnerabilities with others and in being accepted
thereafter. It is a love, for all of it. You can find love for God, it
is there. For the love of God pursue it.

The new plan:

Essentially, I think we had a very good thing going with the cold
showers and lifting program, let's try to get back on that.

Morning routine:

Wake up 5:30

Cold Shower

Pray

Write something motivating, something real. A journal entry is good. For
now those will be in consolidated, later can be moved if it works.

Run -- don't kill yourself but sweat.

Take a 20 minute break, listen to music or do something creative though
lets stay away from youtube. Reddit is ok. Smoking a pipe would be
alright if the occasion permits ( longer break needed). If new episode
of OPM is out that too is ok, only that though. This is short, not so
long.

Go to library and get to work. On the breaks here, do something that
isn't IG (Immediate Gratification). Maybe even a power nap.

Diet:

Full kosher at the dining halls, so no cheese anything. No sugar or
obviously unhealthy stuff. Simple carbs only if you have to. Try to get
protein in.

Exercise:

4x cardio and 2x weights I do think is a good system. Lets keep it.

General restrictions:

Big things to avoid are youtube/reddit/IG, sugar/food pleasure, breaking
Tora, and poor values.

\bigskip
\bigskip
April 16th, 2019

8:21 am

The life goal, what we should pursue in the moment, is not happiness but
what is good for our soul. There is something wrong with us, we are in
exile after all. Happiness in this state is never true happiness. What
we can do to be content is heal our soul, do what is good for it. This
means follow God, follow what you know is good. When I say this I'm
reminded of the misery I might feel and the nihilism that will say
``fuck it, let's just watch YouTube what's the point anyway''. That
voice, that lack of awareness is a poison. Even now, I feel the lack of
awareness -- so focus. Good, get back your awareness of what we should
do and pursue.

\bigskip
\bigskip
April 17th, 2019

8:44 am

I am fatigued but if I give into the fatigue I know it only leads to
awakened and energetic misery. Be peaceful with the body, such
entertainments aren't peaceful, they're a strain, a sour and twisted
one. They will only work to sour and corrupt you, so that you can't be
peaceful with the intellect. If you are fatigued, then be slow for a
time, that's it.

\bigskip
\bigskip
April 18th, 2019

12:20 pm

I feel myself slipping. Yesterday we were very lethargic, we didn't go
hard. The real joy only comes from going all the way, no half ass
anxieties. Don't watch the porn of a shit life, eliminate it. Get back
at it. If not at the gym, then in the books.

\bigskip
\bigskip
April 22nd, 2019

10:24 pm

It comes time to ask the question, what do I want out of life. My life
is out of control, being swayed back and forth by the rivers of
circumstance. I act, not with soul, but with animalistic inclination. It
comes time, then, to consider being on the most abstract level of what
it is I aim to achieve in life. I've always responded, immediately, with
``prophecy'', but this argument is no longer convincing and I find
myself switching back and forth from the life of pleasure to the life of
toil, the life of pleasure being my default state and the life of toil
what I believe to be an ideal, and I'm fighting my nature in order to
live the life of toil. I am rather sick of fighting my nature. If
necessary I will, but wouldn't it be far better if my nature aligned
with the authority of God? Perhaps, then, I can change it. This is thus
an exploration of my nature. At the moment, my nature is very
confidently the life of pleasure. I haven't considered or comprehended
this choice with my being, because I've always regarded it as temporary.
Now I will regard it permanently.

The life of pleasure:

The aim here is to do what is absolutely necessary for survival, for
provisioning sake, and then spend the rest of your time devoted to
pleasure and enjoying life. For the sake of consideration, lets say we
studied game to the necessary capacity and lets say we developed,
somehow through personality, money, or other, a popularity so that we
had the pleasure of people in addition to that of technology and
materials. Essentially, lets consider the life of the hedonistic King as
the ideal here. He need not work, he need not toil. He merely enjoys and
consumes. He fucks women, eats to obesity, heartily laughs with friends,
plays videogames to his whim's desires, watching television series when
tired.

Review of past journal:

I talk of a ``nectar of genius'' and that ``to lose it is unthinkable''.
I don't even know what this is. Is this what is worth pursuing as a life
goal?

I later retrospected about this beginning. Even then, I had an
``analytical nature'' of intelligence. I've now realized something I
suppose has been forgotten for the past few months. My intelligence has
died. We've seen my eloquence dissolve away, but further I don't think
like I used to. The intelligent discourse, the analytical and
impassioned search for truth is gone, burned out and smothered. This was
something beautiful, and I feel good now to feel sad about it's loss. Is
it something I can get back, but more importantly, is this something I
want? Is it something worth pursuing? I look back and, perhaps because
of a nostalgia, perhaps because of a grief, I feel quite sad. I feel a
passion, and this passion is a gift from God. I must harvest it into
action. I've been living the past months of my life in self destruction,
in meandering confusion, in deadened awakeness. I believe this past
retrospection has enabled me to enter anew state of consciousness. I'm
on a search for truth, for God. The fanatics life is wrought with
emotion, I am desperate to maintain it, carefully stepping with my words
and thoughts.

Do I dare even make a life plan? Do I dare associate myself with the
past efforts of failure and despair? I feel, now, meditation is possible
and of use. We still need articulate our planned procedure of life.
Whatever it is God commands of me to achieve prophecy, I shall pursue. I
yet need be open to what that is. The social character perhaps limits
me, it sentences me to stupidity. I don't know at this time how it is I
should act regarding others. Perhaps a new monk mode is finally in
order.

To summarize here of what we must do with our life. God is the only
answer. The fat King is starving. I am starving. The end is not in
people, the end is not in women, the end is in God. In prophecy. I seek
to perceive truly.

Monk Mode 2-1 : Have we yet escaped the desert?

Enforcements:

Religion:

I must do everything in my power to facilitate the state of
consciousness that is this prophecy, that is this heavily emotional
desire. Completely adhering to the commandments of the religion is part
of this.

Health:

Physical ailments impede my prophecy, they impede my clear vision. I
must do everything in my power to create a healthful body, so that I am
better able to perceive truly.

School/career:

I need take care of my school work to the extent necessary that I am not
anxious about it, that it doesn't take my mental realestate and
therethrough impede my efforts to perceive truly. This means studying
for and completing assignments on time in a timely manner.

Restrictions:

Immediate Gratifications:

These are idols for the mind. They are not the reality of God. Youtube
is an idol, Netflix, all of it an idol, human fabrications. I need
perceive the world. It should not be separated from my mind as a
mysterious unknown. Do not block it on webblocker. Instead it should be
fathomed, though we should not take it's idols.

Junk food:

These impede our perception by negatively effecting our health. They
cause stomach aches and disturbances. You have a sense of which foods
won't hurt you, use this sense.

Fapping:

This hurts you by utilizing a sexual energy in an improper manner. It
should be used in profound service to God, in presence of a woman. When
fapping you corrupt yourself through an incomplete incoherent behavior.

\bigskip
\bigskip
April 24th, 2019

Day 0:

11:22pm

We knew on Monday what we were writing was a bunch of whoreshit, it was
simply better to explore what we have than remain with nothing. There is
no such thing as my ``nature'', and Jordan Peterson's bleak view is dark
dump of bullshit. What you experience now is, in part, a product of your
past behaviors. To do what is right and just, what brings meaningful
existence and contentment to the mind, what best enables you to serve
God, to do what makes you more than another worthless pile of crap among
worthless piles of crap, is an amount of hard work. It is neither
struggle nor rest, to characterize behaviors incorrectly as such is to
project human conception on reality and therein skew our behavioral
adjustments. A plan must be made with discipline, for try as we might
the mind cannot always be in ``prophetic'' awareness of seeing clearly
and truly. There must be ritual, discipline, and blind trust to bolster
being when the mind is weakened or physically limited. Drawing from
Goggins, we will make a plan of discipline now, realization later. Our
undisciplined, fap stricken, candy weakened, lethargically inclined,
nihilistic, and shrouded mental and physical state is not ready (or
feasibly capable) of proper realization, and as a result we are throwing
what is logically immensely valuable, perhaps even all that is valuable,
down the toilet. There will be toil and struggle and hardship and
horror, but it will lead to the wisdom for which we are so desperate. To
see we must first claw away the tumors impeding our vision, tumors that
have been there for 20 years.

The plan:

Wake up at 5:30 in the morning. A new environment builds new routine.

Cold shower an incrementing amount, then pray, then meditate, then
exercise.

A schedule be made and followed, with 1 hour of school studying
dedicated each day excluding 24+ hour holidays.

3 meals a day of bland or healthy foods.

Reddit will be allowed for r/nofap as it helps in reforming my mind to
discipline others as I should myself. Otherwise, no videos that aren't
educational, no Facebook YouTube Snapchat etc. Bring certain social
platforms back on later when we are responsible. This will be more
explicitly fleshed out as we encounter issues.

\bigskip
\bigskip
May 16th, 2019

10:06 pm

As I was reading Mastery (one of Robert Greene's books), he described
how we may learn with a certain creative passion and energetic, more
capable capacity. That we might learn faster and more readily solidify
things in our brain. When looking at the great masters, indeed, what
seems to differentiate all of them is that they started working in
whatever it is they were great at very early. For Mozart this was very
young, and Einstein it was 16. This then filled me with a regret, or
perhaps, unhappiness that I wasted so many crucial years not pursuing
things with such a vigor and passion. That my capacity for great
learning which I sometimes have an inkling of is stifled by my own
stupidity and misbehavior.

The problem here is that this disagrees with our axioms of happiness is
always attainable. I wish then to explore this. What if I were to waste
the next ten years of my life, the next twenty? What if I am to be
inevitably mediocre. What path then do I still have to happiness.

And now whatever it was, that last spark I was endeavoring to write
upon, it is entirely lost. Perhaps I can reclaim that idea\ldots{} No,
it's all gone. At the very least, the negative emotion I sought to
eliminate is eliminated, but is this not a result or symptom of my own
emotional disconnect due to my abuse of immediate pleasure, internet and
fapping and so forth? Once I am more in tune to things, which will take
time doing things properly, perhaps this regret will come up again, and
philosophy developed to deal with it.

\bigskip
\bigskip
May 20th, 2019

4:53 pm

After just writing a damage report, I feel an urge to remind ourselves
not to forget how close to relapse we always are. How a life of horror
and regression is very close. Further, of how we derive such great
pleasure from success, both physical and career wise. I see how this
success is certainly the path to finally exercise the emotions which we
by necessity repress. Never forget, you, as you currently are, are
absolutely defective, incapable of securing a woman's love. This must be
changed. It must, and the two known vehicles of this change in which we
can place confidence are working out/dieting -- perfecting our body, and
being successful in our career -- securing a respectable rank in
society. May God help us, that we may upgrade our life condition yet.

\bigskip
\bigskip
May 23rd, 2019

10:51 am

When we speak too much, we often get carried away by emotion. Speaking
is so habitual we prostrate ourselves before our sisters in letting our
tongue run loose. We use a near baby's voice when we communicate with
our family. Observe, how the literal pitch changes when we talk to those
family versus when we talk to strangers. Last night, as a realizing
communication, Rosa and Jaime started to ridicule me. Called me annoying
and the such, when I said certain things are bullshit. This wasn't,
however, an attack on my idea, but an attack on my person. I, in my
whole, was deemed ``annoying'' and this was said with a smile on the
face, as if, ``we think nothing of you, you are near worthless, but
perhaps on occasion you are good company -- though certainly not worth
any effort to preserve. I will then ridicule you as I please, and I do
so lightheartedly, for I don't anticipate a conflict. You will simply
submit, you won't do shit.'' This relationship is utterly toxic to the
soul. I came to a realization last night, when motivated by this affront
to think of them critically, that they don't offer much. They are
feminists, deny the necessity of hard work, are entitled, and by god
have the indecency to prostrate me before my very eyes. And thus, with
that realization, I began to be more cold to them. More deliberate, more
Machiavellian, more within my own interests. I put a flag on my
thoughts, claimed them as mine. You can't have them unless I expressly
permit your having them. The good faith has been breached. But, this
behavior resultant from the new paradigm, this behavior is what should
be held in near all interactions.

This is, perhaps, a pre alpha stage. Territories, now, are in
transition. I am conquering what I had for so many years ceded. For the
moment, I will be at war in conquering this new position. What will be
alpha, later, is once my claim is situated and found solid, once I have
given it a worthy defense against the attackers that may come, only then
might I be absolutely confident in my claim and, from this position
without wanting and worry, I might exercise some compassion and good
will towards them. Till this point, I need be at war. Just as is
necessary in real war, there is no room for jesting or relaxation in
this dominance struggle. An anxiety and a caution will be absolutely
necessary. You may not, and should not, have much fun with them for a
long time. Become distant, absent.

The same is to go for Sammy. We are shit on, every day, by him. We are
always torn because on one hand we want to interact with him as feels
natural. On the other we can't support him prostrating us. When we
become distant, observe how he even attempts to bring us back to a
friendly and jesting state, by poking and making nice and the such. Why?
Because by resituating that state, he maintains his power to me in the
relationship. He still gets to shit on me. It is his counterattack.
``You want to be respected? Watch, I will bring you back to prostrated
goochie goochie play time and you will submit like the child you are.
Get back to your cell, bitch, you have no back bone you have nothing but
empty desires backing what you say.'' We should, then, make the attack
and reclaim what is not a difficultly defended position of at least
self-respect. We should expect a counterattack, no question. I doubt
people are wont to lose territory, even if it is of little use to them.
At the very least we've shown that Sammy will fight back. This campaign
is as, if not more, important than any other we're currently endeavoring
upon to fix our shit life. It should be treated with an equal amount of
care and caution.

\qquad As for how to practically implement this war, perhaps we can not
speak to them, any of them, unless absolutely necessary. This may pose a
number of issues, though. For one, they may try to talk to us. For now I
seem burnt out, I'll finish editing here, but the campaign still
requires further consideration. For now, the strategy will be this: Do
not talk to them outside of logistics. This isn't to say you should
necessarily assume an ``I don't care'' aloof attitude, that would be
alpha behavior, which is perhaps not appropriate for war. No. My
attitude shouldn't be ``I don't care, I won't engage in conflict''. The
interaction should be a battle, as is appropriate for war. Instead of
saying ``I'm sorry Jaime, I don't really care''. Say, with intention of
readily escalating to outright illogical conflict if necessary, ``Jaime,
I don't care''. The problem is, we feel as if need hide the fact that we
are in a campaign at all. This is not a coup; this is a conquest. There
is no hiding it. Be upfront in what you are doing. Keep in mind, ``I am
important, what I'm doing matters more than whatever you could possibly
contribute to and thus I don't care for your presence or interaction.
For a long time, I have been prostrated by you. For the time being,
then, you will leave me be.'' Also, further keep in mind that we aren't
to talk to them like a pussy, that is, as if they are a child out of
behavior. No, acknowledge them for what they are, warriors and my past
lords. Treat them with a respect, and to this figure of respect,
proclaim, ``I am taking what has been yours for too long, what I have a
right to, and that is the respects of my person.''

\bigskip
\bigskip
May 26th, 2019

11:34 am

Last night, after going to sleep far too late, I had a dream. I had been
selected because of some circumstance to enter a competition in which
participants were given a ``capability'' value corresponding to
advantage in the game. Mine was initially higher, instead of starting at
0 it was 1, and it all culminated in ultimate purpose, I believe, to the
fantasy that I was ``special''. A signifier of value or condition of
happiness dependent on other people. I, obviously, dispelled that to the
best of my ability knowing the futility as I do in such an evaluation,
but I don't know if I yet see the solution for which true happiness is
actually obtained, as something independent of all people, or at least
their perceptions anyway as in vanity and so forth.

\qquad I'll leave that thought as that, but the main reason I found it
necessary to write a journal, once again, was my extreme discontent,
lethargy, and mental instability this morning. I felt physically ill
overcome by a horrid fatigue this morning that, in spite of sleeping in,
I despised nothing more than getting out of bed. I spent a large amount
of time in bed on my phone, as I would often do, reading some wikepedia
at first but then reading Roosh's eulogy for his sister. In truth, that
is a complex jungle of a matter which is yet still entirely foreign to
us. Its only use would be to detract us from our purpose right now,
which is to fix our shit life.

\qquad A number of things are then on the agenda, and because our mind
has become confused and lost purpose we will reiterate the entire plan
here.

Firstly, we must abstain from immediate gratification and dopamine
pleasures, so as to accustom our mind to natural being and superior
capacities of awareness that need be trained. Explicitly, for I feel
some anxiety in the leeway of this decree, let us address Reddit,
Wikipedia, and fiction books. Observe how their use has brought troubled
and busy worry to our lives. Observe how we are unacquainted with our
nature and being once again. How there is a positive poison, a barrier
impeding this. They can't just be ignored, these barriers, they must be
addressed. On reddit, we will just use it as a sight for research in
MaleFashionAdvice as well as any other fields that suit our fancy. We
may post as is useful to these research purposes only, and it may only
be on the desktop. As for Wikipedia, we don't need it. Fiction novels we
will exclude to shabbat, reserving for all other times non fiction
(mastery, for now).

Second, our OCD compulsion of nail biting. In brief, we will absolute
refuse all compulsions as they come, cutting our nails short yet
somewhat visually appealing. Also do exercises which we will determine
in detail later, but for now let us look at our nails often, observe
their capacity to be bitten, and the refuse to bite them.

I've grown tired now, perhaps we'll finish when we are more mentally
capable, for now with the above changes we'll just continue our same
plan.

\bigskip
\bigskip
June 2nd, 2019

1:30 pm

It's dawned on me that all of my motivation is rather short lived, in
the span of a week or two, because it doesn't apply well to the right
now. The grandiose motivational incentive of a better life or of
prophecy needs to be met with a short term reward. Or my frame so long
term that I can accurately envision a cycle of hell from which I never
escape that is relapse and mediocrity without that which matters truly,
prophecy. In my head I'll justify relapse. ``Its just one day''. The
answer is not to foolishly imagine that one day equals many, for it is
true one day is only one day. Rather, we should truly perceive the value
of a single day. It should be thus that my rewards aren't only in the
future, but immediate. Perhaps an immediate benefit to my soul. The
philosophy I take on should produce the same behavior if today is
assumed to be our last day or if it is assumed we live till 100.

\bigskip
\bigskip
July 14th, 2019

12:30pm

I've opted to write this entry in the journal rather than in the damage
report because I expect to come to some philosophical exploration, as
oppose to a simple damage reevaluation. Where I'm at right now, since
starting my job really, is new territory. We haven't had this much
success in a long time. Not that we've been so blitheringly successful,
but compared to what we were (and have recently regressed to) we have.
When I chose to watch youtube and Netflix again on Shabbat, it was an
effort to hide from our reality. In the house we were uncomfortable.
Surrounded by the wise father and, otherwise, enemies but no friends. No
persons of companionship, an incomplete tribe. Further, I had no purpose
of my own to supercede social pursuits. For whatever reason, I was only
half interested in academic/philosophical pursuits. Perhaps because
social development with men too, but mostly women, has been a focus for
me. In short, my life at that present wasn't quite bearable or
enjoyable. When I went to work, I had something to do. I woke up, drove,
worked, drove back, exercise, and had miniscule time for life, bullshit
or otherwise. The little time I did have was easily filled with friends
or other beneficial activities. Now, however, when I have no such
productive distraction, no such autopilot, I am left to face my stark
reality. In truth, it is one I'm unhappy with. I don't have my own place
to improve. I don't have women quite yet in my life. I don't have a
business or something to grow. I don't have a personal project of some
variety to drive me, or not one that I've started viably and seriously
yet.

And it is thus, that having nothing to do when awakened from corporate
employment I turn once again to pleasure and poison. In short, I have
yet to develop a life of my own to focus on, build upon, and improve. I
continue to drift as I did throughout all my adolescent years, which
should have remained in my adolescent years, caught in undecided
experience with the winds of life. I get happy when I see my improving
physique, my improving ability with women, for they are resources and
tools with which to build my life. But, I have yet to start this
building process. Perhaps, in part, because it makes me incredibly
nervous that I may begin to assign and devote resources incorrectly. I
don't really know in what direction I want to take my life.

General statistics and computer science, perhaps, but where should I
truly be going with all of this. Perhaps it is a safe option to pursue
social development with experience and pleasure, as many do at this age,
as a primary goal in a sort of incubation phase before you're ready to
make a decision of your career specialization and life direction. I do
feel as though, whatever I do commit to, it must feel right in the
bottom of my gut. It must have security and promise. This sense I feel
is an indicator of to what extent this embodies what is often referred
to as a ``purpose'', though I don't believe in a life purpose. It is,
really, something that is enjoyed, competitively advantageous, and
fiscally valuable. In trying to narrow this down some, I do believe I
want to do some variety of online business. I think I need to be
studying some minor app development perhaps, I want to be able to deploy
some simplistic programs that could make money. Perhaps also doing
courses on what I learn.

To conclude here, I do need to find a purpose or pursuit but it seems,
at present, I don't have enough information. The incubator idea seems
appealing to me, but I can't just hoard resources waiting for the good
investment to come. This won't be something that can save me from the
enticements of poisonous pleasure. I then need to find a pursuit that
still allows me to incubate in the extent that it is general enough to
encompass what I anticipate will be my purpose, but specific enough so
that I make real progress and build upon something, so that I'm not
swept away by too long a term.

\bigskip
\bigskip
August 1st, 2019

10:41 pm

I just got back from Evyatars bbq. I left this event with a sour feeling
in my stomach. My subconscious, I think, was communicating something is
wrong. What I felt was that I wasn't connecting, perhaps at all, with
Evyatar or Segev or anyone there, really. I felt very alone. With people
who don't value me. That same loneliness and despair I felt as a sperg,
as someone with no skills and no love. I don't quite know if it was a
problem with them or a problem with me. With whom do I confide, I
suppose, is the real question. My emotions now are so raw, I'm feeling
nearly overwhelmed in what? Shame? I don't know. Again, I feel that
yearning for the love of a woman, not necessarily because I so desire a
woman, but because I know it means acceptance. Being all alone, I'm
maybe yearning for a place in society, and this is, to some extent, what
a woman provides. You become a team.

\qquad Need I simply become content with myself alone? But what use is
you if no one else likes you? I feel like an isolated caricature,
forever to act a role in submission to others. Perhaps I wasn't being
``real'' at this event, and perhaps I need to be what I want to be, who
I want to be, even when nothing comes to mind of what I should be. All
this talk of a purpose and it's seeming I forgot mine already. I think
what was maybe happening was I was too caught up in the routine. Basing
my actions of purpose on faith of a general principle of sorts. That
sort of, ``talk to people, be social, interact, bla bla bla''. The why
behind why I chose this habitual principle to begin with has been lost,
and with it the nuanced focus has gone off track. I've stopped taking
shit, it's true, and this is a good thing. But possibly I've also
discovered therein from people's reactions that I am not inherently so
valuable, and thus I have no real partners in life.

\qquad Well, of course people won't value you when you aren't bringing
value but going haphazardly through conversational routine aimlessly. I
am feeling now a certain anxiety. I have no friends in whom I can truly
and completely confide, and I therefore have no mode of expression and
acceptance of who I am. I cannot, however, rely on others for my
innermost dependencies. The only person wholly interested in you is you,
and it is then with myself that I must confide, and God.

\qquad If all these people were to go away, to disappear. If I was face
to face with oblivion and God, with no one but myself and He, even then
I must be content. For is this not the base, the foundation upon which
my everything relies? And thus again we are taken to the need for
purpose. A life condition whose retroactive fulfillment is my condition
for happiness, that I recognize as my primary, with others in
interactions being secondary to that. In the absence of a God I would
select this as ``What do I want?'', but in His presence I acknowledge
this as 100\% overlap of both what I want and what He wants. But how
should I judge his desires for me, in determining what I desire for
myself? I need to provide value, in career, for one. Not just something
as a subjective value to others, but a value that I recognize as I guess
legitimate. I'm met again by that feeling I felt starting the 2d game
engine project, that I'm worthless. Embarking on a goal will, perhaps,
give me worth. Solving difficult problems, ones truly difficult not just
nominal and useless goals. We're not going to find this goal concretely,
not yet anyway. But we do need to recognize that it is this goal towards
which we must strive and nothing else, even if we can't articulate that
goal quite yet. To that end no one else matters. Again, confronting that
I am alone in my pursuit, as is everyone in theirs. To the extent these
individual goals overlap, perhaps, we interact, but to seek this
fulfillment in others is to repel them, they having no interest in our
goal and knowing we are on the wrong path in pursuing them with this. As
far as habitual convention is concerned in the avoidance of conflict we
interact in disagreement with this truth, but emotionally and
subconsciously this is felt.

\qquad The conclusion this exploration is heading towards I think is
this, that there is some purpose for which I must live and be
unashamedly self-occupied in completing. Towards this aim I must strive
with everything in my power. I must put all else under this goal,
whether they people, pleasure, or anything. Especially relevant in light
of tonight's experience is subjugating people to this end, and
communicating on your terms. The proper path being circular in this
sense, leading to success in all other avenues, your interactions with
people will become better. Acknowledging the true nature of a good
relationship, utilizing each other for mutual benefit of our individual
goals, or meanings, will make people attracted to you, for your meaning
will then overlap with theirs. When you pursue your meaning in these
people, however, the lack of overlap is blatant, and your value to them
is no more.

\qquad Again, we arrive at the need of something concrete, for though it
is good to recognize a purpose to which we ignore all else insofar as it
doesn't contribute to this purpose, we must have some basic criteria
with which to practice this behavior. Well, and perhaps this is a
workaround but perhaps it is legitimate none the less, what if our
purpose is \emph{to find a purpose}. To that end we might explore
things, work hard in things that seemingly do provide us value, at least
in monetary gain and, therefore, means of a purpose's pursuit, as well
as things that are of general benefit, such as looking good, having sex
and a viable romantic life, and learning Hebrew, a means to study
Judaism which will certainly be a vital tool towards that purpose's end.

Some things to keep in mind of a purpose might then be this:

~~~~• To make money, that I have means necessary to pursue this purpose
I must demand of myself. -- and further to invest in a great money
making asset, my mind, through ``academic'' pursuits of computer
science.

~~~~• To be healthy that I have the physical capacity to pursue this
purpose.

~~~~• To learn Hebrew that I can consume content that will help me to
find this purpose.

A key here is that I must demand of myself the pursuit of this purpose,
and further that I must demand I subjugate others in and to this
pursuit. A request of something that would derail me, of something that
does not at all contribute. No. I must reject it, I will clench my
chest, ground myself in my core, and prepare for all necessary conflict
that may come as a result of rejecting this off-setting force. I am
going to pursue this purpose. That is what is going to happen, if you
choose to strike do your damn worst I will obliterate you or die trying.
I will pursue my purpose with absolute optimal effort, no matter what
you do.

\qquad And it is thus we pursue that purpose in now going to sleep,
pleased with the wise conclusions God has granted me. Whereas my intense
emotion was first of anxiety, it is now of love for God. I wish to grant
Him the highest praise. I am sick with love for God and I am happy.
Thank you.

\bigskip
\bigskip
August 4th, 2019

12:46 am

I just got back from chilling with Matt and his employee Joe. Though I
tried to implement some aspects of ``don't talk to people'', I still
explained a lot, talking about cold approach and women. What I've
discovered? Don't talk to these people unless they specifically ask you
to. And even then, only talk to them inasmuch as they request you to do
so. You're time and insights and conversation are worth a hell of a lot
more than something to just give away without a request even. Any aims
or goals you might have, to expand a cold approach club, to build
valuable relationships and friendships, to have someone with whom to
discuss your cold approach stuff, none of it is worth the strain and
humiliation we incur when we overspeak and beg people to listen to our
conversation. No more, I'm making a pathetic fool of myself. If someone
wants something from me, they'll have to come get it. They'll have to
add to my life. There is no reason I should prostrate myself to others.
Let them contribute to me equally or more than I contribute to them,
because yea, I'm fucking worth it.

Practical steps to take, have in mind always when talking to someone,
``what are you offering me in this conversation?'' ``Are you worth my
time?'' ``Do I see something in you and are you contributing to me
enough that I should risk my interests in imparting to you what wisdom I
may have?'' ``what have you said about yourself, that I should reveal
something about myself?''

Always err on the side of silence and maintain that they must earn your
endearment, must earn your speech, that they must earn your wisdom and
ideas.

Further, I will add, this is a very important and necessary step in
developing into an alpha who is desired, which is necessary for making
people feel good and being gregarious as you like to. Attention is only
valuable when it is not free. It must be earned. When an alpha speaks,
people listen, because he makes himself and his words valuable. We've
for a long time now, felt subconsciously that we are fucking up when we
speak too much, when we give our words away without value. We ignore the
voice and give in to your emotions, which want to talk. We need to
listen to this voice. It is wisdom.

\bigskip
\bigskip
August 11th, 2019

12:54 pm

Again, I'm dealing with a form of nihilism. I am sort of lost in my
mission again, especially in the specifics of what to do as a personal
project or free time. I have found, however, that I should definitely
pursue standup. I've also found though that at least lately my social
skills have been way off in that I'm talking too much as we observed
before. I'm not teaching philosophy though, this time I've just been
entertaining. It really all aligns. We've been ``shit on'' for so long
that we can no longer afford to be talking more than the other person.
See if they want to talk to you about things. If they don't, they aren't
worth your time. We learn from others when they speak, not when we do.
It is an over-defense, but a necessary one until we can be adequately
fortified.

Back to the issue of our nihilism, we will remind ourselves we're
pursuing a sort of wisdom, to perceive truly, and that it is the pursuit
and progress toward this goal that brings us the absence of much
suffering that we may find a contentment, along with the fulfillment of
these needs in themselves. Further, that mastering the physical aspects
of life, addressing the needs common and essential to all men is the
first step in achieving any sort of prophecy. These needs being our
health/diet/exercise, our work capability, and our social success with
both men and women. One sure aspect of our short term plan is keeping
our diet and exercise program. Another is keeping the mind clear that it
may think adequately and, very importantly, pursue the creative ideas
and products which provide for us career potential or personal
enrichment.

To that end, we need to once again cut out entertainment feeds. In
short, we can't be happy when consuming them because we will always
suffer when our mental acuity is weakened as a result, and when we are
so fatigued that all progress toward anything enriching or career
providing comes to a screeching, ugly halt. Even if we need suffer bored
the whole day only to do a small amount of work, we can go to the next
day knowing we made some progress and not feeling a need to upheave our
program of stagnation.

As far as interpersonal relationships go, we must continue to cold
approach and standup, that sort of thing, but also be strict when
interacting with others, especially men. Strict perhaps isn't the best
term, but cognizant of the reality of the dynamic. There's zero reason
we need to take shit. A lot of people like us, a lot of people value us,
like a lot. If people don't demonstrate an interest in talking to you,
don't demonstrate an interest in talking to them.

Practically speaking, what we'll do today then is perhaps meander and
relax still, maybe cook something, but work towards a project. Also
clean the room. Further investigate coding, that sort of thing. Do
errands, to do list stuff.

To conclude the motivation bits.

Why we shouldn't consume the entertainment feeds:

We can't be happy when consuming them because we will always suffer when
our mental acuity is weakened as a result, and when we are so fatigued
that all progress toward anything enriching or career providing comes to
a screeching, ugly halt. Even if we need suffer bored the whole day only
to do a small amount of work, we can go to the next day knowing we made
some progress and not feeling a need to upheave our program of
stagnation.

Why we should stick to our diet/exercise program:

Mastering the needs of our life is a necessary prerequisite to prophecy,
and we must then feel healthy and look good so we might attract women
and better address that need.

\bigskip
\bigskip
August 15th, 2019

10:20pm

On Tuesday night we had a bad relapse, but were able to save ourselves.
Going from such a low, we've gotten a haircut today and with that new
image has been allowed a new attitude. Cold approach went exceedingly
well, and I am far more content with my appearance matching who I want
to be. I especially wanted to document how we observed the a'beed
approach, very masculine and demanding, and incorporated that into our
own approach. When the girl is far away, don't walk towards her but say
``come here'', even insist on it and they come. Very much frame control.

I also want to address our work situation. There's no more point in
trying to hide or feel bad about our lack of progress. Be honest about
it and ready for conflict. I'm not taking any shit, I'm not apologizing.
If they fire me so fucking well be it, I don't care. Do some work when
your there, try and do what you can. That's all. Bring the c book for
when you want to die. That's all we can do

\bigskip
\bigskip
August 23rd, 2019

11:03am

Last night we wrote a damage report and had essentially a relapse,
eating protein bars and that sort of thing. Today we vowed no social
media and I definitely feel much more relaxed. Fuck all of that, create
content by writing. Make guides of whatever.

\bigskip
\bigskip
October 11th, 2019

9:01am

I opted to write this in the journal because I don't want that same
frame of damage report, I need to settle my thoughts freely. Since I've
been sick, really, things have been shit. I've been gaining fat, I
haven't been able to work out, the only saving grace has been the frat.
Except, they don't even fucking like me. To my pledge brothers I'm a
clown. To the brothers I'm fucking weird. I don't give a shit anymore.
And no, I shouldn't have in the back of my head ``oh, now I won't give a
shit and then they'll like me''. No, fuck that. Do not stay where you
aren't welcome, ever, ever, ever. It's not fucking worth it. We are
feeling again first hand that shit, bottom of your gut, feeling of
prostration and it's not worth it. Either the people in the frat like
me, or they fucking don't and they can fuck right off and I get back to
the individuals who do like me.

\qquad In truth this past week and a half since I've been back has
culminated into an inevitable and perhaps rightful depression. I haven't
done anything worth anything, I don't have many real friends at this
time, and my prospects with women are certainly in the toilet. I think
this calls for a monk mode. Social attendance and focus will be
relegated to what is necessary for the frat, nothing more. The focus
becomes inward, on myself. I need to get my shit in order, do things I
want to do, further my own career, my own prospects, my own peace of
mind and contentment.

\qquad Naturally, this involves lifting. All this repressed frustration
need be expressed. Further, I need to be improving my physique again. It
very frankly pissed me off to be fat right now. I'm wasting my shit away
at this frat while my body literally deteriorates. No, that is not the
mission. We don't sacrifice the fucking mission. At the end of the day,
it is all you have. I don't have friends of the fraternity, I don't have
women, I don't have nothing except God. And the mission is the pursuit
of him to some extent. It is what I want to do with my life to feel
content. You only have your own decisions, and deciding to do something
that matters is the only thing that matters, fuck everyone and anyone
else.

\qquad My cravings for candy and crap are also an enemy. An enemy to my
happiness, an enemy to the prospect of an end of suffering. Not worth
it. As much as we'd love to starve and say fuck you to it all, however,
we need to eat. Stick to a system. Yogurt with Ezekiel, you're hate of
it will maybe even let us express this darkness in your heart. Darkness
as a loss of faith near totally in others and the systems they provide.
Regardless, a system must be made. A designed default of the food I eat
and that's it. Something doable and providing proper nutrition.

\qquad Further if there is any happiness or even peace in my current
moderately depressive state it is in the clarity with which I now see my
life. What the priorities are, what must be done, and what must be
avoided. It is known to us that the various entertainment feeds will
steal from us this clarity. They will cloud our thoughts and judgements
that we don't see what is directly before us, that we waste away in a
good little blind box, blind to the life that is being destroyed by our
misbehavior. Imagery of a drunken man regressing to a baby comes to
mind. Totally oblivious and very clearly malcontent, but he just doesn't
know. He cannot see what is the truth before him. I must keep this lens
clear, no matter what. I very desperately don't want to fall to the same
patterns of last year, of mediocrity and suffering. I want to be buff
and looking excellent, but further I want to have much success in my
career, in programming. I want to make money and eventually study torah.
All of those things are material gain and are ultimately meaningless.
The clarity with which we perhaps now see things, that is all that
matters. So long as we maintain this clarity we might live out our days
observing.

\bigskip
\bigskip
October 23rd, 2019

9:52 pm

Today I did indulge in some crap, some youtube or twitter or reddit, but
stuck well to my diet and gym program. I didn't have balls to approach
most girls, but I was close. I contacted some girls on my phone and got
not real responses -- they aren't so interested. Today, I didn't feel
loved but I also feel more in touch with my emotions. I feel there's a
path forward. Unhappiness paired with content and tranquility is truly
not a bad program.

\bigskip
\bigskip
November 4th, 2019

2:10 pm

I'm eager to study philosophy again, that life philosophy which I
consider and explore by necessity. It aligns my mind.

\bigskip
\bigskip
November 5th, 2019

12:28 am

Looking back on my past journals I see how far away contentment truly
is. Even when disciplined, I'll still be unhappy. Even in the greatest
successes, I reckon I'll still be unhappy. I perhaps should give up on
happiness, perhaps even on contentment too. All the things I'm doing,
I'm doing to pursue happiness or contentment, but perhaps I should
accept everlasting discontent and cry out to God for salvation through
good action.

\bigskip
\bigskip
November 6th, 2019

12:39 pm

Journal check in. That same fatigue has overwhelmed me. My physical
faculties perhaps need work, or perhaps my mind needs to adjust to the
fact that this isn't a time for rest. Losing weight is always a rather
lethargic thing. It's ok if we don't do much this semester.

\bigskip
\bigskip
November 7th, 2019

11:17 am

Journal Check in. Woke up earlier today which is good. Still tired,
still not wanting to do work. Still have that inclination towards crap.
Haven't touched Zarathustra because reading seems so unbearably boring
before actually doing it. That's because I'm thinking about it
beforehand, I shouldn't think about things before I do them, I should
just do them. Your powers of predicting experience are weak and
inaccurate -- yet how much we use them for making decisions.

\bigskip
\bigskip
November 8th, 2019

12:27 pm

Journal Check in. Today was a slow start in getting up. It has been
troubling me that I acted like a child last night at the meeting. I
don't want to be a child. I want to be someone who has respect and
doesn't need to act like a clown to garner other's attention. Fuck that,
I must become content alone once again. Go into all of it as if you're
not going to interact with anyone at all. I need a break for a week. If
they come to you and control the conversation as if to tell me
something, fine. Otherwise, my lips are bloody sealed.

\bigskip
\bigskip
November 9th, 2019

7:50 pm

Post Shabbat journal check in. I succumbed to simple pleasures again
today and binged on food to the extent allowed by my diet. I very
seriously considered fapping and felt that same emptiness of addiction.
It didn't feel like there was any way to go on without them, no droll to
occupy my mind. At the same time, it definitely made me compulsive
again, something I'll have to struggle to switch back. Relying on people
is no good either because you'll inevitably interact in a beta way,
giving more mental grief than it's worth. Next shabbat lets try making
up some task to do to keep busy.

\bigskip
\bigskip
November 10th, 2019

11:33 am

Journal Check in. I woke up sick today with a slightly sore throat. I
won't be going to the gym, but I need to make sure I don't succumb to
all the bullshit again. It's better to get sicker physically than
mentally. Every time I'm sick all my programs go down the tubes and I
don't even get that much better.

\bigskip
\bigskip
December 8th, 2019

10:20 am

The day after Christmas party. It's interesting how things have come
full circle. How one persistent wrong thing in one domain ultimately
manifests itself in another, as if a symptom of a sick organism. Perhaps
my subconscious, desiring the explication of the problem, forced through
my actions a problem to occur. I believe I got drunk out of an addiction
to pleasure, but maybe it was, too, a subconscious motive to bring to
the forefront the cloaked elephant in the room. I am pathetic to my frat
brothers, I don't respect myself and they then don't respect me. I'm
always weary of the social disparity, of the ``what if they don't like
me'' possibility. The solution, as we know, is to escalate as much as
you want -- and perhaps your want should be finite -- until they stop
you, then take two steps back. With Rosa and Jaime and Sammy in the
summer we did this in a platonic relationship scale by holding radio
silence. The relationship was destroyed and built from the ground up on
a new frame. I definitely need to do this with my frat brothers.
Absolute radio silence. Not a fucking word. Attend chapter, initiate
zero contact. It's better for all sides, as we know, but it's ok if it
is done and expressed with anger or resentment for now.

I also want to mention, I was nearly begging for a reaction to my shit,
I was begging for someone to blow up at me because it communicates love
and caring. No one blew up because, to that extent, no one cares. This
isn't a fault, there aren't sides in that lack of caring. It is simply
self-interested individuals being self-interested, just as I too am
self-interested. Rejection is not an affront but a natural result of
differing incentives and social market values.

Alongside that radio silence, we also really need to work on
productivity and getting shit done. How are we to be competent
productive members of society, or even just financially secure, in our
current lazy state? This isn't some natural disposition, this is
developed and learned behavior. We should design something to mimic a
work environment. Arrive at library by 9 am, take a lunch hour at 11:30,
then return to work until 4, then exercise. That's 6 hours, very easy.
The days should fly by and my productivity should increase, and slowly I
should return to a solid state of mind and hopefully a solid state of
life. Today we should focus on ensuring we have enough work, including
getting everything we need to get work done.

11:48 am

Considering all these events for the past however many hours, I'm
starting to feel paralyzed again. That I may get me-too'd, I may get
kicked out of the frat. The scene on the roof where I took out my dick
and she wasn't about it is what scares me. At the end of the day, I must
face the possibility that my college career is over, that I'm kicked out
of the frat, that my parents are severely disappointed with me, possibly
even jail time, etc. etc. If that possibility is to happen, there is
nothing I can do. It is already done. Whatever life I have is the
perfection of existence as given to you by God and your past self.

\qquad If your life was to end now, if you were to lose everything and
had to sit in a jail cell for the next however many years, you do your
best and that's it. Don't be daunted by the necessity of living through
a life of shit. If our soul truly lives on in a manner not dissimilar to
how it exists here, it's all going to be the same in the end anyway,
same as now that is. All of this thinking and worry and bla bla bla,
it's all in human conception and abstraction anyway. Can't we just
ignore all that and focus on the present? Is that feasible?

\bigskip
\bigskip
December 10th, 2019

12:37 pm

I tried to address my productivity, but perhaps the first problem I
should address is my entertainment feed addictions. I can feel them
fogging my mind and weakening my body, always tired without the ``fix''.
So we cut off the dopamine and embrace discomfort. Not just from
internet use but from everything.

9:58pm

Now I'm sick, and I was drawn towards watching movies, relaxing in bed,
and eating garbage. Just because we're sick doesn't mean we sacrifice
the mission. Unless there is legitimate reason to, continue not to
consume garbage, continue to eat right, continue to do work when you
can. Perhaps don't work out, but otherwise stick to the plan.

\bigskip
\bigskip
December 23rd, 2019

8:47 pm

I will briefly address our mind has been lost entirely to immediate
gratification and comfort. Our thought is mostly occluded. I don't know
or perceive or realize as much as I can. Any greatness is no longer
desired for or really fathomed. In any event, I know that I do desire
that greatness and freedom, and I especially don't want to end up like
my father -- stuck and bitter and seemingly helpless. No way in dick do
I want to believe my financial capability limits me. And so, in these
few precious moments we have left, I would very much like to make
something of myself. Seemingly a newfound emotional yearning toward that
making of myself is rising, which is nice, but we know too well it will
soon flee. When I'm left desiring to the point of physical discomfort,
assorted immediate gratification, when I'm starving or nauseous or tired
-- how will I behave in a way to make something of myself. The metric I
think is very easily productivity, so how do I stay productive? Even if
I made money with Judah, it's not really something that would make me
happy or proud or accomplished -- that's really just shooting arrows
into the ocean until one hits a damn fish. No, I should produce and
live, be en route to accomplishment and actualizing into an actual
someone. Manifesting all my pent up individuality. It's not a matter of
lacking individuality, it's simply putting the damn paint on the canvas.
Bloody enough, just do something.

\qquad That expression said, without too much emotion which is perhaps
good news for it's consistency, what is a practical plan of action. I
know things should be considered in terms of positive and not negative
benefit, but we should be off reddit and youtube and Minecraft and that
sort of thing firstly. Secondly, we need to exercise, of bloody course
we need to exercise -- the best time to do it being when exceedingly
tired as a pick me up. Thirdly, in order to facilitate that physical
exertion the diet, of course, has to be right. No bullshit. Fourth, we
need to get shit done. Responsibilities, tasks, whatever they may be --
just push through fatigue. We've been fatigued our whole life, why?
Because we succumb to it in the first place. Tell fatigue and physical
limits to go fuck themselves and perhaps they will. I know for a fact we
will never be as productive as we ought to be if we don't address this
problem of chronic fatigue. It's not in diet, it's not in some physical
attribute -- it is all about the mental decision to move forward or lie
down.

\qquad So, in conclusion

~~~~1- No entertainment feeds/ video games

~~~~2- Work out

~~~~3- Eat right

~~~~4- Battle fatigue with action.

~~~~5- Also, don't be a bitch. Don't interact with sisters or Sammy for
a long time. Notice how hard it is -- that means you really shouldn't do
it that you'll experience change.

Lets apply these new practical things right now, not in morning
bullshit. It works at any time of day. Lots of things need doing, and we
shouldn't rest until a time. Midnight is good. So now go home, shit,
shower, and start organizing your room and belongings. Then, decide a
book and start reading. Then comparch. Then bloody sleep. Break.

\bigskip
\bigskip
January 1st, 2020

1:24 am

This is after the new years party.

Over the past week I've seen some success productively. I'm not entirely
addicted to immediate gratification and sugar, but I haven't been
perfect. I've watched a lot of tv, I've eaten crackers, chips, that sort
of thing for a while, and I've been ODing on cream and barista drinks.
I've grown fat, I've grown boring, I've grown unattractive, and I still
feel its sting after the sudden adjustment of my surroundings to what
has become of my inner reality. In fairness, that sounds like a load of
essentialist whoreshit, but I'm too tired to care to analyze it so
deeply. All I know is I need to get skinny, I need to continue to be
productive, and I need to read. I need to build myself up and perhaps
after that address social things. Really, I'm in dire need of a monk
mode. The specifics of how I will address these three goals, fitness
(lose weight), productivity (coding), and reading/abstaining from
entertainment feeds, these specifics I'll leave out of the journal. One
thing for certain is I need to exercise and wake up at a consistent
time. 5:30 or earlier is ideal for this now. I need to get on a schedule
outside of people.

\bigskip
\bigskip
January 8th, 2020

9:02 pm

Have just gotten back from the gym.

Things have been going very well and, to an extent, very not so well. It
is the not so well that has prompted me to write this journal. I say
prompted but it is more nagged. I've felt it for most of the past week.
Although we've been, compared to recent times, exceedingly productive
and well on a diet/gym plan, there have been some problems. Of course, I
refer to the more red pill social problems. The goochie goo shit with
Sammy, for instance. Our prostration to our family, having resurfaced.
Our moderate inability to socialize, especially emphasized by the new
years party. Most of that remains. I also refer to some issues still
with my productivity, after I had the hot chocolate esque drink I became
very hyper and incapable of work. I've been still watching tv most
nights after I've done some work in the day and am too tired to do much
else. I also haven't been reading as much as I should, and have perhaps
been too much on reddit.

\qquad As far as concerned with comparch study and things like that,
keep progressing. Next project will be perhaps standup or competitive
coding. Also, be strict with vim. Disable mouse=a in our vimrc, get
github going, and set up vim on the pc.

\qquad With diet and exercise, keep going. We will yet have a body in
which we can place confidence. Keep things strict, however. 2 drinks a
day, period. One cappuccino and one tea latte, finish. Also, investigate
possible ways to incorporate more protein into the diet.

\qquad With reading, we need to do more, and it can't just be when we're
about to go to bed and are too tired to read well, or the content of the
book wakes us up and we don't fall asleep for a while. Tomorrow, after
we've woken up and showered and would normally browse reddit, lets drive
to the park or somewhere and read there. That period when everyone's
still sleeping so I can't use my facilities to work.

\qquad With people, be cognizant of over investing. Whether it's the
recursion inclination or habit or whatever it is, don't over invest.
This is no longer driven by an angered resentment or frustration. It's
from the fact that I know it is best for me, and I also am growing
increasingly apathetic towards my siblings. What do they do for me that
I couldn't live without? Because I know I can't live well without
respect, so unless in my subordination and prostration I receive in
return something more valuable than that, the answer is to demand
respect at the short term, or even long term, loss of the relationship.

\qquad And with that we can close the journal. No intense emotions, no
deep pensive thought and analysis of ``what the fuck is going on''. It's
rather peaceful, almost boring. It's through the repetition of this
vanilla boredom, however, that we may culminate in peaceful, powerful
brilliance.

\qquad Closing out, there is actually another thought I want to express.
The idea of we are ok, flawed as we are, is sinking in again, and I'm
espousing the reality of what and who I am. When trying to sever
relationships with Sammy and others, he will near violently pester me
with further interaction. We can expect this violent pestering to
continue as we now increase our efforts and attempt to demand respect
with dedication. We must hold frame. What is this frame. ``I'm ok as I
am, what you say or think is silly, funny, with no impact on practical
reality. I am what I am, whether that is Billy Beta or worthless slob or
what have you.

After reading some of my past journals:

In some of my most emotional and intense moments, I come back always to
the fact that the ultimate pursuit must be wisdom, knowledge,
understanding. It is to observe with security and peace, that is all. To
understand we must act. To see we must experience. Ah, I'm feeling a
slight confusion come on. Perhaps this idea is too complex or deep to
address just yet. Just keep in mind our prior conclusions, our practical
steps to take towards a good life, prioritizing the lack of prostration.

\qquad It's just been revealed to me slightly in how we might execute
that defense against prostration, it's simply in the definition of what
is demanding respect and what isn't. Lead. Operate on your terms
exclusively. Before I was thinking in responses only. ``oh no, what will
he do next'', but that is the wrong thinking. I should be thinking
``what will I do, what will I allow and disallow. How will I steer and
captain the interaction effectively?''. Greet people, say hello, then
dismiss them and move on. Simply. Don't wait for them. The Sages
describe a man who greets others before they him. It's not out of
politeness, it is to govern the interaction, to conquer it and operate
it on one's terms. One who has the courage and desire to take the wheel
often will do good for both parties, and thus this conquest of the good
king is encouraged to all. I would be more than happy to submit to a
competent frame if one such existed, but alas it is, almost by design,
rare. And even then, I would need to be my own person. Even in
consideration, it doesn't make sense in my head as a frame perfectly
aligning to my own is near impossible. If not simply for momentary
circumstantial differences in emotional balances. Every man is meant to
captain a ship for himself.

\bigskip
\bigskip
January 9th, 2020

9:14 pm

Today started out ok, not great. I woke up far too late, then got to
work but only on navigating windows vim and windows context menus. I
still haven't even gotten windows vim to work properly, only gvim.

I was very very close to fapping. I watched youtube and crap again. This
is not how we want to exist. Don't take for granted experience of life
and progress we've had recently. Don't take for granted how quickly and
peacefully the days have gone by, where before each day was agony. Day
after day of headache, stagnation, decay. Rejection from women.
Prostration to men. The deepest and most profound emotions I've ever
felt, only being the direct result of my own shit status, of my own
absolute and petty mediocrity. I can't let this continue.

As much as I now want to go to sleep, I know I need prove myself. Going
to the gym right now is truly the last thing I want to do. Perhaps it's
physically even suboptimal. But, change in action never comes without
change in mind. Going to the gym right now, slow burn or normal, however
I do it, it's a big fat fuck you to the mediocrity. It's a big fat fuck
you to descending into the warm cozy life I would so normally just
descend back into as I go to school, then face the horrors and anxieties
of stagnation and lack of ability. FUCK THAT. Fuck it. I've lived
virtually my whole fucking life this way and we know how shit it is. How
can we not?

What are the practical steps then? First, see if we can get command line
vim working so we don't have to deal with that crap in the morning. Then
Gym, then sleep. 4:30 tomorrow we're going for a run dick face.

\bigskip
\bigskip
January 11th, 2020

8:56 pm

After shabbat.

Shabbat was not spent great, not horrible though. I watched a lot of
youtube and crap, wasn't super productive coding wise. Also failed in
repeatedly acting childish and prostrating myself to family (Ma). I
stuck to nofap ok enough.

What's slightly bothering me is my interview with AT\&T. This will need
to be addressed better tomorrow. But, in truth, there is nothing to
worry about. I need to be upfront about everything, no lies, I took the
semester off this past semester because of double pneumonia -- out of
commission for 3 weeks. If you're honest about it and present it right
there should be no problem. That is who you are after all, if they can't
take that well tough shit I can't lie. Further, if all things considered
they don't want me I won't have them. I'll enforce the frame that I'm
excellent for them, and I'm extremely excited to start working -- which
I am. If they reject that frame so be it.

Logistically we'll have to make sure our wardrobe is ready, and also
study our resume. Bring the 2d game ready on your laptop.

I think we'll be ready. Envisioning the conversations now, I'm having a
good time. Feeling the energy in my heart.

\bigskip
\bigskip
January 16th, 2020

9:04 pm

Last journal, when considering the interview, we said we felt the energy
in our heart, and so did Hansika, our interviewer, and others at AT\&T.
We have the job.

This is good, but in light of that high, however, we've fell into shit.
Yesterday and today were pretty much exclusively unproductive days, and
now school is coming up where we'll just be busy all the time.
Competitive coding is a great pursuit if we can study it in a meaningful
way.

The mantra is to keep doing. The less we do the more we crumble. The
quality of what we do is almost negligible, so long as we seek to first
do and then improve what we do. There is also, conversely, what we don't
do. For entertainment feed garbage is positively doing nothing, actively
not doing.

\bigskip
\bigskip
January 31st, 2020

12:31 pm

Experiences of the past few days have been too disparate to organize
well under a few abstractions so I won't attempt here to summarize them,
as I shouldn't. What's prompting me now to write this is an anger and
strong emotion. Last night, and I suppose many previous nights too, I've
been just taking too much shit. At points I'll feel independent, like I
don't give a damn. At other times I'll fall into habit of perhaps over
investing, of perhaps caring and subordinate myself. Or maybe what's
bothering me is a general malaise of everything. My emotions at present
are simply I don't really give a shit. I'm underscored by anger. Then,
of course, I'm only able to stop giving a shit because of shits given in
the past, and the moment my DGAF attitude anticipates a conflict with
the cozy system that's been setup for me I immediately back it down and
play the character until I feel it safe again to not give a fuck. That
behavior is being a pussy. And, of course, now considering this mindset,
when some ideal philosophies and mindsets become too complex to hold in
our head, we turn to self-interest. And then we think ``what is in our
interests'', then we lose touch with the socializing habits of normalcy,
start being autistic, get scared, and revert back to the essential we
know, which is inevitably overinvestment.

We can't have this malaise attitude; it gets us nowhere but the above
bullshit loop. Take control of the moment, direct that anger into a lack
of mercy or consideration for the person from whom you are conquering
the moment that it is most pleasing to you. Instead of taking some moral
high ground for an external observer, really being yourself or God, to
give you bonus points, actually manifest the lack of caring by placing
your bet on something. There are no points given for potential. Don't
think ``I'll do what my emotions want in this moment and if you don't
like it fuck you''. That is a rather bluepill idea of self-interest. We
understand to a significantly practical extent how people behave. Use
that knowledge combined with a consciously identified self interest. We
need be more than just self-interested, we need to be interested in the
right self.

And then, of course, we shouldn't get too lost in the Machiavellian
aspect of things, because true self interest as far as others are
concerned is ideally a mutual benefit. So a lack of consideration or
mercy must be granted for the few times we're screwing someone over, but
most of the time it should be compassion towards firstly yourself and
secondly others, that both parties' benefit.

Now, as far as girls are concerned, for example that one girl Anushka, I
don't believe the sort of radio silence pouty beta thing is quite right,
but it's certainly better than overinvesting. Regarding that, I so hate
taking it up the ass. No more. I want to hold in all my interaction that
females are worth jack dick squiddly shit. Hold standards for if they
earn the right to waste your time fucking. It's a large investment
setting up logistics for a girl. Let the girl invest in you and earn her
fucking keep if you're to take charge, take her needy ass aboard your
ship, and captain it now with her needs in mind. Not every girl is worth
it, and the more they make it easy for you to captain the ship, the
easier can be the decision to bring them aboard. If they cause problems,
fuck em. Don't matter if they're a 2 or a 10, they all pale in
comparison to the glory of God at the end of the day. They're not jack
diddly dick to the true pleasures of using the muscle of the mind and
finding love for God.

Delete the numbers, damn that feels good. We're hitting the right notes
with that fuck. Perhaps even better than sex, no almost certainly
better. I feel alive. Fuck that bitch.

\bigskip
\bigskip
February 3rd, 2020

7:58 am

The current status is, yesterday I was mostly unproductive though I went
to the gym. I got tired after a bit and tried to sleep around 6pm. I
couldn't sleep and fapped, then fapped 3 more times ultimately to porn.

I think that failure, as failure usually is, was an inevitable surfacing
of a deeper issue, though how much deeper I'm not sure. I wasn't very
focused last week and certainly felt the low level lobster status I've
created for myself at the frat. That feeling of being underscored by
anger, it has always lead to trouble. To some extent I've lost touch
with some motivation I might remember having a few weeks ago. Just by
acting out the motions, however, I'm again starting to see the apparent
incentive. I'm feeling uncertain, however. My fear is that this
uncertainty will lead me to give in when things inevitably get tough, if
only for a short while.

One motivation which seemed promising is a view of the world as a blank
canvas. Every consciousness is a painter, we can put colors here or
there. You can dick around for a while, painting in circles because it's
fun, or you can put your efforts towards a deliberate art. The question
then comes, I suppose, what's the point of doing either, and we're back
in the same nihilistic loop.

After reading some of my previous journals, perhaps investigating the
motivation I had that prompted me to get my shit back together at new
years, I've become quite content with just the calm of it all. The
tranquility. Why do work, provide for yourself, keep moving forward?
Well, simply that we might enjoy the climb higher, and take security in
the fact that as long as we move forward we will be free of most worry.

Why relieve yourself of addictions and pleasures? Because they bring
worry, they threaten your tranquility. But this itself, ironically being
of tranquility, brings to me some worry that it isn't sufficient
incentive or motivation that my life won't fall apart again. Needn't
there be some positive incentive, rather than negative? Do we not need
to run towards, instead of away, from something (or at least do both)?
One thing missing from this equation, I think, is people. We've sworn
off our frat brothers as a defense and logical, automatic response to
their seeming rejection of us, but we must maintain that, perhaps within
some merely practically objective truth (to address a Buddhist
emptiness), this rejection is self caused and has potential to be
rectified. If they are not the problem, but I am, then long term I
should be able to rectify myself and refriend and reincorporate them
into my life, and most importantly any potential person of similar
value, status, and modes of interaction.

In short, we had sworn off the pursuit of high value (socially) since
those of high value rejected us. But, really, we should be pursuing high
value, even if at present we are rejected by the high value society, and
their favor is seemingly impossible to re-attain. For one, we should be
pursuing high value with others besides those that have witnessed you in
the shit. High value transcends the fraternity, it is with all people.
It's true, the fraternity is a concentration of high value people,
however there's more besides Rutgers. I've taken a position that people
in the fraternity are almost fundamentally different from those outside
it, not because of a hazing or anything like that, but because they are
social and can interact warmly, socially, and irrationally -- something
you don't see in most people. They have fun, and maintain high value.
This capacity, however, even if not expressed in most people, I must
believe is present in everyone. And, further, as a result there are high
value individuals from whom to attain and express your own value that
are worthwhile. Further, the frat will inevitably become less important
in my life after I graduate, and my own value will shine through the
circles I enter and maintain later in my career. I should then build
myself up into a valuable individual by my own standards. My physical
manifestation, itself, being the canvas. Build my mind, my mannerisms,
my body, my possessions into an art piece of a person. Design it like an
artist would his art.

\bigskip
\bigskip
February 6th, 2020

12:03 am (night of Feb 5th)

I was very close to fapping tonight. I found myself trying to remember
why I didn't and very vaguely connecting with that yearning for
something better. The intense sadness and malcontent I've felt in the
past. Has my life really that much improved from then? Sure, I've gained
some amount of productivity and career success, though not to a standard
I would really hope or enjoy enthusiastically. I've gained an amount of
social success and have slept with women finally, but I still don't have
any consistent sex and my frat brothers don't really respect me. I'm
still socially quite broken. Physically I've gotten much better, but
even when I do hit abs I don't think all that much will be different.

\qquad Perhaps we know from past that whatever you are seeking doesn't
exist. Whatever we achieve becomes the new default, and a greater
achievement is yearned for. It's true, we've been through this logic,
the journey itself must be the destination. Well fuck, that really
doesn't lead to any solution -- but there must be a solution.

\qquad Start again. I was close to fapping, and then I thought on why I
didn't in the past, and slightly reconnected with that intense emotion,
that yearning for something better, that initially prompted me to pursue
it. My life was such trash back then, and maybe to a large extent it
still is. Well, have we ever really gone all out to break out of the
shit hole? I don't think so. Maybe we've attempted it, but we didn't
really commit. Lets clarify some components of the best life we can live
right now and see where it goes.

1- Work hard, effectively, creatively, and sufficiently. Get shit done,
express yourself.

2- Make yourself sexy, fit, an attractive personage.

3- Read books, to make yourself interesting and to explore with your
mind interesting things. To interact, also, with the world.

4- Take up an art form? Some mode of self expression? What would I
feasibly take up? I think writing. We can start with short stories for
fun, see where it goes. Goal is to convey an emotion. Further on this
point, perhaps the secret to social interaction is that it, itself, is
an art form, arbitrary but still requiring the artists hand to make
beautiful.

From this ideal, what are perhaps practical steps to be taken?

Firstly, we can say we need to get all our work in order. Prepare for
software meth stuff tomorrow. Finish studying algo, really understand
it.

Second, we can say continue to gym, eat right, etc. But our diet is out
of control in regards to cough drops and gum. Cut it all out. We
shouldn't need it, if you don't have it you simply wont need it. Also,
we should be strict on our calories restriction. No need for protein
shakes during off days, I think. Barbecue sauce is also literally just
corn syrup. Out. Bread with hummus chicken is a meal. Two pieces of
bread is ok I think, otherwise we crave the carbs. Lets up the cardio,
however. When we do 2 a days we really feel proper.

Third, on reading, this has always been tough. We need to implement
strong goals here. Start with 30 minutes a day after a meal.

Fourth, writing. Come up with ideas for 20 minutes maybe. Right before a
meal. This can be put off if we really want.

\bigskip
\bigskip
February 7th, 2020

12:56 am

I wasn't going to write a journal just now. I opened this document,
closed it, and had a tab open to go to some other site, but felt a
headache come on, a fatigue. All the busyness of the virtual world, of
really most things external it seems, all seem meaningless. I'm
approaching an almost nihilistic fatigue. If we can channel this fatigue
into a disregard for all that, in truth, brings you no benefit and a
then unapologetic regard and aggressive conquest for that which does
give you benefit, that would be good. Otherwise this feeling might
manifest into a nihilism and inevitable relapse. Further, we find
ourselves bordering again on a general malaise of anger and resentment.
``This is all shit anyway, the fuck would I care about you or anyone
else? I know what I need to do to perhaps make this slightly more
bearable, I'll do that in my peace.'' But perhaps consider no one is out
to get you, we're all pursuing the same thing really. You interact with
them, and they interact with you. We are all the same variety of people,
don't think you're any special or different. That bit I think is
slightly relevant, but didn't go anywhere in the end. As far as
practical steps, etc, and maybe I'm rushing this so as to settle things
in my head and sleep peacefully, but it would be good to settle things
no? Anyway, need we not fall back on the tried and true methods of
benefitting our life? Wake up early, read, lift, cold approach, work
hard, make your days fly by. Notice the one big glaring thing in our
face, the cold approach. It's so bloody horrifying, it really always is.
Logistically, how would I go to a mall? Where would I find time?
Further, most of the girls at malls are young, perhaps too young? And
our fundraising position -- it's very easy. Do your best and if you
flop, let the fraternity handle it.

I'm too tired for now. Lets see if I'll be able to sleep yet.

\bigskip
\bigskip
February 11th, 2020

7:26 am

Over the weekend I relapsed badly, and yesterday just played games and
fapped last night. I've been good on the diet since the weekend though,
and yesterday resolved to get my shit together by means of a sleep
schedule. So I woke up at 5:30 yesterday, after going to sleep around 3
or 4, and slept well at 9pm last night, waking up today at 5:30. I'm now
resolving to get my shit together by means of this journal, and
investigating how we might now implement an optimal lifestyle, our sleep
schedule being a foundation of that now set.

Firstly, I feel much better waking up early. I feel awake and present,
and the life progress also brings me some peace. We outlined in one of
the last few journals that we want to read difficult things again.
Effectively, perhaps its equivalent to studying. How then should we
handle priorities? Maybe like gym? Assume it first being done, then work
around that? No, I think it can be read casually. Fit in somewhere 30
minutes a day. Lets try right after morning journal. It's not a late
night cram thing, that's more along the lines of school.

To address entertainment feeds, we really need to address that desire
and urge to browse whatever, the illusion of connectedness. Satiate that
desire for awareness by \emph{asking people of their experience}. Ask
them what's new, ask them if they've heard anything interesting. Let
their sphere of concern become your news source. This is how information
is supposed to spread, it creates such a wonderous society. Technology
has ruined that to an extent. So, then, when we are feeling an urge to
know something or be entertained -- ask someone about what's going on.
This doubly will improve your social skills and interactions.

That's it for today I think. I'm emotionally not so directed towards a
task anymore, maybe I'm fatigued. When emotions don't guide you, the
best thing is to just do what you know is right I suppose.

\bigskip
\bigskip
February 12th, 2020

7:27 am

Yesterday I wrote two things. One, that we should just read Horizontal
Society casually, and that's working well even though we may not absorb
every detail. And two, that we should rely on other people for
entertainment, and that worked only ok. I'm not so great at getting
information and finding things I'm interested out of people, it turns
out, so I did a bit of supplicating and seemingly interaction for the
sake of interaction. Further, sometimes I was just tired and didn't have
the energy to go extract entertainment from someone, or what they could
offer couldn't compare to the high dopamine rush of digital
entertainment, so perhaps that only means I need time to re-adjust my
dopamine. It's then very important I continue to abstain from both
technology and fapping for that dopamine readjustment purpose.

\qquad I also came to a few other conclusions, or rather re-discovered
them as they're ideas I've stumbled across before. That is, emotion is a
choice, a product of conscious outlook. If we can choose to have
positive or negative emotions, choose positive ones -- or, rather, the
optimal emotional disposition (perhaps one espousing Maimonides middle
path or something). Be, perhaps not elated, but content at all times --
and never anger unless it suits you (which, it's hard to imagine any
scenario in which it does). After looking this up, Maimonides seems to
agree anger is never useful and is, in fact, a hindrance to higher
understanding which makes perfect sense.

\qquad The other conclusion I came to, more in line with the social
manipulations I was considering and investigating in the summer, is the
value of love for people. If someone loves you, for some reason
biological or instinctual (or both), you cannot hate them. It even
becomes difficult to dislike them. Someone who loves you seems the exact
opposite of a threat, if anything you exercise at a minimum pity for
them, if not an amount of reverence for you have similar interests in
that you both like you. But, this automatic conclusion we make isn't
exactly accurate. Someone who loves you is not necessarily totally non
threatening, nor totally aligned with your interests. Someone who loves
you can be a real threat, and this is where the biological response can
be nobly exploited.

\qquad We could fake love, but why not genuinely espouse it, like the
Buddhist? By exercising love towards all people, \textbf{but not
necessarily respecting them}, everyone will be kind and warm and
amicable towards you while you are still acting within your interests.
You can stab them in the belly, a warm smile on your face and love in
your heart for their being (without attachment, of course), and unless
they consciously analyze your behavior and reframe your love in their
head as disguised contempt, they will respond as we have described, that
is, completely disregarding you as a threat to their interests.

Does this mean we should use love in some psychotic way to exploit
people, murdering with love in our hearts? Obviously no, but it does
mean we should act self interested \textbf{and} love others, especially
when \textbf{our interests don't line up, or conflict, with their
interests}. By loving them you are delighted at what they have created
for themselves, at the book of this world God has written them into. Of
course, we are still primarily concerned with our own character, but we
can be pleasantly amused, delighted, and grateful for the stimulation of
others (as a ketab) along the way amidst the plethora of interpretations
available from which to view them (mikhtab).

\qquad That's all for today I think. A good journal, I'm happy.

\bigskip
\bigskip
February 13th, 2020

9:40 am

Party last night went very well. I was a bit beta with regard to certain
pledges, and that must be addressed even if not articulated here, but
otherwise had a lot of fun. I lead the interactions with energy and had
them go as I wanted them to. It's important not to get sucked into the
pleasure, however. The most pleasurable possibility would be to remain
both disciplined and fun. To create discipline within the party life
itself, that we don't flip from disciplined state to all out
emotionality at parties. It shouldn't be something extra-curricular to
your routine, it should be incorporated.

\qquad I'm also noticing I'm not having many insights right now. My mind
is just moving, but I don't know or control exactly where. Almost like
I've been over-caffeinated. I'm now seeing how this was/is a product of
leaving the sphere of my discipline and introspection at the party.
Don't let everything go, don't become Dionysus then return to Apollo.
Integrate play and work into a single mindset. The priorities should not
change, only the specific one being addressed at a specific time.

\bigskip
\bigskip
February 14th, 2020

8:30 am

Yesterday, perhaps because I woke up late, I ended up very
undisciplined. Ended up watching youtube videos again, playing games
again, unable to do work. Without discipline we fall apart. A man cannot
participate in higher thought without discipline. In this effort we must
then be strict and sure. No dopamine things. If we're tired we can sleep
or do chores, or some menial software meth stuff. My mind is blank and
I'm tired, craving a dopamine fix. Perhaps this craving is why my mind
is blank. Let us reject it now.

\bigskip
\bigskip
February 15th, 2020

6:27 pm

Party last night was retarded. Fucked raw, never again, and fucked
Anushka. Weird. Just now with her I was a little beta again -- let us
avoid this. I'm also slipping out of my discipline. We need to be
strict, or we will fall apart. There is too much to do with school and
other things. We can't fall off track. 5:30 wakeup is a must. Apart from
that, I think not much we can do for tonight.

\bigskip
\bigskip
February 16th, 2020

1:16 pm

Couldn't wake up today at 5:30, woke up late at 9:30 and am only getting
around to journal now. Today just focus on getting software meth work
done, going to gym, keeping diet, and maybe doing some amazon returns. I
don't have any other insights left to make, really. Just tired, blank.
Need to get back into discipline.

9:31 pm

This is a sort of emergency journal entry. Things fell apart fairly bad.
I contacted rodna to fuck, jerked off, overate slightly, and watched
youtube and garbage all day. I got absolutely no work done for software
meth. All we can really do is do the software meth work and go to sleep.
Nothing else will heal us.

\bigskip
\bigskip
February 17th, 2020

8:17 am

Last night was definitely something horrendous. I suppose we shouldn't
relegate the failure or catastrophe or accident or whatever one may call
it to only last night, though. I'm hoping it's a result of some deeper
issue that perhaps we can fix, that it's not just as simple as ``I'm
tired, I don't want to work right now''. I suspect it may have something
to do with our sexual deviancy and debauchery, specifically fucking
Rodna -- that was a disgusting mistake.

\qquad In any event, my life has largely gone to shit -- especially
espoused by my recent inability to do the work I know I need to be
doing, abdicating those fundamental responsibilities to life. I'm very
tired and fatigued right now, and this frightens me that I won't have
the energy to take care of what I know I need to do, being the remainder
of my software meth project. That, being our current primary source of
stress, must be addressed with a top priority. Perhaps we'll do that now
and return to the journal once it is all done.

1:41 pm

I finished project, had some nicotine and coffee and dicked around for a
while. I feel much better though, relaxed, though likely not masculine.
Mind is still blank, but let us plan out at least a small plan of things
to do for today.

Finish comparch project, submit software meth with bobby

\bigskip
\bigskip
February 19th, 2020

8:00 am

Yesterday we scheduled a meet with Anushka, I went to her place
expecting to smash. What actually happened is I meandered for 45 minutes
while she got ready, then I drove her to her train. I made out with her
and played with her tits, but it ended up being very beta. I just kept
trying to escalate and she kept trying to shut it down. We could feel
deep in our soul that we were sacrificing our values for the temptation
of pussy. That can never happen again.

\qquad Ok, but what should we have done? Once we got to the point where
she wasn't going to fuck, what were we to do? We could have said we had
to go, and leave. No, not that we had to, that we are going to. Our
social charm is more powerful than we think. Be nice, say nice things,
exercise love and caring for the other, then \textbf{do what you want to
do anyway, act within your interests}. ``Listen, Anushka, I want you to
have a safe trip, to enjoy your time in New York. I'm gonna go, \ldots{}
Yea I'll let you finish getting ready for your trip. Bye, I'll see you
at date night''.

\qquad We can't be ashamed, or expect her to be mad at us, if all we do
is fuck. I must maintain that distance because she will undoubtedly
cheat on me if we enter a relationship. I feel as if I'm typing that
only out of principle now, and as if I really don't believe it. That I
believe she has the restraint to be loyal. But that's the issue, even if
she were loyal, that loyalty would be out of restraint -- nothing else.
It would not be out of a genuine desire for loyalty, it would not be
because I'm truly the only guy she desires. And yet, the love I would
project onto her would be grounded on myself being her only desire.
Claiming her for myself. To this false aim I would forego everything,
all of my mission. This perception of reproductive actualization would
be a false god to which I subordinate everything else. After all,
reproduction is a primary goal of a being, worthy of subordinating all
other actualizations to. Except, reproduction is off the table with this
woman. I would only be fooling myself. And, perhaps, in every sexual
encounter I'm fooling myself.

\qquad I've been fucking for pleasure or clout or a search for meaning I
suppose, but very clearly, it makes sense, sex is for reproduction.
Because of its absence in my life prior it felt like something I need to
explore, but thus explored we should treat it as a known thing. What is
the benefit of fucking? Certainly, it's superior to fapping, so we ought
to fuck instead of fap when we need to fap. But do we need to fap?
Coming from a perspective not of ``I can't have this'', but ``Do I want
this?'', I don't know if it's necessary to ejaculate every so often.

\qquad Our philosophy of fucking, and therefore all female relations,
may then be this. Find the optimal amount of sex to facilitate our
mission, and pursue women only to fulfill that quantity. But, what of
the ideas that a woman completes your animus with her anima? Is this so
essential? What even is this idea? Would it even apply to random women,
or could it only be facilitated by a single competent one whom you know
deeply and for a long time? Would I even be able to attain such a woman
at Rutgers?

\qquad After reading some pook, I do believe we've arrived at a
solution. That is, casual dating. Women, in this way, serve two
purposes. Sex, and fun dates and/or activities preceding sex. Sex is a
very important aspect of this, and if not sex at least she must blow
you. Not because we so desire to cum all the time, but as a respect. Any
woman who doesn't do this, is not worth a date.

\qquad Leaving this journal, I'm thinking if I enjoy Nirali's photos I
may take her to my datenight. I need to consider things in a perspective
excluding the possibility of who will fuck me. Idk, I'm still rather
jumbled.

\bigskip
\bigskip
February 20th, 2020

8:58 am

After consulting with Matt, my pledge brother, and also briefly Jordan,
also my PB, I arrived at an attractive analysis of the situation. That
to go with Anushka is a safe option. I'll almost certainly have sex,
I'll have a good time getting drunk with this girl, and all will be
swell. Nirali, however, is the high risk high reward option. The
interaction could go sour, it isn't guaranteed. The potential reward
though is that I fuck Nirali, a new body, and further that I can situate
a beneficial interaction with Anushka moving forward, from a frame of
respect. And so, as we know, with nothing to lose we must have
everything to gain. Fortune favors the bold and Anushka has been
anushdumped. We set sail to the Indian sea to fuck Nirali with our big
fat peepee.

\qquad I now feel happy, at peace, excited for the future to come. I
feel making that decision was significant, beginning a new mental
adjustment for the better. Standards with women have now been realized.
I actually enforced a punishment for a negative behavior. I'm showing
that I genuinely won't tolerate bad behavior, and thus demand good
behavior. No more walking on me, baby. I'm gonna give you that frame you
love, by virtue of it being all mine.

\bigskip
\bigskip
February 21st, 2020

2:27 pm

In stark contrast to some of the relaxation I felt earlier, I'm feeling
full of energy but also impulsivity. Almost like a caffeine rush, but I
only had a double shot in the morning like I always do. Perhaps this is
a result of eating at maintenance calories as I have. As far as caring
about whether it will affect the night, I think no bother and it seems I
can focus on the present fairly easily if I try. And trying I'm now
observing my stomach hurt perhaps slightly. Is there some activity we
can do to be more relaxed, more calm? I don't feel quite good in all
honesty. Alcohol should fix that when the time comes, but for now I
think drink a lot of water. Also, rest in bed a bit. Go for a walk
maybe. Clean up your shit in main area too.

\bigskip
\bigskip
February 26th, 2020

11:43 pm

So today fell to shit once again. I've found myself familiarly looking
at examples of the seemingly hyper successful, and feeling sad or
melancholy that I'll seemingly never attain that level of success. Of
course, it's been hashed before that our perceptions of their success
are meaningless and inaccurate, and also that if it's something out of
our reach it doesn't matter whatsoever. I'm finding peace again with the
stoic mind, that all we have is that which is in our control. This deep
angst, or cry for some form of salvation. I come back to it not
infrequently, an undirected love aching for direction. I'm inclined to
think my feelings this time are different and more relevant, but it's so
obviously familiar that logically I know they can't be. I feel
inadequate. Like, so what I can become a social fiend -- my attempts at
standup have been crap thus far, I can't even write a single bit. I
think for that I have to just go and do it.

12:11am

So after writing that last bit I signed up for the Rutgers standup and
saw a message from Ethan from Israel. I then saw some stuff from Bayley,
Ellie, Evie, and ultimately Lucy, who's now doing standup which is
interesting. It reminded me of those shit years, really being
representative of the majority of my shit life. That sadness and
malcontent has returned, and with it the striving for something better.
It's interesting though, because this desire for greatness wasn't
prompted for the sake of it, but because of perceiving others and
considering how they perceive me. Or, alternatively, because of how much
they've accomplished while I've pissed away. Even in the wake of my
recent progress, I still end up pissing away my life. I feel stagnant.

\qquad Perhaps there's some excitement in that malcontent because it
usually signifies a motivational boost for the better. In truth, my more
recent spurs of success and motivation were prompted by that same
feeling. Jordan Peterson and other sources of wisdom will say ``compare
yourself to who you were yesterday, not who someone else is today'' but
that sounds like bull to me. We are all people, all with seemingly
similar enough capability. If someone can do something and accomplish
something while I'm pissing away in the dust -- why shouldn't I feel
like crap. Feeling like crap is the only way I find peace. I do feel so
stagnant lately though. My physique is stagnating, my academic progress
is stagnating. Perhaps even my game is stagnating. Is my life really
underscored by stagnation? Can't we say I made progress in this field or
that? Perhaps a little bit, but then don't I get caught up in ego, in
reaping the rewards of what I sowed and, in error, close down the bloody
farm right as the yield was getting good? Lets look back at some of
those facebook things again, as this melancholy and depression is
fleeting, and I feel it is what gives me peace and strength.

\qquad In conclusion. Be sad. Sadness is a good thing. Exercise love for
others, but also for excellence. Demand it. Feel the immense suffering
and pain present in this world without demanding excellence. Let us not
forget however, that exercising certain emotions in themselves is part
of the demands of excellence. When with others we must demand of
ourselves happiness, or seriousness, or whatever the occasion calls for
that we may maximize the interaction to our benefit. Don't be sad and
mopey all the time, but in our most intimate moments, when I am faced
only with myself and God, only and always then must I be sad, must I
feel that melancholy which motivates me toward greatness, Man's defense
against existential suffering.

1:12 am

After reading more of my past journals, it seems highly likely to me
that every bout of motivation, contentment, and zealous truth we feel
and go through are all generated through that sadness or malcontent.
That striving for better, that realization of ``yes, I am a worthless
piece of fucking trash''. I'm become only more convinced that
existential sadness is the best way to live, that we may be sad without
suffering, and see in our melancholy the truer nature of our existence
and of God.

\bigskip
\bigskip
February 27th, 2020

8:59 am

The intensity of that sadness seems to have dissipated, but I'm still of
mind enough to challenge myself. That stagnation, as I've probably
already discovered in the past, is I think a product of giving into to
fear, of not pushing against resistance. Because, of course, resistance
is essential for growth. One unable to push against resistance is wholly
unable to grow. I feel an eagerness to work, but not as much for
horizontal society so maybe for the sake of that eagerness we'll forgo
it for today.

\bigskip
\bigskip
February 28th, 2020

11:17 am

I've encountered the problem again where I'm needing to love everybody
more. So we'll be trying that. Don't have much to say otherwise.

\bigskip
\bigskip
February 29th, 2020

7:48 pm

Possibly related to our breaking of nofap, we've been in a total shit
streak. Last nights party was certifiably comparable to new years.
Whatever mojo may have existed is, once again, lost. This idiocy of up
and down, alpha and beta, has to totally stop. I can't handle this shit.
The answer is very simple -- become unattached to women. It's been
staring us in the face all along, the implementation is just
understandably daunting. All of my success is based on shaky emotional
circumstance. When I feel good I act good, when I feel bad I act bad.
The only consistency in your life you can control is your career, your
mission. That must be the primary, from which secondary pleasures stem.
I'll enter a monk mode then. Won't I need human interaction though?
Sure, when we're ready for it and on a significant nofap. Commit to 2
weeks nofap/no ejaculation. We do not need sex at this time. We've had
our fun, 7 bodies is plenty.

10:02 pm

Just visiting the frat now, I notice myself making compromises. In macro
behavior, I commit to one thing, to monk mode and a degree of social
isolation. When thrust into circumstance, however, I hesitate, lingering
and wanting to interact. Whatever I commit to, I must commit to. No
social interaction apart from logistics and (arguable included in
logistics) the necessary pleasantries of interaction. I need to isolate,
I need time to find my own inner meaning and purpose separate from any
purpose or woman. I need to find a favorite way to live which is wholly
sufficient for all my needs, that I am independent and unreliant on
others (or their body parts).

\qquad Further, I'm not going to try to sleep when I clearly can't --
that's just a fucking nightmare. It seems daunting and not unbearable to
us in forethought, but lets try working, coding.

\bigskip
\bigskip
March 3rd, 2020

8:39 pm

In recent we've fallen off moreso than we have before. Not exactly as
much in behavior, but almost in an archetypal succumbing to all the
things we know to be wrong. We ate crap, we've become enslaved with
surprising violence to simple pleasures. That surprising violence has
also been reflected in our physical state, which was highly irregular. I
woke up today at 7 or 8, immediately watched crap, then slept again
until 3pm or so. Extremely tired, today barely existed. Today was,
however, some moderate progress from yesterday, in that I kept strictly
to a diet -- not that I had many temptations to overcome if I'm honest.
I've had headaches all day today. There was that ethereal, temporary,
almost mobile feeling again that seems to come with spring, as if I'm on
the verge of something. Of some large change, that I don't overinvest in
the present soon to change. My mind has become rather empty once again.
My motivation, if I have any, is sort like this spiritual curiosity.

I don't know what will come of this state. It seems like a huge crash is
imminent. Can this be avoided? Is it a necessary reformation of my
psyche? Is my body forcing dramatic failure that I can be built better
from the ashes? If that's the case, I'd surely like to avoid that
dramatic crash. The failure to complete my responsibilities quite scares
me -- as it should.

Right now I do have a motivation, it seems, to do my course work.
Perhaps I can focus on that. I also have, from that mentioned curiosity,
some motivation or want to continue abstaining from certain things, that
I might see how far down the rabbit hole goes. This isn't good though. I
remember these same feelings in Israel. This leads to dysfunctional
disaster, we should do what we can to reenter normal routine and return
to normal.

8:54pm

I don't have conviction, but I'm seemingly lacking addiction and desire.
I'm also growing excited thinking of building myself, being the artist
of my person. Let us pursue.

12:14am

We've sort of come back to normal I'm thinking. Lets wake up tomorrow on
time, go running as we do, and try to reclaim some responsibility.
Coding is certainly the most attractive labor. We should study some
comparch for the exam though. We can wait for algo tomorrow to see
studying for that.

\bigskip
\bigskip
March 5th, 2020

12:28 pm

We're seemingly starting to come out of that strange funk. Still quite
in the funk, but I can feel it alleviating slightly. I'm thinking it's
now time to revisit those old lessons of discipline. We need to find
tangible tasks and do them, and they need to be ones related to
alleviating this stress about our exams.

First let us situate a hierarchy. First, study fully and completely for
comparch to the extent we're able with what we have right now. Do this
studying on paper, perhaps dedicate to it a notebook. The same thing,
then, for Info class. Then also for software meth, and finally catch up
with algo. If all goes well, on Sunday we should have an additional
session to reconfirm our knowledge and situate confidence in the
material. This shouldn't be necessary at all for info. A similar session
should happen for software meth on Tuesday.

\bigskip
\bigskip
